---
title: "Network Modeling for GlobalMix India Data"
author: "Billy Dehao Chen"
date: "7/6/2023"
output: word_document
---

# Background
This is a living document for network modeling of the India GlobalMix diary data. The current modeling focuses on the the mixing at home and will be expanded to other settings later (nonhome, rural, urban) (discussion point).

# Method
## Retrieving degree information from the India data
We used the daily mean degree data by network predictor (e.g., contact location), participant's age group, and contact's age group to calculate the total mean degree of the whole network by network predictor. We retrieved the total daily degree of each age group from the symmetric contact matrix, from which we also calculated the proportion of within-age-group matching by network predictor.

```{r, echo=F, warning=F, message=FALSE}
library(tidyverse)
library(socialmixr)
library(EpiModel)

# things to be completed - sync to git, average age of participants


# load contact data----------------------------------------

# 'raw'  mixing data by mean degree for one day
gm <- readRDS("../output/data/india_mix.sum.no15.RData")[[2]] # mixing degree by contact location
# daily mixing matrix
matrix <- readRDS("../output/data/avg.matrix.india.predictors.RData") 

#  daily mixing matrix by mean degree
gm2 <- matrix$avg.matrix.india.contact_location$avg.matrix %>%
  rename(contact_location = predictor_contact) %>% # for now, we will initiate the model by contact location
  ungroup()
rm(matrix)

# total mean degree by contact location using raw data
md <- gm %>%
  group_by(contact_location,p_age,n_participants) %>%
  summarise(n_contacts = sum(n_contacts)) %>% # the sum of two-day contacts
  ungroup() %>%
  group_by(contact_location) %>%
  summarise(n_contacts = sum(n_contacts), #  total contacts over two days
            n_participants = sum(n_participants)) %>%
  mutate(md.daily = (n_contacts/n_participants)/2) # mean degree at daily scale

# Total daily mean degree from the global mix data
md.h <- md %>%
  filter(contact_location == "Home") %>%
  select(md.daily) %>%
  as.numeric()

#  total daily degree of edges per age group for nodefactor()
md.h.ag <- gm2 %>%
  filter(contact_location == "Home") %>%
  select(total_degree) %>%
  as_vector() %>%
  as.numeric()

# proportion of daily within-age-group matching by contact_location
md.match <- gm2  %>% 
  mutate(within_age_edges = total_degree*prop_match) %>% # at the daily scale
  select(contact_location,age,total_degree,within_age_edges) %>%
  group_by(contact_location) %>%
  summarise(total_degree = sum(total_degree),
            within_age_edges = sum(within_age_edges)) %>%
  mutate(match = within_age_edges/total_degree) # at the daily scale


```

### Total mean degree of the whole network by contact location.
```{r, warning=F, message=FALSE, echo=F}
md
```

### Total daily degree of edges from age groups 1 to 10
```{r, warning=F, message=FALSE, echo=F}
md.h.ag
```

### Proportion of daily within-age-group matching by contact location
```{r, warning=F, message=FALSE, echo=F}
md.match
```

## Modeling
### Network set-up
As a start, we set up the network in the following way. The distribution for age was chosen arbitrary, so this needs to be strengthened by better knowing the age distribution of the target population (discussion point).

```{r, warning=F, message=FALSE, echo=T}
### nodes
n <- 10000 

### age group
age <- round(rnorm(n, mean = 39, sd = 21), 1) # arbitrary select mean and sd to Define age.
age <- pmax(age, 0) # if an obs. w/ age < 0, assign 0 to this obs.
age <- pmin(age, 99)

age.breaks <- seq(0, 100, 10)
age.grp <- cut(age, age.breaks, labels = FALSE, right = FALSE) # divide age into 10 even groups

nw <- network.initialize(n)
nw <- set_vertex_attribute(nw, "age.grp", age.grp)
hist(age)
```

### Models
#### Formation model
We explored the following model. For the model adjusting for heterogeneity by age group, we excluded the 10th group to make the model identifiable. This age group has the lowest target statistic of 381 (discussion point, would the dropping of other levels be necessary?).
```{r, warning=F, message=FALSE, echo=T}
formation.edge <- ~edges 
formation.edge.nf <- ~edges + nodefactor("age.grp" , levels = 1:9) # dropping the 10th age group
```

#### Dissolution model
```{r, warning=F, message=FALSE, echo=T}
coef.diss.hh <- dissolution_coefs(dissolution = ~offset(edges), duration = 100000) 
```

#### Calculating target statistics
We used the following script to calculate the target statstics. The target statistics for the model with "edges" and "nodefactor" terms is shown at the bottom.
```{r, warning=F, message=FALSE, echo=T}
### Total Edges, at daily scale
edges.h <- md.h * n/2 

### Number of edges per age group, at daily scale
#### Number of target population within each age group
age.grp.num <- as.numeric(table(age.grp)) 
#### Number of edges per age group for nodefactor(), at daily scale
nf.h.ag <- md.h.ag * age.grp.num # daily total degree * total number of people in each age group = number of edges per age group

###  Number of edges involved in within-group mixing
#### Proportion of daily within-group mixing 
#match.h.ag <- md.match$match[md.match$contact_location == "Home"]
#### for nodematch()
#nm.hh.ag <- edges.h * match.h.ag
target.stats.edges.h <- c(edges.h)
target.stats.edges.nf.h <- c(edges.h, nf.h.ag[1:9]) # initially [1:9], see if grp 1 is the reference group by default
target.stats.edges.nf.h
```

#### Edge-only model
We fitted an edge-only model and encountered the following warning (discussion point). Based on its estimates, we simulated networks with edges and nodefactor.
```{r, warning=F, message=T, echo=T}
## Fit edge-only model to data
est.h.edges <- netest(nw, formation.edge, target.stats.edges.h, coef.diss.hh,
                 set.control.ergm = control.ergm(MCMLE.maxit = 500)
                 )
#### Simulate based on the edge model adding an extra term, 
dx.h.edges.age.grp <- netdx(est.h.edges, nsims = 1, ncores = 1, nsteps = 1000, dynamic = T,
               set.control.ergm = control.simulate.formula(MCMC.burnin = 1e6),
               nwstats.formula = ~edges  + 
                 nodefactor("age.grp"), 
               keep.tedgelist = TRUE)
```

```{r, warning=F, message=FALSE, echo=F}
dx.h.edges.age.grp <- 
dx.h.edges.age.grp$stats.table.formation %>% select(2, 4) %>%
  filter(!row_number() %in% c(1)) %>% 
  mutate(Sim_mean_ci_low = `Sim Mean` -1.96*`Sim SE`,
         Sim_mean_ci_up = `Sim Mean` +1.96*`Sim SE`) %>% 
  rownames_to_column(var= "age.grp") %>% 
  mutate(age.grp=str_replace(age.grp,  "nodefactor.age.grp.", "")
  ) %>% 
 select(-`Sim SE`)
```
#### Model with edges and nodefactor
We fitted a model with edges and nodefactor and simulated networks with these two terms. 
```{r, warning=F, message=FALSE, echo=T}
## Fit model with edge and nodefactor to data
est.h.edges.nf <- netest(nw, formation.edge.nf, target.stats.edges.nf.h, coef.diss.hh,
                      set.control.ergm = control.ergm(MCMLE.maxit = 500)
                      )
dx.h.edges.age.grp.obs <- netdx(est.h.edges.nf, nsims = 1, ncores = 1, nsteps = 1000, dynamic = T,
                            set.control.ergm = control.simulate.formula(MCMC.burnin = 1e6),
                            nwstats.formula = ~edges  + 
                              nodefactor("age.grp", levels =1:9), 
                            #nodefactor("age.grp",levels = NULL), 
                            keep.tedgelist = TRUE) 
```

```{r, warning=F, message=FALSE, echo=F}
dx.h.edges.age.grp.obs <- 
dx.h.edges.age.grp.obs$stats.table.formation %>% select(2, 4) %>%
  filter(!row_number() %in% c(1)) %>% 
  mutate(Sim_mean_ci_low_obs = `Sim Mean` -1.96*`Sim SE`,
         Sim_mean_ci_up_obs = `Sim Mean` +1.96*`Sim SE`) %>% 
  rownames_to_column(var= "age.grp") %>% 
  mutate(age.grp=str_replace(age.grp,  "nodefactor.age.grp.", "")
  ) %>%  rename(Sim_mean_obs = `Sim Mean`) %>% select(-`Sim SE`)
```

# Result
We compared the simulated and observed target statistics of age groups. In the following figure, the observed degrees arree indicated by black dots. The simulated degrees and their 95% confidence intervals (CIs), based on the edgee-only model, are listed in gray. The simulated degrees and their 95% confidence intervals, based on the model with edge abd nodefactor, are listed in green. Given wide the range of degree across age groups, the CIs were squeezed with the simulated estimates.

Except for the 10th age group, the observed target statistics of age groups were far from their counterparts of the edge-only model. This suggests it is necessary to account for age.group for the next step. Despite a close proximity between the observed and simulated target statistics of the model with edge and nodefactor terms, the observed statistics still fall out of the simulated 95CIs (discussion point).

```{r, warning=F, message=FALSE, echo=F, fig.width=7, fig.height=5}
full_join(dx.h.edges.age.grp, dx.h.edges.age.grp.obs, by = "age.grp") %>% 
  mutate(age.grp = as.numeric(age.grp)) %>% 
  arrange(age.grp) %>% 
  mutate(age.grp = factor(age.grp)) %>% 
  bind_cols(target_pop_mean =nf.h.ag) %>% 
  
  ggplot(aes(x= age.grp, y = `Sim Mean`))+
    geom_point(color = "gray")+
  geom_errorbar(aes(ymin = Sim_mean_ci_low,
                    ymax = Sim_mean_ci_up ), color = "gray")+
  geom_point(aes(x= age.grp, y = Sim_mean_obs), color = "forestgreen")+
  geom_errorbar(aes(ymin = Sim_mean_ci_low_obs,
                    ymax = Sim_mean_ci_up_obs), color = "forestgreen")+
  geom_point(aes(x= age.grp, y = target_pop_mean), color = "black"
  ) + ylab("Number of edges") +  theme_classic() 
# Note: Given the simulated target statistics of age.group differ from the counterparts of the target population, 
# there is a need to account for this attribute in model estimation.
```

# Questions
1. For the India data, the 10 age groups have uneven intervals while the 10 age groups for the target population have even intervals. Also, the age intervals of the study and target populations do not match with each other. How we can resolve this mismatching?
2. For the dissolution model, it seems duration, a parameter without time unit, can be randomly selected?
3. Given the above figure, is the age group of 1 treated as a reference group in simulation for the simulation yielding the gray estimates? If so, what is the reference group for the simulation yielding the green estimates? Is it group 10?
4. For the edge-level edge, node-level nodefactor, and edge-level nodematch terms, how the counting twice of edge for nodefactor and counting once for nodematch be reflected in target statistics for estimation and simulation outputs.
5. Currently, the contacts at home and at other home are combined as contact at home. Is there any issue with this?
6. Is the model selection rule summarized correctly?




