---
title: "Descriptive Degree Summary of GlobalMix India Data"
author: "Billy Dehao Chen"
date: "09/07/2023"
output:
  html_document: default
  word_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

# Background
This is a descriptive summary of contact degree of the India GlobalMix diary data.

# Method
There are two ways to derive target statistics for ERGM, one is using poisson model based on individual-count data, the other is based on the symmetric contact matrix, the approach for Corporate Mix. Given the symmetric contact matrix may not account for the different number of participants among age group, we go with the glm-based approach to calculate the summary network statistics.

We adapted the code Maria developed for the CorporateMix data to the GlobalMix data to calculate degree information. The degree information was summarized into four separate networks for two different epidemic models (one rural, one urban). We consider the mixing occurs within locations (urban, rural) and across two types of network layers (home/school/work/nonhome [other than school/work], indoors/outdoors). We do not model contacts across layers, as we assume they are mutually exclusive across environments. We regrouped the age categories in the first two decades of life by decade.


We excluded contacts lasted ≤ 15 mins in analysis. The degree information was summarized as the arithmetic mean of signle-day degrees of contact between group A and group B and between group B and group A of the two-day visits. Given the data were egocentric, we use $M.D.=\frac{edges}{n}$ for the relationship between mean degree ($M.D.$) and the number of edges.


```{r, echo=F, warning=F, message=FALSE, include = FALSE}
setwd("~/Documents/GitHub/COVID-GlobalMix")

# Load libraries and data  ------------------------------------------------
lapply(c("ggpubr", "statnet", "EpiModel", "tidyverse", "socialmixr", "knitr",  "sjlabelled", "kableExtra", "broom"), require, character.only = TRUE)


## participant data
india_participant <- 
readRDS("~/Documents/GitHub/COVID-GlobalMix/data/participant_contact/india_participant_data_aim1.RDS")%>% rename(id = rec_id)
#readRDS("../Documents/GitHub/COVID-GlobalMix/data/participant_contact/india_participant_data_aim1.RDS")%>% rename(id = rec_id)


## contact data 
india_contact <- 
 readRDS("~/Documents/GitHub/COVID-GlobalMix/data/participant_contact/india_contact_data_aim1.RDS")%>% rename(id = rec_id)
#readRDS("../Documents/GitHub/COVID-GlobalMix/data/participant_contact/india_contact_data_aim1.RDS")%>% rename(id = rec_id)

# Note - validated study_site of participant is exactly the same as those in contact

# Reclassifying participant's and contact's age groups into 0-9 years old, 10-19 years old, while treating other age groups as is.
## participant
india_participant <- 
india_participant %>% 
  mutate(
      participant_age = case_when(
        participant_age %in% c("<6mo", "6-11mo",   "1-4y",   "5-9y") ~ "0-9y",
        participant_age %in% c("10-14y", "15-19y") ~ "10-19y",
        .default =  participant_age
      )
    )%>% 
  mutate(participant_age= factor(participant_age, levels=c("0-9y", "10-19y", "20-29y", "30-39y", "40-59y",   "60+y")
                                         )
         ) 

## contact
india_contact <- 
india_contact %>%     
  mutate(
      contact_age = case_when(
        contact_age %in% c("<6mo", "6-11mo",   "1-4y",   "5-9y") ~ "0-9y",
        contact_age %in% c("10-14y", "15-19y") ~ "10-19y",
        .default =  contact_age
      )
    )%>% 
    mutate(contact_age= factor(contact_age, levels=c("0-9y", "10-19y", "20-29y", "30-39y", "40-59y",   "60+y")
                                         )
         )

# merge participants and contact datasets and process data  and basic data processing ------------------------------------------------
india_mix <- india_participant %>%
  dplyr::select(id,participant_age) %>%
  right_join(india_contact,
            by = "id") %>% 
  # characterization of home/nonhome status
   mutate(contact_location = case_when(location_contact___0 == 1  ~ "Home", # 0 - "My home"
                                            location_contact___2 == 1 & location_contact___0 == 0 ~ "School", # "School" but not "my home"
                                             location_contact___3 == 1 & location_contact___0 == 0 ~ "Work", # "work" but not "my home"
                                       
                                       
                                       (
                                       location_contact___1 == 1 | location_contact___4 == 1 | # "Other home",  "Transport/Hub"
                                       location_contact___5 == 1 | location_contact___6 == 1 | # "Market/Shop", "Street"
                                       location_contact___7 == 1 | location_contact___8 == 1 | # "Playground", "Well"
                                       location_contact___9 == 1 | location_contact___10 == 1 | # "Agricultural Field", "Market/Shop"
                                       location_contact___11 == 1 | location_contact___12 == 1 | # "Restaurant", "Religious centre"
                                       location_contact___13 == 1 | location_contact___14 == 1 | # "Govt offices", "Health center"
                                       location_contact___15 == 1 | location_contact___16 == 1 | # "Bank", "Movie theatre"
                                       location_contact___17 == 1 | location_contact___18 == 1 | location_contact___19 == 1 #"Exhibition", "Social hall", "Other"
                                       ) &
                                         !(location_contact___3 == 1 | location_contact___2 == 1) # Excluding work/school
                                       
                                       ~ "Nonhome") # assign contacts into home or nonhome layer
         )  %>% 
  mutate(contact_location = factor(contact_location,
                                   # levels = c("Home","Nonhome"),
                                    ordered = TRUE)
         ) %>% 
  filter(!(duration_contact %in% c("<5 mins", "5-15 mins"))) %>% # filter out contact with duration ≤ 15 mins
  mutate(
         duration_contact = factor(duration_contact,
                                    levels = c( "16-30 mins",  "31 mins-1 hr", "1-4 hrs", ">4 hrs", "Unknown"),
                                    ordered = TRUE)
         )  
   

```
## Characterization of network layers
The network layers is processed from multiple questions asking contact locations. Given these questions are not mutually exclusive due to the check-box design in REDCap, a contact is characterized as at home when any contact with a participant reportedly occurred at the participant's home (i.e., "my home")  regardless of the responses for other contact location types. The contacts occurred at other's home is considered as a non-home contact: given the sociological contact pattern in a participant's residence and other’s home is likely vary, we consider contacts occurring at home and others' home separately.
For contacts occurred at work or school, we assigned them into one of these categories. For the two contacts (shown below) that occurred at both work (location 3 in REDCap) and school (location 2), we categorized them as at school, considering the contacts were at school age.
For non-home contacts excluding work and school, we categorize them into the non-home category.
For a contact checked non of the categories, we assigned an NA to this contact.

```{r, echo=F, warning=F, message=FALSE}
india_mix %>% select(participant_age, contact_age, location_contact___2, location_contact___3) %>% mutate(sum = location_contact___2+location_contact___3) %>% filter(sum==2) %>% select(-sum)%>%  kable() %>%  kableExtra::kable_classic(full_width = F, html_font = "Cambria")
```

```{r, echo=F, warning=F, message=FALSE, fig.show='hide', results='hide'}
## Distribution of indoor/outdoor status
#The following is a break down of the observed categories of the variable "where_contact" indicating in- and out-door status. In the original data, there is a "Both" category indicates a participant contacted with a contact both in- and out-doors.  Since the "Both" category could have a higher transmission potential similar to the "Indoors" category, we merge the "Both" into the "Indoors" category. We will adjust for this status as a nodefactor. For building the transmission model, we will assign lower risk for the "Outdoors" category during simulation.

# merge the both and indoor categories into the latter.
india_mix <-
india_mix %>% mutate(where_contact2=case_when(where_contact %in% c("Indoors", "Both") ~ "Indoors",
                                              .default = where_contact)
                     )

india_mix %>% 
  
  group_by( where_contact2, study_site) %>%
  tally() %>%  spread(study_site, n) %>% kable()%>%
   kableExtra::kable_classic(full_width = F, html_font = "Cambria")

#chisq.test(table(india_mix$contact_location, india_mix$study_site))
```



```{r, echo=F, warning=F, message=FALSE}
# split data into urban and rural networks using study site, and get the number of participants with 0 contact in specified age groups

# 20230919 - update this function to get individual-level participants w/o contacts
data_split <- function(india_mix., india_participant., india_contact., study_site., age.grp){
 out <-  list()
 out[[1]] <-
 india_mix. %>% filter(!is.na(contact_location) # complete-case analysis - exclude contacts didn't have a contact location from analysis
                      ) %>% 
  filter(study_site == study_site.) # here we split the dataset into urban or rural samples


out[[2]] <- # participants with 0 contacts by study site in India
  india_participant. %>%
  filter(!(id %in% india_contact.$id)) %>%
  filter(study_site == study_site.) %>% # here we split the dataset into urban or rural samples
  group_by(participant_age) %>%
  tally(name = "n_participants0")

names(out) <-  c(paste0("india_mix.", tolower(study_site.), age.grp), 
                 paste0("india.no.contacts.",  tolower(study_site.), age.grp)
                 )

out
} 



india_mix.rural.6age.grps <- # rural mixing, six age groups
data_split(india_mix. = india_mix, 
           india_participant. = india_participant, 
           
           india_contact. = india_contact,
           study_site. ="Rural", age.grp = ".6age.grps") # .6age.grps


india_mix.urban.6age.grps <- # urban mixing, six age groups
data_split(india_mix. = india_mix , 
           india_participant. = india_participant, 
           
           india_contact. = india_contact,
           study_site. ="Urban", age.grp = ".6age.grps") # .6age.grps
```



## Uncertainties of network statistics
The following characterization of network statistics is adapted from ARTnet. We use the following models to estimate the network statistic's uncertainties in each layer of the rural network.
$$
M.D_{i,j} \sim Poisson(\beta_0)
$$

$$
M.D_{i,j} \sim Poisson(\beta_{age.grp}*age.grp_i)
$$


```{r}

# Data processing
contact_freq <- 
function(data, site, india_participant, india_contact){
  locations <- levels(data$contact_location)
  
## participants having no contact
id_no_contact <- 
  india_participant %>%
  filter(!(id %in% india_contact$id)) %>%
  filter(study_site == site)


## Total number of contacts over two days
contact_count <- 
data %>%
   group_by(id, contact_location, fromdayone, .drop = F)%>% summarise(n_contacts = n()) %>% # summarizing number of contacts by type
  ungroup() %>% 
  mutate(
    n_contacts = case_when(
    contact_location %in% c("Home", "Work","School") ~ n_contacts, # for these layers, a replicated contact is counted as unique contact
    contact_location %in% c("Nonhome" ) & fromdayone == "Both days" ~ n_contacts*2, # for non-home layer, a replicated contact is counted as two contact
    contact_location %in% c("Nonhome" ) & fromdayone %in% c("Day 1", "Day 2") ~ n_contacts, # for non-home layer, a unique contact is counted as one contact
    T ~ n_contacts # for observation with fromdayone information missed, we return the original n_contacts
    )  
    )%>% 
  group_by(id, contact_location, .drop = F) %>% summarise(n_contacts = sum(n_contacts)
                                                          ) %>% ungroup() %>% # total number of contacts over two days
   # add the participants w/o contact to the data
  rbind(., 
        data.frame(
          id = rep(as.character(id_no_contact$id), each = length(locations)),
          contact_location= rep(locations, 
                                nrow(id_no_contact)
                                ),
          n_contacts=rep(0,  nrow(id_no_contact)*length(locations))
        )
  ) %>% 
  # joining w/ participant's age
  left_join(india_participant %>% select(id, participant_age),
            by = "id"
            )

## Number of contacts of the same age group, individual-level
same.age.grp_count <- 
data %>% 
  mutate(same.age.grp = ifelse(participant_age == contact_age, 1, 0)
         
           ) %>% 
 mutate(
    same.age.grp_1 = case_when(
    contact_location %in% c("Home", "Work","School") ~  same.age.grp, # for these layers, a replicated contact is counted as unique contact
    contact_location %in% c("Nonhome" ) & fromdayone == "Both days" ~ same.age.grp*2, # for non-home layer, a replicated contact is counted as two contact
    contact_location %in% c("Nonhome" ) & fromdayone %in% c("Day 1", "Day 2") ~ same.age.grp, # for non-home layer, a unique contact is counted as one contact
    T ~ same.age.grp # for observation with fromdayone information missed, we return the original same.age.grp
    )  
    ) %>%
  select(id,  contact_location, same.age.grp_1,  contact_age) %>% 
  rbind(., 
        data.frame(
          id = rep(as.character(id_no_contact$id), each = length(locations)),
          contact_location= rep(locations, 
                                nrow(id_no_contact)
                                ),
           same.age.grp_1=rep(0,  nrow(id_no_contact)*length(locations)),
          contact_age =NA
        )
        )%>% 
  # joining w/ participant's age
  left_join(india_participant %>% select(id, participant_age),
            by = "id"
            ) 

  out <-list(contact_count, same.age.grp_count); names(out) <- c("contact_count", "sameage.grp.count")
  
  out

}


contact_count_rural <- contact_freq(data=india_mix.rural.6age.grps$india_mix.rural.6age.grps, 
                              site = "Rural",
                              india_participant = india_participant ,
                              india_contact = india_contact)

contact_count_urban <- contact_freq(data=india_mix.urban.6age.grps$india_mix.urban.6age.grps, 
                              site = "Urban",
                              india_participant = india_participant ,
                              india_contact = india_contact)


#contact_count_rural$sameage.grp.count %>% View()


# Fit contact_count to glm 
#output <- list()

## Edges 
fit_edge <- 
  contact_count_rural$contact_count %>% 
  glm(n_contacts~ -1+contact_location, data=., family = poisson) %>% summary() # coefficient for two-day contact rate
fit_edge

fit_edge <- (fit_edge$coefficients%>% as.data.frame() %>% select(Estimate) %>% exp())/2 # the two is averaging two-day's contact rate to one-day

#output[[1]] <- fit_edge


## nodefactor age.grp
nf_dat_pred <- 
data.frame(
  participant_age=
 contact_count_rural$contact_count$participant_age %>% levels()
 )

nf <- data.frame() #matrix(NA, nrow = length(locations), ncol = length(levels(contact_count$participant_age)))
for (i in 1:4 #length(locations)
     ) {
  fit_nf_single <- 
  contact_count_rural$contact_count %>% filter(contact_location == levels(contact_count_rural$contact_count$contact_location)[i]) %>% 
  glm(n_contacts~ -1+participant_age, data=., family = poisson) # coefficient for two-day contact rate
  
  nf_single <- fit_nf_single$coefficients %>% exp()/2 # the two is averaging two-day's contact rate to one-day
  
  nf <- 
  rbind(nf, nf_single)
      #     y_link_nf <- 
#   predict(fit_nf, 
#           newdata = nf_dat_pred, 
#           type = "link",
#           se.fit = T
#          )
#  y <- exp(y_link$fit)
#   y_up <- exp(y_link$fit+1.96*y_link$se)
# y_low <- exp(y_link$fit-1.96*y_link$se)


}

colnames(nf) <- contact_count_rural$contact_count$participant_age %>% levels()
row.names(nf) <- levels(contact_count_rural$contact_count$contact_location)
nf


### average matched degree across age groups
contact_count_rural$sameage.grp.count %>% group_by(participant_age) %>% 
  summarize(mean(same.age.grp_1)/2
                  )
  
fit_nm <- glm(same.age.grp_1 ~ -1+ participant_age,
               data = contact_count_rural$sameage.grp.count, family = binomial
              )
#mean(
predict(fit_nm, newdata = nf_dat_pred, type = "response")/2  
#)
### average matched degree regardless of age groups
mean(data$same.age.grp)

fit_nm_1 <- glm(same.age.grp_1 ~ 1,
               data = contact_count_rural$sameage.grp.count, family =  poisson
              )

predict(fit_nm_1, newdata = data.frame(1), type = "response") 

##### To be completed - no contacts need to be adjusted
           

```

## Contact durations
```{r}
india_mix.rural.6age.grps$india_mix.rural.6age.grps$duration_contact %>% table(., useNA = "always")

india_mix.rural.6age.grps$india_mix.rural.6age.grps <- 
india_mix.rural.6age.grps$india_mix.rural.6age.grps %>% 
  #filter(contact_location %in% c("School", "Work")) %>% select(duration_contact, frequency_contact, known_contact)  %>%  
  mutate(duration_contact_mid =    case_when(duration_contact == "16-30 mins" ~ "23 mins",
                                          duration_contact == "31 mins-1 hr" ~ "46 mins",
                                           duration_contact ==  "1-4 hrs"  ~ "2.5 hrs",
                                             duration_contact ==  ">4 hrs" ~ ">4hrs")
         )# calculate midpoint here %>% View()

india_mix.rural.6age.grps$india_mix.rural.6age.grps$duration_contact_mid %>% table()
```

## Correlation between layers
```{r}
# rural
library(GGally)

## data to wide format 
 test_rural  <- 
contact_count_rural$contact_count %>% data.frame()%>% 
  tidyr::pivot_wider(names_from = "contact_location", values_from = "n_contacts"
                     ) %>%  # 608 rows, each row for a participant
  as.data.frame()
 
 # urban
## data to wide format 
 test_urban  <- 
contact_count_urban$contact_count %>% data.frame()%>% 
  tidyr::pivot_wider(names_from = "contact_location", values_from = "n_contacts"
                     ) %>%  # 608 rows, each row for a participant
  as.data.frame()


## pearson correlation,rural
test_rural %>% select(-c(id, participant_age)) %>% ggpairs(upper = list(continuous = wrap("cor", method = "spearman")))

## pearson correlation,urban
test_urban %>% select(-c(id, participant_age)) %>% ggpairs(upper = list(continuous = wrap("cor", method = "spearman")))



```

