---
title: "Descriptive Degree Summary of GlobalMix India Data"
author: "Billy Dehao Chen"
date: "09/25/2023"
output:
  html_document: default
  word_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

# Background
This is a descriptive summary of contact degree of the India GlobalMix diary data.

# Method
There are two ways to derive target statistics for ERGM, one is using poisson model based on individual-count data, the other is based on the symmetric contact matrix, the approach for Corporate Mix. Given the symmetric contact matrix may not account for the different number of participants among age group, we go with the glm-based approach to calculate the summary network statistics.

We adapted the code Maria developed for the CorporateMix data to the GlobalMix data to calculate degree information. The degree information was summarized into four separate networks for two different epidemic models (one rural, one urban). We consider the mixing occurs within locations (urban, rural) and across two types of network layers (home/school/work/nonhome [other than school/work], indoors/outdoors). We do not model contacts across layers, as we assume they are mutually exclusive across environments. We regrouped the age categories in the first two decades of life by decade.


We excluded contacts lasted ≤ 15 mins in analysis. The degree information was summarized as the arithmetic mean of signle-day degrees of contact between group A and group B and between group B and group A of the two-day visits. Given the data were egocentric, we use $M.D.=\frac{edges}{n}$ for the relationship between mean degree ($M.D.$) and the number of edges.


```{r, echo=F, warning=F, message=FALSE, include = FALSE}
setwd("~/Documents/GitHub/COVID-GlobalMix")

# Load libraries and data  ------------------------------------------------
lapply(c("ggpubr", "statnet", "EpiModel", "tidyverse", "socialmixr", "knitr",  "sjlabelled", "kableExtra", "broom", "stringr"), require, character.only = TRUE)


## participant data
india_participant <- 
readRDS("~/Documents/GitHub/COVID-GlobalMix/data/participant_contact/india_participant_data_aim1.RDS")



## contact data 
india_contact <- 
 readRDS("~/Documents/GitHub/COVID-GlobalMix/data/participant_contact/india_contact_data_aim1.RDS")
#readRDS("../Documents/GitHub/COVID-GlobalMix/data/participant_contact/india_contact_data_aim1.RDS")

# Note - validated study_site of participant is exactly the same as those in contact

# Reclassifying participant's and contact's age groups into 0-9 years old, 10-19 years old, while treating other age groups as is.
## participant
india_participant <- 
india_participant %>% 
  mutate(
      participant_age = case_when(
        participant_age %in% c("<6mo", "6-11mo",   "1-4y",   "5-9y") ~ "0-9y",
        participant_age %in% c("10-14y", "15-19y") ~ "10-19y",
        .default =  participant_age
      )
    )%>% 
  mutate(participant_age= factor(participant_age, levels=c("0-9y", "10-19y", "20-29y", "30-39y", "40-59y",   "60+y")
                                         )
         ) %>% mutate(participant_ageyr = floor(participant_ageyr)
                      )

## contact
india_contact <- 
india_contact %>%     
  mutate(
      contact_age = case_when(
        contact_age %in% c("<6mo", "6-11mo",   "1-4y",   "5-9y") ~ "0-9y",
        contact_age %in% c("10-14y", "15-19y") ~ "10-19y",
        .default =  contact_age
      )
    )%>% 
    mutate(contact_age= factor(contact_age, levels=c("0-9y", "10-19y", "20-29y", "30-39y", "40-59y",   "60+y")
                                         )
         )

# merge participants and contact datasets and process data  and basic data processing ------------------------------------------------
india_mix <- india_participant %>%
  dplyr::select(rec_id,participant_age, participant_ageyr) %>%
  right_join(india_contact,
            by = "rec_id") %>% 
  # characterization of home/nonhome status
   mutate(contact_location = case_when(location_contact___0 == 1  ~ "Home", # 0 - "My home"
                                            location_contact___2 == 1 & location_contact___0 == 0 ~ "School", # "School" but not "my home"
                                             location_contact___3 == 1 & location_contact___0 == 0 ~ "Work", # "work" but not "my home"
                                       
                                       
                                       (
                                       location_contact___1 == 1 | location_contact___4 == 1 | # "Other home",  "Transport/Hub"
                                       location_contact___5 == 1 | location_contact___6 == 1 | # "Market/Shop", "Street"
                                       location_contact___7 == 1 | location_contact___8 == 1 | # "Playground", "Well"
                                       location_contact___9 == 1 | location_contact___10 == 1 | # "Agricultural Field", "Market/Shop"
                                       location_contact___11 == 1 | location_contact___12 == 1 | # "Restaurant", "Religious centre"
                                       location_contact___13 == 1 | location_contact___14 == 1 | # "Govt offices", "Health center"
                                       location_contact___15 == 1 | location_contact___16 == 1 | # "Bank", "Movie theatre"
                                       location_contact___17 == 1 | location_contact___18 == 1 | location_contact___19 == 1 #"Exhibition", "Social hall", "Other"
                                       ) &
                                         !(location_contact___3 == 1 | location_contact___2 == 1) # Excluding work/school
                                       
                                       ~ "Nonhome") # assign contacts into home or nonhome layer
         )  %>% 
  mutate(contact_location = factor(contact_location,
                                   # levels = c("Home","Nonhome"),
                                    ordered = TRUE)
         ) %>% 
  filter(!(duration_contact %in% c("<5 mins", "5-15 mins"))) %>% # filter out contact with duration ≤ 15 mins
  mutate(
         duration_contact = factor(duration_contact,
                                    levels = c( "16-30 mins",  "31 mins-1 hr", "1-4 hrs", ">4 hrs", "Unknown"),
                                    ordered = TRUE)
         )  %>% filter(!is.na(contact_location) # complete-case analysis - exclude contacts didn't have a contact location from analysis, Moses confirmed this is okay
                      ) 
   

# confirm that those ids of contacts in aim 2 are exclusive of aim 1
intersect(
india_contact %>% filter(study_aim ==2) %>% pull(rec_id) %>% unique() ,
india_contact %>% filter(study_aim ==1) %>% pull(rec_id) %>% unique()
) # output character(0), confirming no intersection of study participant
```




## Characterization of network layers
The network layers is processed from multiple questions asking contact locations. Given these questions are not mutually exclusive due to the check-box design in REDCap, a contact is characterized as at home when any contact with a participant reportedly occurred at the participant's home (i.e., "my home")  regardless of the responses for other contact location types. The contacts occurred at other's home is considered as a non-home contact: given the sociological contact pattern in a participant's residence and other’s home is likely vary, we consider contacts occurring at home and others' home separately.
For contacts occurred at work or school, we assigned them into one of these categories. For the two contacts (shown below) that occurred at both work (location 3 in REDCap) and school (location 2), we categorized them as at school, considering the contacts were at school age.
For non-home contacts excluding work and school, we categorize them into the non-home category.
For a contact checked non of the categories, we assigned an NA to this contact.

```{r, echo=F, warning=F, message=FALSE}
india_mix %>% select(participant_age, contact_age, location_contact___2, location_contact___3) %>% mutate(sum = location_contact___2+location_contact___3) %>% filter(sum==2) %>% select(-sum)%>%  kable() %>%  kableExtra::kable_classic(full_width = F, html_font = "Cambria")
```

```{r, echo=F, warning=F, message=FALSE, fig.show='hide', results='hide'}
## Distribution of indoor/outdoor status
#The following is a break down of the observed categories of the variable "where_contact" indicating in- and out-door status. In the original data, there is a "Both" category indicates a participant contacted with a contact both in- and out-doors.  Since the "Both" category could have a higher transmission potential similar to the "Indoors" category, we merge the "Both" into the "Indoors" category. We will adjust for this status as a nodefactor. For building the transmission model, we will assign lower risk for the "Outdoors" category during simulation.

# merge the both and indoor categories into the latter.
india_mix <-
india_mix %>% mutate(where_contact2=case_when(where_contact %in% c("Indoors", "Both") ~ "Indoors",
                                              .default = where_contact)
                     )

india_mix %>% 
  
  group_by( where_contact2, study_site) %>%
  tally() %>%  spread(study_site, n) %>% kable()%>%
   kableExtra::kable_classic(full_width = F, html_font = "Cambria")

#chisq.test(table(india_mix$contact_location, india_mix$study_site))
```


## Uncertainties of network statistics
The following characterization of network statistics is adapted from ARTnet. We use the following models to estimate the network statistic's uncertainties in each layer of the rural network.
$$
M.D_{i,j} \sim Poisson(\beta_0)
$$

$$
M.D_{i,j} \sim Poisson(\beta_{age.grp}*age.grp_i)
$$


```{r}

# Function characterizing number of contact at the individual  and the status of if a participant and contact was in the same age group for the contact data
contact_freq_site <- function(india_mix., india_participant., india_contact., study_site.){
india_mix.site <- 
 india_mix.  %>% 
  filter(study_site == study_site.) # here we split the dataset into urban or rural samples


id_no_contact.site <- # participants with 0 contacts by study site in India
  india_participant. %>%
  filter(!(rec_id %in% india_contact.$rec_id)) %>%
  filter(study_site == study_site.) 


locations <- levels(india_mix.site$contact_location)


## Total number of contacts over two days
contact_count <- 
india_mix.site %>%
   group_by(rec_id, contact_location, fromdayone, .drop = F)%>% summarise(n_contacts = n()) %>% # summarizing number of contacts by type
  ungroup() %>% 
  mutate(
    n_contacts = case_when(
    contact_location %in% c("Home", "Work","School") ~ n_contacts, # for these layers, a replicated contact is counted as unique contact
    contact_location %in% c("Nonhome" ) & fromdayone == "Both days" ~ n_contacts*2, # for non-home layer, a replicated contact is counted as two contact
    contact_location %in% c("Nonhome" ) & fromdayone %in% c("Day 1", "Day 2") ~ n_contacts, # for non-home layer, a unique contact is counted as one contact
    T ~ n_contacts # for observation with fromdayone information missed, we return the original n_contacts
    )  
    )%>% 
  group_by(rec_id, contact_location, .drop = F) %>% summarise(n_contacts = sum(n_contacts)
                                                          ) %>% ungroup() %>% # total number of contacts over two days
   # add the participants w/o contact to the data
  rbind(., 
        data.frame(
          rec_id = rep(as.character(id_no_contact.site$rec_id), each = length(locations)),
          contact_location= rep(locations, 
                                nrow(id_no_contact.site)
                                ),
          n_contacts=rep(0,  nrow(id_no_contact.site)*length(locations))
        )
  ) %>% 
  # joining w/ participant's age
  left_join(india_participant. %>% select(rec_id, participant_age),
            by = "rec_id"
            )

## Number of contacts of the same age group, individual-level
same.age.grp_count <- 
india_mix.site %>% 
  mutate(same.age.grp = ifelse(participant_age == contact_age, 1, 0)
         
           ) %>% 
 mutate(
   # adjusting replicated contacts
    same.age.grp_1 = case_when(
    contact_location %in% c("Home", "Work","School") ~  same.age.grp, # for these layers, a replicated contact is counted as unique contact
    contact_location %in% c("Nonhome" ) & fromdayone == "Both days" ~ same.age.grp*2, # for non-home layer, a replicated contact is counted as two contact
    contact_location %in% c("Nonhome" ) & fromdayone %in% c("Day 1", "Day 2") ~ same.age.grp, # for non-home layer, a unique contact is counted as one contact
    T ~ same.age.grp # for observation with fromdayone information missed, we return the original same.age.grp
    )  
    ) %>%
  select(rec_id,  contact_location, same.age.grp_1,  contact_age) %>% 
  rbind(., 
        data.frame(
          rec_id = rep(as.character(id_no_contact.site$rec_id), each = length(locations)),
          contact_location= rep(locations, 
                                nrow(id_no_contact.site)
                                ),
           same.age.grp_1=rep(0,  nrow(id_no_contact.site)*length(locations)),
          contact_age =NA
        )
        )%>% 
  # joining w/ participant's age
  left_join(india_participant. %>% select(rec_id, participant_age),
            by = "rec_id"
            ) 

 # Replicate each observation/row w/ same.age.grp_1 = 2 twice and recode same.age.grp_1 to 1; for observations w/ same.age.grp_1 = 1/0, we treat them as-is
same.age.grp_count <-  
same.age.grp_count %>% filter(same.age.grp_1==2) %>% slice(rep(1:n(), each = 2)) %>% mutate(same.age.grp_1=1) %>% 
   rbind(., same.age.grp_count %>% filter(same.age.grp_1 !=2)
         )


  
 out <-list(contact_count, same.age.grp_count); names(out) <- c("contact_count", "sameage.grp.count")
  
  out



}

contact_count_rural <- # rural mixing
contact_freq_site(india_mix. = india_mix, 
           india_participant. = india_participant, 
           india_contact. = india_contact,
           study_site. ="Rural") 


contact_count_urban  <- # urban mixing
contact_freq_site(india_mix. = india_mix , 
           india_participant. = india_participant, 
           
           india_contact. = india_contact,
           study_site. ="Urban") 

# Function characterizing network statistics
network_stats <- function(contact_count_site){

  output <- list()
  
## Edges 
fit_edge <- 
  contact_count_site$contact_count %>% 
  glm(n_contacts~ -1+contact_location, data=., family = poisson) %>% summary() # coefficient for two-day contact rate

fit_edge <- fit_edge$coefficients%>% as.data.frame()  # the two is averaging two-day's contact rate to one-day

n_participants_site <- 
contact_count_site$contact_count$rec_id %>% unique() %>% length()  # number of participants
 
fit_edge <- 
fit_edge %>% 
            mutate(
              # single-day mean degree, original scale
              single_day_md = exp(Estimate)/2,
              
              # calculation, log-link scale
              two_day_sd_link = `Std. Error`*sqrt(n_participants_site), # two-day standard deviation for the coefficient at the log scale
              single_day_sd_link = two_day_sd_link/2,  # single-day standard deviation for the coefficient at the log scale
              single_day_se_link = single_day_sd_link/sqrt(n_participants_site), # single-day standard error for the coefficient at the log scale
              single_day_md_link = log(single_day_md),
              
               # uncertainties, original scale
              single_day_lower95ci = exp(single_day_md_link -1.96*single_day_se_link),
              single_day_upper95ci =  exp(single_day_md_link +1.96*single_day_se_link)
                    ) %>% select(single_day_md, single_day_lower95ci, single_day_upper95ci
                                 )



output[[1]] <- fit_edge %>% rownames_to_column(var="contact_location") %>%
  mutate(contact_location=str_remove(contact_location, "contact_location")
         )


## nodefactor age.grp

n_participants_nf_site <- # number of participants in each age.grp
contact_count_site$contact_count %>% group_by( participant_age) %>% 
  summarize(n_participants_nf_site = n_distinct(rec_id)) %>% mutate(participant_age = as.character(participant_age))

nf <- data.frame() #matrix(NA, nrow = length(locations), ncol = length(levels(contact_count$participant_age)))
for (i in 1:4 #length(locations)
     ) {
  fit_nf_single <- 
  contact_count_site$contact_count %>% filter(contact_location == levels(contact_count_site$contact_count$contact_location)[i]) %>% 
  glm(n_contacts~ -1+participant_age, data=., family = poisson) %>% summary() # coefficients for two-day contact rate
  
  fit_nf_single <- fit_nf_single$coefficients %>% as.data.frame()
  
  fit_nf_single <-
  fit_nf_single%>% rownames_to_column() %>% 
    rename(participant_age=1) %>% mutate(participant_age= str_remove(participant_age, "participant_age") 
                                 ) %>% 
    left_join(
      n_participants_nf_site
    )
  
  fit_nf_single <- 
  fit_nf_single %>% 
            mutate(
              # single-day mean degree, original scale
              single_day_nf_md = exp(Estimate)/2,
              
              # calculation, log-link scale
              two_day_nf_sd_link = `Std. Error`*sqrt(n_participants_nf_site), # two-day standard deviation for the coefficient at the log scale
              single_day_nf_sd_link = two_day_nf_sd_link/2,  # single-day standard deviation for the coefficient at the log scale
              single_day_nf_se_link = single_day_nf_sd_link/sqrt(n_participants_nf_site), # single-day standard error for the coefficient at the log scale
              single_day_nf_md_link = log(single_day_nf_md), # single-day mean degree, log scale
              
               # uncertainties, original scale
              single_day_nf_lower95ci = exp(single_day_nf_md_link -1.96*single_day_nf_se_link),
              single_day_nf_upper95ci =  exp(single_day_nf_md_link +1.96*single_day_nf_se_link)
                    ) %>% select(participant_age, single_day_nf_md, single_day_nf_lower95ci, single_day_nf_upper95ci
                                 ) %>% 
           mutate(contact_location = levels(contact_count_site$contact_count$contact_location)[i]) # specify layer

  
  
  
  
  nf <- 
  rbind(nf, fit_nf_single)

}

# relative degree frequency of each age group
nf <- nf %>% group_by( contact_location) %>% 
  mutate(single_day_nf_md_prop = single_day_nf_md/sum(single_day_nf_md)) %>% 
  ungroup()

output[[2]] <- nf




### average matched degree across age groups
expit <- function(x){exp(x)/(1+exp(x))}; logit <- function(x){log(x/(1-x))}

nm <- data.frame() #matrix(NA, nrow = length(locations), ncol = length(levels(contact_count$participant_age)))
for (i in 1:4 #length(locations)
     ) {
  
 
  data_nm <- 
  contact_count_site$sameage.grp.count %>% filter(contact_location == levels(contact_count_site$sameage.grp.count$contact_location)[i]) 
    
  n_obs_age.grp <- data_nm %>% group_by(participant_age) %>% summarize(n=n()) %>% mutate(participant_age = as.character(participant_age)
                                                                                         )
  
    
  fit_nm_single <- 
    data_nm %>% 
  glm(same.age.grp_1 ~ -1+ participant_age,
               data = ., family = "binomial"
              )  %>% summary() # coefficients for two-day contact rate
  
  fit_nm_single <- fit_nm_single$coefficients %>% as.data.frame()
  
  fit_nm_single <-
  fit_nm_single%>% rownames_to_column() %>% 
    rename(participant_age=1) %>% mutate(participant_age= str_remove(participant_age, "participant_age") 
                                 ) %>% 
    left_join(
      n_obs_age.grp
    )
  
  fit_nm_single <- 
  fit_nm_single %>% 
            mutate(
              # single-day mean degree, original scale
              single_day_nm_md = expit(Estimate)/2,
              
              # calculation, logit-link scale
              two_day_nm_sd_link = `Std. Error`*sqrt(n), # two-day standard deviation for the coefficient at the logit scale. HEre should be updated
              single_day_nm_sd_link = two_day_nm_sd_link/2,  # single-day standard deviation for the coefficient at the logit scale
              single_day_nm_se_link = single_day_nm_sd_link/sqrt(n), # single-day standard error for the coefficient at the logit scale
              single_day_nm_md_link = logit(single_day_nm_md), # single-day mean degree, logit scale
              
               # uncertainties, original scale
              single_day_nm_lower95ci = expit(single_day_nm_md_link -1.96*single_day_nm_se_link),
              single_day_nm_upper95ci =  expit(single_day_nm_md_link +1.96*single_day_nm_se_link)
                    ) %>% select(participant_age, single_day_nm_md, single_day_nm_lower95ci, single_day_nm_upper95ci
                                 ) %>% 
           mutate(contact_location = levels(contact_count_site$contact_count$contact_location)[i]) # specify layer
  
  nm <- 
  rbind(nm, fit_nm_single)

}

output[[3]] <- nm

names(output) <- c("edge", "nf.age.grp", "nm.age.grp")

output
}

network_stats_rural <- network_stats(contact_count_site = contact_count_rural)

network_stats_urban <- network_stats(contact_count_site = contact_count_urban)


network_stats <- 
list(network_stats_rural, network_stats_urban)
names(network_stats) <- c("rural", "urban")

saveRDS(network_stats, file = "~/Documents/GitHub/COVID-GlobalMix/data/network_params/formation_stats.RData")


```

## Contact durations
```{r}

know_dur <- function(india_mix.){
  
known_dur_gt_10yr <- india_mix. %>% filter(known_contact == ">10 yrs" & contact_location %in% c( "School", "Work" )
                                  ) %>%
    mutate(known_duration = (participant_ageyr - 10)/2) 
#known_dur_gt_10yr %>% filter(known_duration<0) # participants w/ age < contact duration, discuss w/ Sam

known_dur_gt_10yr <- 
known_dur_gt_10yr %>% 
  group_by(study_site, contact_location) %>% 
  summarize(known_contact_avg = mean(known_duration)*365) %>% ungroup()

known_duration <-
india_mix. %>% 
  filter(contact_location %in% c("School", "Work")) %>% 
  group_by(study_site, contact_location, frequency_contact, known_contact) %>% 
  tally() %>% 
  spread(frequency_contact,n) %>% data.frame() %>% rename(daily = Daily..almost.daily) %>% 
  select(study_site, contact_location, known_contact, daily ) %>% 
  filter(!is.na(known_contact)) %>% # filter out the empty category
  ungroup() %>% 
  # characterize mid point for known duration for categories except >10yrs
    mutate(know_contact_d = # median duration in days
           case_when(known_contact=="Never met before" ~0, 
                     known_contact=="<1 yr" ~182, # mid. point
                     known_contact=="1-2 yrs" ~ 548,# mid. point
                     known_contact=="3-5 yrs" ~ 1460,# mid. point
                     known_contact=="6-10 yrs" ~ 2922,# mid. point
                     # avg. midpoint of knowing the contacts, based on participant's age, for those having know the contacts for > 10yrs
                     known_contact==">10 yrs" & study_site == "Rural" & contact_location == "School" ~ 
                       known_dur_gt_10yr %>% filter( study_site == "Rural" & contact_location == "School") %>% 
                       select(known_contact_avg) %>% as.numeric(),
                      known_contact==">10 yrs" & study_site == "Rural" & contact_location == "Work" ~ 
                       known_dur_gt_10yr %>% filter( study_site == "Rural" & contact_location == "Work") %>% 
                       select(known_contact_avg) %>% as.numeric(),
                      known_contact==">10 yrs" & study_site == "Urban" & contact_location == "School" ~ 
                       known_dur_gt_10yr %>% filter( study_site == "Urban" & contact_location == "School") %>% 
                       select(known_contact_avg) %>% as.numeric(),
                      known_contact==">10 yrs" & study_site == "Urban" & contact_location == "Work" ~ 
                       known_dur_gt_10yr %>% filter( study_site == "Urban" & contact_location == "Work") %>% 
                       select(known_contact_avg) %>% as.numeric(),
                     )
           ) %>% 
  group_by(study_site, contact_location) %>% 
  mutate(
     daily_prop = daily/sum(daily, na.rm = T), # proportion of daily contact,
     weighted_known_contact_d = know_contact_d*daily_prop
  ) %>%   # The script until here create a data frame of the midpoint of known duration of contact and daily proportion
  summarize(know_contact_duration_avg = sum(weighted_known_contact_d, na.rm = T)
            ) %>% ungroup()
  
}
known_duration <- know_dur(india_mix. = india_mix)

saveRDS(known_duration, file = "~/Documents/GitHub/COVID-GlobalMix/data/network_params/known_dur_school_work.RData")

# Association between layer and household status
## Moses indicates that frequency_contact and known_contact were only surveyed for non-household contacts from participants. We check whether there are HH member having contact at school/work. There are 4 school/work contact and 58 nonhome of household members. Of these non-home (school, work, other non-home) contacts that are of household members, Billy thinks they can be re-classified as home contact.
table(
india_mix$contact_location,
india_mix$hh_membership
)

india_mix %>% select(contact_location, hh_membership)


```

## Correlation between layers

```{r}
# rural
library(GGally)

 
# individual-level contact count at different locations by row
## data to wide format 
 contact_count_wide_rural  <- 
contact_count_rural$contact_count %>% data.frame()%>% 
  tidyr::pivot_wider(names_from = "contact_location", values_from = "n_contacts"
                     ) %>%  # 608 rows, each row for a participant
  as.data.frame()
 
 # urban
## data to wide format 
 contact_count_wide_urban  <- 
contact_count_urban$contact_count %>% data.frame()%>% 
  tidyr::pivot_wider(names_from = "contact_location", values_from = "n_contacts"
                     ) %>%  # 608 rows, each row for a participant
  as.data.frame()


## pearson correlation,rural
contact_count_wide_rural %>% select(-c(rec_id, participant_age)) %>% ggpairs(upper = list(continuous = wrap("cor", method = "spearman")))

## pearson correlation,urban
contact_count_wide_urban %>% select(-c(rec_id, participant_age)) %>% ggpairs(upper = list(continuous = wrap("cor", method = "spearman")))

```
With the degree distribution, the degree can be categorized into the categories of 0, 1-2, 3-5, and 6+.

```{r}
# Create degree category
contact_count_wide_rural <- 
contact_count_wide_rural %>% mutate(
  Nonhome_cat = case_when(Nonhome==0 ~ "0",
                          Nonhome %in% c(1:2) ~ "1-2",
                          Nonhome %in% c(3:5) ~ "3-5",
                          Nonhome >=6 ~ "6+"),
  Nonhome_cat = factor( Nonhome_cat)
)


# Effect of non-home contact on home 
glm_h_nh <- 
contact_count_wide_rural %>% 
  glm(Home~ -1+ Nonhome, data=., family = poisson(link=log))
glm_h_nh %>% summary()

barplot(contact_count_wide_rural$Nonhome_cat, log(contact_count_wide_rural$Home))
mean(contact_count_wide_rural$Home); var(contact_count_wide_rural$Home) # overdisperson exist in the outcome


# Home ~ Work
# Home ~ School
# Home ~ Nonhome + school + work
 
 # 20230927 still couldn't get head around this.


```

