---
title: "Descriptive Degree Summary of GlobalMix India Data"
author: "Billy Dehao Chen"
date: "09/25/2023"
output:
  html_document: default
  word_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

# Background
This is a descriptive summary of contact degree of the India GlobalMix diary data.

# Method
There are two ways to derive target statistics for ERGM, one is using poisson model based on individual-count data, the other is based on the symmetric contact matrix, the approach for Corporate Mix. Given the symmetric contact matrix may not account for the difference of distributions between the study and target populations, we go with the glm-based approach to calculate the summary network statistics. We regrouped the age categories in the first two decades of life by decade. We excluded contacts lasted ≤ 15 mins in analysis. The degree information was summarized as the arithmetic mean of signle-day degrees of contact between group A and group B and between group B and group A of the two-day visits. Given the data were egocentric, we use $M.D.=\frac{edges}{n}$ for the relationship between mean degree ($M.D.$) and the number of edges.
Characterization of network layers: The network layers is processed from multiple questions asking contact locations. Given these questions are not mutually exclusive due to the check-box design in REDCap, we characterized contact location as the location having primary contact follow the order of home, school, work, non-home (excluding work and school). There are two contacts that occurred at both work (location 3 in REDCap) and school (location 2), we categorized them as at school, considering the participants (and contacts) were at school age (10-19y, 0-9y). This logic is not spelled out in the below script but is adjusted by the higher priority of school than work. For a contact checked non of the categories, we assigned an NA to this contact and excluded them considering them as missing data.


```{r, echo=F, warning=F, message=FALSE, include = FALSE}
setwd("~/Documents/GitHub/COVID-GlobalMix")

# Load libraries and data  ------------------------------------------------
lapply(c("ggpubr", "statnet", "EpiModel", "tidyverse", "socialmixr", "knitr",  "sjlabelled", "kableExtra", "broom", "stringr", "GGally"), require, character.only = TRUE)


## participant data
india_participant <- 
readRDS("~/Documents/GitHub/COVID-GlobalMix/data/participant_contact/india_participant_data_aim1.RDS")



## contact data 
india_contact <- 
 readRDS("~/Documents/GitHub/COVID-GlobalMix/data/participant_contact/india_contact_data_aim1.RDS")
#readRDS("../Documents/GitHub/COVID-GlobalMix/data/participant_contact/india_contact_data_aim1.RDS")

# Note - validated study_site of participant is exactly the same as those in contact

# Reclassifying participant's and contact's age groups into 0-9 years old, 10-19 years old, while treating other age groups as is.
## participant data
india_participant <- 
india_participant %>% 
  mutate(
      participant_age = case_when(
        participant_age %in% c("<6mo", "6-11mo",   "1-4y",   "5-9y") ~ "0-9y",
        participant_age %in% c("10-14y", "15-19y") ~ "10-19y",
        .default =  participant_age
      )
    )%>% 
  mutate(participant_age= factor(participant_age, levels=c("0-9y", "10-19y", "20-29y", "30-39y", "40-59y",   "60+y")
                                         )
         ) %>% mutate(participant_ageyr = floor(participant_ageyr)
                      )

## contact data
india_contact <- 
india_contact %>%     
  mutate(
      contact_age = case_when(
        contact_age %in% c("<6mo", "6-11mo",   "1-4y",   "5-9y") ~ "0-9y",
        contact_age %in% c("10-14y", "15-19y") ~ "10-19y",
        .default =  contact_age
      )
    )%>% 
    mutate(contact_age= factor(contact_age, levels=c("0-9y", "10-19y", "20-29y", "30-39y", "40-59y",   "60+y")
                                         )
         )

# merge participants and contact datasets and process data  and basic data processing ------------------------------------------------
india_mix <- india_participant %>%
  dplyr::select(rec_id,participant_age, participant_ageyr) %>%
  right_join(india_contact,
            by = "rec_id") %>% 
  # characterization of home/nonhome status
   mutate(contact_location = case_when(location_contact___0 == 1  ~ "Home", # 0 - "My home"
                                            location_contact___2 == 1 & location_contact___0 == 0 ~ "School", # "School" but not "my home" 
                                             location_contact___3 == 1 & (location_contact___0 == 0  | location_contact___2 ==0)~ "Work", # "work" but not "my home" / "school"
                                       
                                       
                                       (
                                       location_contact___1 == 1 | location_contact___4 == 1 | # "Other home",  "Transport/Hub"
                                       location_contact___5 == 1 | location_contact___6 == 1 | # "Market/Shop", "Street"
                                       location_contact___7 == 1 | location_contact___8 == 1 | # "Playground", "Well"
                                       location_contact___9 == 1 | location_contact___10 == 1 | # "Agricultural Field", "Market/Shop"
                                       location_contact___11 == 1 | location_contact___12 == 1 | # "Restaurant", "Religious centre"
                                       location_contact___13 == 1 | location_contact___14 == 1 | # "Govt offices", "Health center"
                                       location_contact___15 == 1 | location_contact___16 == 1 | # "Bank", "Movie theatre"
                                       location_contact___17 == 1 | location_contact___18 == 1 | location_contact___19 == 1 #"Exhibition", "Social hall", "Other"
                                       ) &
                                         !(location_contact___3 == 1 | location_contact___2 == 1 | location_contact___0 == 1) # Excluding work/school/home
                                       
                                       ~ "Nonhome") # "Nonhome" but not "home", "school", "work"
         )  %>% 
   ## Weighing in household membership in determining contact location - tabulating contact_location and hh_membership, we found there are 58,1,3 household member contacts in the nonhome, school, and work layers. We reclassify these as home contacts. We also found 2176 non-members at the home layer, and we reclassify them into non-home (other than school, work) contacts given the presumed turnover rate for this group is short. 
  mutate(
    contact_location = case_when(hh_membership == "Member" & contact_location %in% c("Nonhome", "School", "Work") ~ "Home",
                                 hh_membership == "Non-member" & contact_location %in% c("Home") ~ "Nonhome",
                                 T ~ contact_location
                                 )

  ) %>%
  mutate(contact_location = factor(contact_location,
                                    ordered = TRUE)
         ) %>% 
  filter(!(duration_contact %in% c("<5 mins", "5-15 mins"))) %>% # filter out contact with duration ≤ 15 mins
  mutate(
         duration_contact = factor(duration_contact,
                                    levels = c( "16-30 mins",  "31 mins-1 hr", "1-4 hrs", ">4 hrs", "Unknown"),
                                    ordered = TRUE)
         )  %>% filter(!is.na(contact_location) # complete-case analysis - exclude contacts didn't have a contact location from analysis, Moses confirmed this is okay
                      ) %>% 

## Distribution of indoor/outdoor status
# We the break down of the observed categories of the variable "where_contact" indicating in- and out-door status. In the original data, there is a "Both" category indicates a participant contacted a contact both in- and out-doors. Since the "Both" category could have a higher transmission potential similar to the "Indoors" category, we merge the "Both" and the "Indoors" categories. We will adjust for this status as a nodefactor. For building the transmission model, we will assign lower risk for the "Outdoors" category during simulation.
   mutate(where_contact =case_when(where_contact %in% c("Indoors", "Both") ~ "Indoors_or_both",
                                              .default = where_contact)
                     )



## Check implementation of the cross-checking between household membership and contact location
table(
india_mix$contact_location,
india_mix$hh_membership
)


```


## Uncertainties of network statistics

```{r}

# Function characterizing number of contact at the individual-level (outputted in "contact_count") and the status of if a participant and contact was in the same age group (outputted in "sameage.grp.count") for the contact data
contact_freq_site <- function(india_mix., india_participant., india_contact., study_site.){
india_mix.site <- 
 india_mix.  %>% 
  filter(study_site == study_site.) # here we split the dataset into urban or rural samples


id_no_contact.site <- # participants with 0 contacts by study site in India
  india_participant. %>%
  filter(!(rec_id %in% india_contact.$rec_id)) %>%
  filter(study_site == study_site.) 


locations <- levels(india_mix.site$contact_location) # retrieve the full levels of contact locations


#### Total number of contacts over two days, for ~ edge and nodefactor ####
contact_count <- 
india_mix.site %>%
   group_by(rec_id, contact_location, fromdayone, .drop = F)%>% summarise(n_contacts = n()) %>% # summarizing number of contacts by characteristics included in "group_by"
  ungroup() %>% 
  mutate(
    n_contacts = case_when(
    contact_location %in% c("Home", "Work","School") ~ n_contacts, # for these layers, a replicated contact is counted as unique contact
    contact_location %in% c("Nonhome" ) & fromdayone == "Both days" ~ n_contacts*2, # for non-home layer, a replicated contact is counted as two contact
    contact_location %in% c("Nonhome" ) & fromdayone %in% c("Day 1", "Day 2") ~ n_contacts, # for non-home layer, a unique contact is counted as one contact
    T ~ n_contacts # for observation with fromdayone information missed, we return the original n_contacts
    )  
    )%>% 
  group_by(rec_id, contact_location, .drop = F) %>% summarise(n_contacts = sum(n_contacts)
                                                          ) %>% ungroup() %>% # total number of contacts over two days
   # add the participants w/o contact to the data
  rbind(., 
        data.frame(
          rec_id = rep(as.character(id_no_contact.site$rec_id), each = length(locations)),
          contact_location= rep(locations, 
                                nrow(id_no_contact.site)
                                ),
          n_contacts=rep(0,  nrow(id_no_contact.site)*length(locations))
        )
  ) %>% 
  # joining w/ participant's age
  left_join(india_participant. %>% select(rec_id, participant_age),
            by = "rec_id"
            )

#### Number of contacts of the same age group, individual-level, for nodematch ####
same.age.grp_degree <- 
india_mix.site %>% 
  mutate(same.age.grp = ifelse(participant_age == contact_age, 1, 0)
         
           ) %>% 
 mutate(
   # adjusting replicated contacts
    same.age.grp = case_when(
    contact_location %in% c("Home", "Work","School") ~  same.age.grp, # for these layers, a replicated contact is counted as unique contact
    contact_location %in% c("Nonhome" ) & fromdayone == "Both days" ~ same.age.grp*2, # for non-home layer, a replicated contact is counted as two contact
    contact_location %in% c("Nonhome" ) & fromdayone %in% c("Day 1", "Day 2") ~ same.age.grp, # for non-home layer, a unique contact is counted as one contact
    T ~ same.age.grp # for observation with fromdayone information missed, we return the original same.age.grp
    )  
    ) %>%
  select(rec_id,  contact_location, participant_age, contact_age, same.age.grp
         )
  # Given nodematch is defined at the edge, I think the following code with 0 contact (i.e., w/o edge) don't need to be accounted
  # rbind(., 
  #       data.frame(
  #         rec_id = rep(as.character(id_no_contact.site$rec_id), each = length(locations)),
  #         contact_location= rep(locations, 
  #                               nrow(id_no_contact.site)
  #                               ),
  #          same.age.grp=rep(0,  nrow(id_no_contact.site)*length(locations)),
  #         contact_age =NA
  #       )
  #       )%>%

 # Replicate each observation/row w/ same.age.grp == 2 twice and recode these observations' same.age.grp to 1; for observations w/ same.age.grp = 1/0, we treat them as-is
same.age.grp_degree <- 
  same.age.grp_degree %>% filter(same.age.grp==2) %>% slice(rep(1:n(), each = 2)) %>% mutate(same.age.grp=1) %>% 
    rbind(., same.age.grp_degree %>% filter(same.age.grp !=2)
          ) 


#### Status of whether one group matched to another, for nodemix ####
age.grp_mix <- 
india_mix.site %>% 
  # select subset of variables for ouput
  select(rec_id, contact_location, participant_age, contact_age, fromdayone) %>% 
  
  # The following levels are used to code the age groups "0-9y"~1, "10-19y"~2, "20-29y"~3, "30-39y"~4, "40-59y"~5, "60+y"~6  
  mutate(age.grp1_1 = ifelse(participant_age == "0-9y" & contact_age ==  "0-9y", 1, 0),
         age.grp1_2 = ifelse(participant_age == "0-9y" & contact_age ==  "10-19y", 1, 0),
         age.grp1_3 = ifelse(participant_age == "0-9y" & contact_age ==  "20-29y" , 1, 0),
         age.grp1_4 = ifelse(participant_age == "0-9y" & contact_age ==  "30-39y" , 1, 0),
         age.grp1_5 = ifelse(participant_age == "0-9y" & contact_age ==  "40-59y", 1, 0),
         age.grp1_6 = ifelse(participant_age == "0-9y" & contact_age ==  "60+y", 1, 0),
         
         age.grp2_1 = ifelse(participant_age == "10-19y" & contact_age ==  "0-9y", 1, 0),
         age.grp2_2 = ifelse(participant_age == "10-19y" & contact_age ==  "10-19y", 1, 0),
         age.grp2_3 = ifelse(participant_age == "10-19y" & contact_age ==  "20-29y" , 1, 0),
         age.grp2_4 = ifelse(participant_age == "10-19y" & contact_age ==  "30-39y" , 1, 0),
         age.grp2_5 = ifelse(participant_age == "10-19y" & contact_age ==  "40-59y", 1, 0),
         age.grp2_6 = ifelse(participant_age == "10-19y" & contact_age ==  "60+y", 1, 0),
         
         age.grp3_1 = ifelse(participant_age == "20-29y" & contact_age ==  "0-9y", 1, 0),
         age.grp3_2 = ifelse(participant_age == "20-29y" & contact_age ==  "10-19y", 1, 0),
         age.grp3_3 = ifelse(participant_age == "20-29y" & contact_age ==  "20-29y" , 1, 0),
         age.grp3_4 = ifelse(participant_age == "20-29y" & contact_age ==  "30-39y" , 1, 0),
         age.grp3_5 = ifelse(participant_age == "20-29y" & contact_age ==  "40-59y", 1, 0),
         age.grp3_6 = ifelse(participant_age == "20-29y" & contact_age ==  "60+y", 1, 0),
         
         age.grp4_1 = ifelse(participant_age == "30-39y" & contact_age ==  "0-9y", 1, 0),
         age.grp4_2 = ifelse(participant_age == "30-39y" & contact_age ==  "10-19y", 1, 0),
         age.grp4_3 = ifelse(participant_age == "30-39y" & contact_age ==  "20-29y" , 1, 0),
         age.grp4_4 = ifelse(participant_age == "30-39y" & contact_age ==  "30-39y" , 1, 0),
         age.grp4_5 = ifelse(participant_age == "30-39y" & contact_age ==  "40-59y", 1, 0),
         age.grp4_6 = ifelse(participant_age == "30-39y" & contact_age ==  "60+y", 1, 0),
         
         age.grp5_1 = ifelse(participant_age == "40-59y" & contact_age ==  "0-9y", 1, 0),
         age.grp5_2 = ifelse(participant_age == "40-59y" & contact_age ==  "10-19y", 1, 0),
         age.grp5_3 = ifelse(participant_age == "40-59y" & contact_age ==  "20-29y" , 1, 0),
         age.grp5_4 = ifelse(participant_age == "40-59y" & contact_age ==  "30-39y" , 1, 0),
         age.grp5_5 = ifelse(participant_age == "40-59y" & contact_age ==  "40-59y", 1, 0),
         age.grp5_6 = ifelse(participant_age == "40-59y" & contact_age ==  "60+y", 1, 0),
         
         age.grp6_1 = ifelse(participant_age == "60+y"  & contact_age ==  "0-9y", 1, 0),
         age.grp6_2 = ifelse(participant_age == "60+y"  & contact_age ==  "10-19y", 1, 0),
         age.grp6_3 = ifelse(participant_age == "60+y"  & contact_age ==  "20-29y" , 1, 0),
         age.grp6_4 = ifelse(participant_age == "60+y"  & contact_age ==  "30-39y" , 1, 0),
         age.grp6_5 = ifelse(participant_age == "60+y"  & contact_age ==  "40-59y", 1, 0),
         age.grp6_6 = ifelse(participant_age == "60+y"  & contact_age ==  "60+y", 1, 0)
         
           ) %>% 
 mutate(
   # adjusting replicated contacts
    across(
      c(age.grp1_1:age.grp6_6),
      ~case_when(
    contact_location %in% c("Home", "Work","School") ~  ., # for these layers, a replicated contact is counted as unique contact
    contact_location %in% c("Nonhome" ) & fromdayone == "Both days" ~ .*2, # for non-home layer, a replicated contact is counted as two contact
    contact_location %in% c("Nonhome" ) & fromdayone %in% c("Day 1", "Day 2") ~ ., # for non-home layer, a unique contact is counted as one contact
    T ~ . # for observation with fromdayone information missed, we return the original data
    )  )
    )
# for each mixing, we replicate with contact with count == 2 into two rows and save each mixing as a component in list
age.grp_mix_degree <- list()

  for (i in 6:ncol(age.grp_mix)
       ) {
    age.grp_single_mix <- 
      age.grp_mix%>% select(rec_id:fromdayone, all_of(i)) %>% 
      rename(mix_count =ncol(.) # give a temporal col name to facilitate data manipulation
             )  
     # Replicate each observation/row w/ mix_count == 2 twice and recode these observations' mix_count to 1; for observations w/ mix_count = 1/0, we treat them as-is
  age.grp_single_mix <- 
    age.grp_single_mix %>% 
  filter(mix_count==2) %>% slice(rep(1:n(), each = 2)) %>% mutate(mix_count=1) %>%
   rbind(., age.grp_single_mix %>% filter(mix_count !=2)
         ) 
  
  colnames(age.grp_single_mix)[length(colnames(age.grp_single_mix))] <- colnames(age.grp_mix)[i] # rename col back to its original name
  
  age.grp_mix_degree[[i-5]] <- age.grp_single_mix %>% select(-fromdayone)
  }

names(age.grp_mix_degree)<- colnames(age.grp_mix %>% select(age.grp1_1:age.grp6_6)) # adding mixing as name to the list
    
   
 out <-list(contact_count, same.age.grp_degree#, age.grp_mix_degree
            );
 names(out) <- c("contact_degree", "same.age.grp_degree" #, "age.grp_mix_degree"
                 )
  
  out

}

contact_count_rural <- # rural mixing
contact_freq_site(india_mix. = india_mix, 
           india_participant. = india_participant, 
           india_contact. = india_contact,
           study_site. ="Rural") 



contact_count_urban  <- # urban mixing
contact_freq_site(india_mix. = india_mix , 
           india_participant. = india_participant, 
           
           india_contact. = india_contact,
           study_site. ="Urban") 

# Function characterizing network statistics
# 20231019 reach here - think how to characterize md for nodemmix - averaging the two direction?
network_stats <- function(contact_count_site){

  output <- list()
  
# Edges 
fit_edge <- 
  contact_count_site$contact_degree %>% 
  glm(n_contacts~ -1+contact_location, data=., family = poisson) %>% summary() # coefficient for two-day contact rate

fit_edge <- fit_edge$coefficients%>% as.data.frame()  # the two is averaging two-day's contact rate to one-day

n_participants_site <- 
contact_count_site$contact_degree$rec_id %>% unique() %>% length()  # number of participants of a network
 
fit_edge <- 
fit_edge %>% 
            mutate(
              # single-day mean degree, original scale
              single_day_md = exp(Estimate)/2,
              
              # calculation, log-link scale
              two_day_sd_link = `Std. Error`*sqrt(n_participants_site), # two-day standard deviation for the coefficient at the log scale
              single_day_sd_link = two_day_sd_link/2,  # single-day standard deviation for the coefficient at the log scale
              single_day_se_link = single_day_sd_link/sqrt(n_participants_site), # single-day standard error for the coefficient at the log scale
              single_day_md_link = log(single_day_md),
              
               # uncertainties, original scale
              single_day_lower95ci = exp(single_day_md_link -1.96*single_day_se_link),
              single_day_upper95ci =  exp(single_day_md_link +1.96*single_day_se_link)
                    ) %>% select(single_day_md, single_day_lower95ci, single_day_upper95ci
                                 )



output[[1]] <- fit_edge %>% rownames_to_column(var="contact_location") %>%
  mutate(contact_location=str_remove(contact_location, "contact_location")
         )


# nodefactor - age.grp
n_participants_nf_site <- # number of participants in each age.grp in a network
contact_count_site$contact_degree %>% group_by( participant_age) %>% 
  summarize(n_participants_nf_site = n_distinct(rec_id)) %>% mutate(participant_age = as.character(participant_age))

nf <- data.frame() 
for (i in 1:4 # characterize mean degree and uncertainties for each layer
     ) {
  fit_nf_single <- 
  contact_count_site$contact_degree %>% filter(contact_location == levels(contact_count_site$contact_degree$contact_location)[i]) %>% 
  glm(n_contacts~ -1+participant_age, data=., family = poisson) %>% summary() # coefficients for two-day contact rate
  
  fit_nf_single <- fit_nf_single$coefficients %>% as.data.frame()
  
  fit_nf_single <-
  fit_nf_single%>% rownames_to_column() %>% 
    rename(participant_age=1) %>% mutate(participant_age= str_remove(participant_age, "participant_age") 
                                 ) %>% 
    left_join(
      n_participants_nf_site
    )
  
  fit_nf_single <- 
  fit_nf_single %>% 
            mutate(
              # single-day mean degree, original scale
              single_day_nf_md = exp(Estimate)/2,
              
              # calculation, log-link scale
              two_day_nf_sd_link = `Std. Error`*sqrt(n_participants_nf_site), # two-day standard deviation for the coefficient at the log scale
              single_day_nf_sd_link = two_day_nf_sd_link/2,  # single-day standard deviation for the coefficient at the log scale
              single_day_nf_se_link = single_day_nf_sd_link/sqrt(n_participants_nf_site), # single-day standard error for the coefficient at the log scale
              single_day_nf_md_link = log(single_day_nf_md), # single-day mean degree, log scale
              
               # uncertainties, original scale
              single_day_nf_lower95ci = exp(single_day_nf_md_link -1.96*single_day_nf_se_link),
              single_day_nf_upper95ci =  exp(single_day_nf_md_link +1.96*single_day_nf_se_link)
                    ) %>% select(participant_age, single_day_nf_md, single_day_nf_lower95ci, single_day_nf_upper95ci
                                 ) %>% 
           mutate(contact_location = levels(contact_count_site$contact_degree$contact_location)[i]) # specify layer

  
  
  
  
  nf <- 
  rbind(nf, fit_nf_single)

}


output[[2]] <- nf


# nodematch - porportion of matched edges of each age group among all the edges
expit <- function(x){exp(x)/(1+exp(x))}; logit <- function(x){log(x/(1-x))}

nm <- data.frame() #matrix(NA, nrow = length(locations), ncol = length(levels(contact_count$participant_age)))
for (i in 1:4 #length(locations)
     ) {
  
 
  data_nm <- 
  contact_count_site$same.age.grp_degree %>% filter(contact_location == levels(contact_count_site$same.age.grp_degree$contact_location)[i]) 
    
  n_obs_age.grp <- data_nm %>% group_by(participant_age) %>% summarize(n=n()) %>% mutate(participant_age = as.character(participant_age)
                                                                                         ) # "n" is the total number of edges in each age agoup in a network
  
    
  fit_nm_single <- 
    data_nm %>% 
  glm(same.age.grp ~ -1+ participant_age,
               data = ., family = "binomial"
              )  %>% summary() # coefficients for two-day contact rate
  
  fit_nm_single <- fit_nm_single$coefficients %>% as.data.frame()
  
  fit_nm_single <-
  fit_nm_single%>% rownames_to_column() %>% 
    rename(participant_age=1) %>% mutate(participant_age= str_remove(participant_age, "participant_age") 
                                 ) %>% 
    left_join(
      n_obs_age.grp
    )
  
  fit_nm_single <- 
  fit_nm_single %>% 
            mutate(
              # single-day mean degree, original scale
              single_day_nm_md = expit(Estimate)/2, # the reason 2 is here is because we convert 2 day to one day statistics
              
              # calculation, logit-link scale
              two_day_nm_sd_link = `Std. Error`*sqrt(n), # two-day standard deviation for the coefficient at the logit scale. HEre should be updated
              single_day_nm_sd_link = two_day_nm_sd_link/2,  # single-day standard deviation for the coefficient at the logit scale
              single_day_nm_se_link = single_day_nm_sd_link/sqrt(n), # single-day standard error for the coefficient at the logit scale
              single_day_nm_md_link = logit(single_day_nm_md), # single-day mean degree, logit scale
              
               # uncertainties, original scale
              single_day_nm_lower95ci = expit(single_day_nm_md_link -1.96*single_day_nm_se_link),
              single_day_nm_upper95ci =  expit(single_day_nm_md_link +1.96*single_day_nm_se_link)
                    ) %>% select(participant_age, single_day_nm_md, single_day_nm_lower95ci, single_day_nm_upper95ci
                                 ) %>% 
           mutate(contact_location = levels(contact_count_site$same.age.grp_degree$contact_location)[i]) # specify layer
  
  nm <- 
  rbind(nm, fit_nm_single)

}

output[[3]] <- nm


# nodemix TB finished - porportion of edges of specific mixing among all the edges



names(output) <- c("edge", "nf.age.grp", "nm.age.grp")

output
}

network_stats_rural <- network_stats(contact_count_site = contact_count_rural)





network_stats_urban <- network_stats(contact_count_site = contact_count_urban)


network_stats <- 
list(network_stats_rural, network_stats_urban)
names(network_stats) <- c("rural", "urban")

```

## Correlation between layers
```{r}

# rural
# individual-level contact count at different locations by row
## data to wide format 
 contact_count_wide_rural  <- 
contact_count_rural$contact_count %>% data.frame()%>% 
  tidyr::pivot_wider(names_from = "contact_location", values_from = "n_contacts"
                     ) %>%  # 608 rows, each row for a participant
  as.data.frame()
 
 # urban
## data to wide format 
 contact_count_wide_urban  <- 
contact_count_urban$contact_count %>% data.frame()%>% 
  tidyr::pivot_wider(names_from = "contact_location", values_from = "n_contacts"
                     ) %>%  # 624 rows, each row for a participant
  as.data.frame()




# spearman correlation,urban
contact_count_wide_urban %>% select(-c(rec_id, participant_age)) %>% ggpairs(upper = list(continuous = wrap("cor", method = "spearman")))


# spearman correlation,urban
contact_count_wide_rural %>% select(-c(rec_id, participant_age)) %>% ggpairs(upper = list(continuous = wrap("cor", method = "spearman")
                                                                                          )
                                                                             )



# Poisson regression for associations between contact between layers
assoc_btw_layers <- function(contact_count_wide, category_type, output_type){

  output_model <-   list()
  
# Create degree category, one binarized, one multiple categories
  if(category_type != "binary"){
 
    # With the degree distribution, the degree can be categorized into the categories of 0, 1-2, 3-5, and 6+.
contact_count_wide <- 
contact_count_wide %>% mutate(
  Nonhome_cat = case_when(Nonhome==0 ~ "0",
                          Nonhome %in% c(1:2) ~ "1-2",
                          Nonhome %in% c(3:5) ~ "3-5",
                          Nonhome >=6 ~ "6+"),
  Nonhome_cat = factor( Nonhome_cat),
  
  Home_cat = case_when(Home==0 ~ "0",
                          Home %in% c(1:2) ~ "1-2",
                          Home %in% c(3:5) ~ "3-5",
                          Home >=6 ~ "6+"),
  Home_cat = factor( Home_cat),
  
  School_cat = case_when(School==0 ~ "0",
                          School %in% c(1:2) ~ "1-2",
                          School %in% c(3:5) ~ "3-5",
                          School >=6 ~ "6+"),
  School_cat = factor( School_cat),
  
  Work_cat = case_when(Work==0 ~ "0",
                          Work %in% c(1:2) ~ "1-2",
                          Work %in% c(3:5) ~ "3-5",
                          Work >=6 ~ "6+"),
  Work_cat = factor( Work_cat)
  )
  
  

} else{ # binarized coefficient
  contact_count_wide <- 
contact_count_wide %>% mutate(
  Nonhome_cat = case_when(Nonhome==0 ~ 0,
                          Nonhome >0 ~ 1),
  Nonhome_cat = factor( Nonhome_cat),
  
    Home_cat = case_when(Home==0 ~ 0,
                          Home >0 ~ 1),
  Home_cat = factor( Home_cat),
  
    School_cat = case_when(School==0 ~ 0,
                          School >0 ~ 1),
  School_cat = factor( School_cat),
  
    Work_cat = case_when(Work==0 ~ 0,
                          Work >0 ~ 1),
  Work_cat = factor( Work_cat)
)
}
  

# Effects on home contact
output_model[[1]] <- 
contact_count_wide %>% 
  glm(Home~ Work_cat, data=., family = poisson(link=log))

output_model[[2]] <- 
contact_count_wide %>% 
  glm(Home~ Nonhome_cat, data=., family = poisson(link=log)) 

output_model[[3]] <- 
contact_count_wide %>% 
  glm(Home~ School_cat, data=., family = poisson(link=log))

output_model[[4]] <- 
contact_count_wide %>% 
  glm(Home~ Nonhome_cat + School_cat + Work_cat, data=., family = poisson(link=log))

# Effects on Nonhome contact
output_model[[5]] <- 
contact_count_wide %>% 
  glm(Nonhome~ Home_cat, data=., family = poisson(link=log))

output_model[[6]] <- 
contact_count_wide %>% 
  glm(Nonhome~ School_cat , data=., family = poisson(link=log))

output_model[[7]] <- 
contact_count_wide %>% 
  glm(Nonhome~ Work_cat , data=., family = poisson(link=log))



# Effects on School contact
output_model[[8]] <- 
contact_count_wide %>% 
  glm(School~ Home_cat, data=., family = poisson(link=log))

output_model[[9]] <- 
contact_count_wide %>% 
  glm(School~ Nonhome_cat , data=., family = poisson(link=log))

output_model[[10]] <- 
contact_count_wide %>% 
  glm(School~ Work_cat , data=., family = poisson(link=log))

# Effects on Work contact
output_model[[11]] <- 
contact_count_wide %>% 
  glm(Work~ Home_cat, data=., family = poisson(link=log))

output_model[[12]] <- 
contact_count_wide %>% 
  glm(Work~ School_cat , data=., family = poisson(link=log))

output_model[[13]] <- 
contact_count_wide %>% 
  glm(Work~ Nonhome_cat , data=., family = poisson(link=log))



names(output_model) <- c(  "h_w", "h_nh", "h_s", "h_nh_s_w", "nh_h", "nh_s", "nh_w", "s_h", "s_nh", "s_w", "w_h", "w_s", "w_nh")

if (output_type == "summary"){

output_model_summary <- rbind("h",
               summary(output_model[[1]])$coefficients %>% round(.,2),  summary(output_model[[2]])$coefficients %>% round(.,2) ,  summary(output_model[[3]])$coefficients %>% round(.,2) ,  summary(output_model[[4]])$coefficients %>% round(.,2) ,
                              "nh",
                               summary(output_model[[5]])$coefficients %>% round(.,2) ,  summary(output_model[[6]])$coefficients %>% round(.,2) , summary(output_model[[7]])$coefficients %>% round(.,2) , 
                              "s",
                               summary(output_model[[8]])$coefficients %>% round(.,2) ,  summary(output_model[[9]])$coefficients %>% round(.,2) ,  summary(output_model[[10]])$coefficients %>% round(.,2) ,
                              "w",
                               summary(output_model[[11]])$coefficients %>% round(.,2) ,  summary(output_model[[12]])$coefficients %>% round(.,2) ,  summary(output_model[[13]])$coefficients %>% round(.,2) )
} else if (output_type == "model") {
output_model
} else if (output_type == "data") {
contact_count_wide
}

}

## Rural
### Bivariate predictors
layer_rural_assoc_bi <- 
assoc_btw_layers(contact_count_wide = contact_count_wide_rural, category_type = "binary", output_type = "model")
layer_rural_assoc_bi_summary <- 
assoc_btw_layers(contact_count_wide = contact_count_wide_rural, category_type = "binary", output_type = "summary")
layer_rural_assoc_bi_data <- 
assoc_btw_layers(contact_count_wide = contact_count_wide_rural, category_type = "binary", output_type = "data")

h_w <- predict(layer_rural_assoc_bi$h_w, newdata = data.frame(Work_cat = factor(1)
                                                 ), 
                type = "response", interval = "confidence") %>% as.numeric()

deg.h_w.dist <- prop.table(table(layer_rural_assoc_bi_data$Work_cat))

### Multivariate predictors
layer_rural_assoc_multi  <- 
assoc_btw_layers(contact_count_wide = contact_count_wide_rural, category_type = "nonbinary", output_type = "model")

layer_rural_assoc_multi_summary  <- 
assoc_btw_layers(contact_count_wide = contact_count_wide_rural, category_type = "nonbinary", output_type = "summary")







## Urban
### Bivariate predictors
layer_urban_assoc_bi <- 
assoc_btw_layers(contact_count_wide = contact_count_wide_urban, category_type = "binary", output_type = "model")
layer_urban_assoc_bi_summary <- 
assoc_btw_layers(contact_count_wide = contact_count_wide_urban, category_type = "binary", output_type = "summary")

### Multivariate predictors
layer_urban_assoc_multi  <- 
assoc_btw_layers(contact_count_wide = contact_count_wide_urban, category_type = "nonbinary", output_type = "model")

layer_urban_assoc_multi_summary  <- 
assoc_btw_layers(contact_count_wide = contact_count_wide_urban, category_type = "nonbinary", output_type = "summary")






```



```{r}

network_stats$rural$correlate$h_w <- h_w
network_stats$rural$correlate$deg_w_dist <- deg.h_w.dist 
#saveRDS(network_stats, file = "~/Documents/GitHub/COVID-GlobalMix/data/network_params/formation_stats.RData")


```

## Contact durations
For duration at the home layer, we assume it to be non-dissolving so it would be a large number. For duration at the nonhome layer, we assume it refreshes daily. The duration of the school and work layer is characterized in the following way. We tabulate time of knowing a contact and contact frequency to retrieve the distribution of daily contact under categories of the duration of knowing the contact. For a contact is known less than ≤ 10 years, we took the mid point of each know contact category as the duration. For a contact is know > 10 years, we the population average of the mid point between participant's age and 10 year as the duration. We multiple the proportion of daily contact (as weight) and the duration to calculate the known duration. There are few contact whose participants' age is less than the reported know contact duration of > 10 yrs, randering the characterized duration to be <0; we used the participant's age as the duration for these observations.
```{r}

know_dur <- function(india_mix.){
  
  #  Characterize the known duration for known_contact >10 yrs
known_dur_gt_10yr <- india_mix. %>% 
  filter(known_contact == ">10 yrs" & contact_location %in% c( "School", "Work" )
                                  ) %>%
  #  the known duration is the middle point between 10 yrs and participants age
    mutate(known_duration = (participant_ageyr - 10)/2
           ) %>% 
  # for participants whose characterized know duration < 0, we consider the known duration the same as participant's age.
    mutate(
      known_duration = case_when(known_duration <= 0 ~ participant_ageyr,
                                 known_duration > 0 ~ known_duration) 
    )

  # Avg. known duration of contact in days by network and layer
known_dur_gt_10yr <- 
known_dur_gt_10yr %>% 
  group_by(study_site, contact_location) %>% 
  summarize(known_contact_avg = mean(known_duration)*365) %>% ungroup()

known_duration <-
india_mix. %>% 
  # characterize  frequency of daily contact 
  filter(contact_location %in% c("School", "Work")) %>% 
  group_by(study_site, contact_location, frequency_contact, known_contact) %>% 
  tally() %>% 
  spread(frequency_contact,n) %>% data.frame() %>% rename(daily = Daily..almost.daily) %>% 
  select(study_site, contact_location, known_contact, daily ) %>% 
  filter(!is.na(known_contact)) %>% # filter out the empty category
  ungroup() %>% 
  # characterize mid point for known duration for categories except <= 10yrs
    mutate(know_contact_d = # median duration in days
           case_when(known_contact=="Never met before" ~0, 
                     known_contact=="<1 yr" ~182, # mid. point
                     known_contact=="1-2 yrs" ~ 548,# mid. point
                     known_contact=="3-5 yrs" ~ 1460,# mid. point
                     known_contact=="6-10 yrs" ~ 2922,# mid. point
                     # Avg. know duration of contact for known_contact >10 yrs
                     known_contact==">10 yrs" & study_site == "Rural" & contact_location == "School" ~ 
                       known_dur_gt_10yr %>% filter( study_site == "Rural" & contact_location == "School") %>% 
                       select(known_contact_avg) %>% as.numeric(),
                      known_contact==">10 yrs" & study_site == "Rural" & contact_location == "Work" ~ 
                       known_dur_gt_10yr %>% filter( study_site == "Rural" & contact_location == "Work") %>% 
                       select(known_contact_avg) %>% as.numeric(),
                      known_contact==">10 yrs" & study_site == "Urban" & contact_location == "School" ~ 
                       known_dur_gt_10yr %>% filter( study_site == "Urban" & contact_location == "School") %>% 
                       select(known_contact_avg) %>% as.numeric(),
                      known_contact==">10 yrs" & study_site == "Urban" & contact_location == "Work" ~ 
                       known_dur_gt_10yr %>% filter( study_site == "Urban" & contact_location == "Work") %>% 
                       select(known_contact_avg) %>% as.numeric(),
                     )
           ) %>% 
  group_by(study_site, contact_location) %>% 
  
  mutate(
     daily_prop = daily/sum(daily, na.rm = T), # proportion of daily contact under each know_contact cateogry
     weighted_known_contact_d = know_contact_d*daily_prop # duration of known contact weighted by daily contact proportion
  ) %>%   
  # weighted avg. of duration of contact
  summarize(know_contact_duration_avg = sum(weighted_known_contact_d, na.rm = T)
            ) %>% ungroup()
  
}
known_duration <- know_dur(india_mix. = india_mix)

#saveRDS(known_duration, file = "~/Documents/GitHub/COVID-GlobalMix/data/network_params/known_dur_school_work.RData")







```



