---
title: "Descriptive Degree Summary of GlobalMix India Data"
author: "Billy Dehao Chen"
date: "09/25/2023"
output:
  html_document: default
  word_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

# Background
This is a descriptive summary of contact degree of the India GlobalMix diary data.

# Method
There are two ways to derive target statistics for ERGM, one is using poisson model based on individual-count data, the other is based on the symmetric contact matrix, the approach for Corporate Mix. Given the symmetric contact matrix may not account for the difference of distributions between the study and target populations, we go with the glm-based approach to calculate the summary network statistics. We regrouped the age categories in the first two decades of life by decade. We excluded contacts lasted ≤ 15 mins in analysis. The degree information was summarized as the arithmetic mean of signle-day degrees of contact between group A and group B and between group B and group A of the two-day visits. Given the data were egocentric, we use $M.D.=\frac{edges}{n}$ for the relationship between mean degree ($M.D.$) and the number of edges.
Characterization of network layers: The network layers is processed from multiple questions asking contact locations. Given these questions are not mutually exclusive due to the check-box design in REDCap, we characterized contact location as the location having primary contact follow the order of home, school, work, non-home (excluding work and school). There are two contacts that occurred at both work (location 3 in REDCap) and school (location 2), we categorized them as at school, considering the participants (and contacts) were at school age (10-19y, 0-9y). This logic is not spelled out in the below script but is adjusted by the higher priority of school than work. For a contact checked non of the categories, we assigned an NA to this contact and excluded them considering them as missing data.


```{r, echo=F, warning=F, message=FALSE, include = FALSE}
setwd("~/Documents/GitHub/COVID-GlobalMix")

# Load libraries and data  ------------------------------------------------
lapply(c("ggpubr", "statnet", "EpiModel", "tidyverse", "socialmixr", "knitr",  "sjlabelled", "kableExtra", "broom", "stringr", "GGally"), require, character.only = TRUE)


## participant data
india_participant <- 
readRDS("~/Documents/GitHub/COVID-GlobalMix/data/participant_contact/india_participant_data_aim1.RDS")



## contact data 
india_contact <- 
 readRDS("~/Documents/GitHub/COVID-GlobalMix/data/participant_contact/india_contact_data_aim1.RDS")
#readRDS("../Documents/GitHub/COVID-GlobalMix/data/participant_contact/india_contact_data_aim1.RDS")

# Note - validated study_site of participant is exactly the same as those in contact

# Reclassifying participant's and contact's age groups into 0-9 years old, 10-19 years old, while treating other age groups as is.
## participant data
india_participant <- 
india_participant %>% 
  mutate(
      participant_age = case_when(
        participant_age %in% c("<6mo", "6-11mo",   "1-4y",   "5-9y") ~ "0-9y",
        participant_age %in% c("10-14y", "15-19y") ~ "10-19y",
        .default =  participant_age
      )
    )%>% 
  mutate(participant_age= factor(participant_age, levels=c("0-9y", "10-19y", "20-29y", "30-39y", "40-59y",   "60+y")
                                         )
         ) %>% mutate(participant_ageyr = floor(participant_ageyr)
                      )

## contact data
india_contact <- 
india_contact %>%     
  mutate(
      contact_age = case_when(
        contact_age %in% c("<6mo", "6-11mo",   "1-4y",   "5-9y") ~ "0-9y",
        contact_age %in% c("10-14y", "15-19y") ~ "10-19y",
        .default =  contact_age
      )
    )%>% 
    mutate(contact_age= factor(contact_age, levels=c("0-9y", "10-19y", "20-29y", "30-39y", "40-59y",   "60+y")
                                         )
         )

# merge participants and contact datasets and process data  and basic data processing ------------------------------------------------
india_mix <- india_participant %>%
  dplyr::select(rec_id,participant_age, participant_ageyr) %>%
  right_join(india_contact,
            by = "rec_id") %>% 
  # characterization of home/nonhome status
   mutate(contact_location = case_when(location_contact___0 == 1  ~ "Home", # 0 - "My home"
                                            location_contact___2 == 1 & location_contact___0 == 0 ~ "School", # "School" but not "my home" 
                                             location_contact___3 == 1 & (location_contact___0 == 0  | location_contact___2 ==0)~ "Work", # "work" but not "my home" / "school"
                                       
                                       
                                       (
                                       location_contact___1 == 1 | location_contact___4 == 1 | # "Other home",  "Transport/Hub"
                                       location_contact___5 == 1 | location_contact___6 == 1 | # "Market/Shop", "Street"
                                       location_contact___7 == 1 | location_contact___8 == 1 | # "Playground", "Well"
                                       location_contact___9 == 1 | location_contact___10 == 1 | # "Agricultural Field", "Market/Shop"
                                       location_contact___11 == 1 | location_contact___12 == 1 | # "Restaurant", "Religious centre"
                                       location_contact___13 == 1 | location_contact___14 == 1 | # "Govt offices", "Health center"
                                       location_contact___15 == 1 | location_contact___16 == 1 | # "Bank", "Movie theatre"
                                       location_contact___17 == 1 | location_contact___18 == 1 | location_contact___19 == 1 #"Exhibition", "Social hall", "Other"
                                       ) &
                                         !(location_contact___3 == 1 | location_contact___2 == 1 | location_contact___0 == 1) # Excluding work/school/home
                                       
                                       ~ "Nonhome") # "Nonhome" but not "home", "school", "work"
         )  %>% 
   ## Weighing in household membership in determining contact location - tabulating contact_location and hh_membership, we found there are 58,1,3 household member contacts in the nonhome, school, and work layers. We reclassify these as home contacts. We also found 2176 non-members at the home layer, and we reclassify them into non-home (other than school, work) contacts given the presumed turnover rate for this group is short. 
  mutate(
    contact_location = case_when(hh_membership == "Member" & contact_location %in% c("Nonhome", "School", "Work") ~ "Home",
                                 hh_membership == "Non-member" & contact_location %in% c("Home") ~ "Nonhome",
                                 T ~ contact_location
                                 )

  ) %>%
  mutate(contact_location = factor(contact_location,
                                    levels = c("Home", "School", "Work", "Nonhome")
                                   )
         ) %>% 
  filter(!(duration_contact %in% c("<5 mins", "5-15 mins"))) %>% # filter out contact with duration ≤ 15 mins
  mutate(
         duration_contact = factor(duration_contact,
                                    levels = c( "16-30 mins",  "31 mins-1 hr", "1-4 hrs", ">4 hrs", "Unknown")
                                   )
         )  %>% filter(!is.na(contact_location) # complete-case analysis - exclude contacts didn't have a contact location from analysis, Moses confirmed this is okay
                      ) %>% 

## Distribution of indoor/outdoor status
# We the break down of the observed categories of the variable "where_contact" indicating in- and out-door status. In the original data, there is a "Both" category indicates a participant contacted a contact both in- and out-doors. Since the "Both" category could have a higher transmission potential similar to the "Indoors" category, we merge the "Both" and the "Indoors" categories. We will adjust for this status as a nodefactor. For building the transmission model, we will assign lower risk for the "Outdoors" category during simulation.
   mutate(where_contact =case_when(where_contact %in% c("Indoors", "Both") ~ "Indoors_or_both",
                                              .default = where_contact)
                     )



## Check implementation of the cross-checking between household membership and contact location
table(
india_mix$contact_location,
india_mix$hh_membership
)


```


## Uncertainties of network statistics

```{r}
expit <- function(x){exp(x)/(1+exp(x))}; logit <- function(x){log(x/(1-x))}
# Function characterizing number of contact at the individual-level (outputted in "contact_count") and the status of if a participant and contact was in the same age group (outputted in "sameage.grp.count") for the contact data over the two-day period.
contact_freq_site <- function(india_mix., india_participant., india_contact., study_site.){
india_mix.site <- 
 india_mix.  %>% 
  filter(study_site == study_site.) # here we split the dataset into urban or rural samples


id_no_contact.site <- # participants with 0 contacts by study site in India
  india_participant. %>%
  filter(!(rec_id %in% india_contact.$rec_id)) %>%
  filter(study_site == study_site.) 


locations <- levels(india_mix.site$contact_location) # retrieve the full levels of contact locations


#### Total number of contacts over two days, for ~ edge and nodefactor ####
contact_count <- 
india_mix.site %>%
   group_by(rec_id, contact_location, fromdayone, .drop = F)%>% summarise(n_contacts = n()) %>% # summarizing number of contacts by characteristics included in "group_by"
  ungroup() %>% 
  mutate(
    n_contacts = case_when(
    contact_location %in% c("Home", "Work","School") ~ n_contacts, # for these layers, a replicated contact is counted as unique contact
    contact_location %in% c("Nonhome" ) & fromdayone == "Both days" ~ n_contacts*2, # for non-home layer, a replicated contact is counted as two contact
    contact_location %in% c("Nonhome" ) & fromdayone %in% c("Day 1", "Day 2") ~ n_contacts, # for non-home layer, a unique contact is counted as one contact
    T ~ n_contacts # for observation with fromdayone information missed, we return the original n_contacts
    )  
    )%>% 
  group_by(rec_id, contact_location, .drop = F) %>% summarise(n_contacts = sum(n_contacts)
                                                          ) %>% ungroup() %>% # total number of contacts over two days
   # add the participants w/o contact to the data
  rbind(., 
        data.frame(
          rec_id = rep(as.character(id_no_contact.site$rec_id), each = length(locations)),
          contact_location= rep(locations, 
                                nrow(id_no_contact.site)
                                ),
          n_contacts=rep(0,  nrow(id_no_contact.site)*length(locations))
        )
  ) %>% 
  # joining w/ participant's age
  left_join(india_participant. %>% select(rec_id, participant_age),
            by = "rec_id"
            )

#### Number of contacts of the same age group, individual-level, for nodematch ####
same.age.grp_degree <- 
india_mix.site %>% 
  mutate(same.age.grp = ifelse(participant_age == contact_age, 1, 0)
         
           ) %>% 
 mutate(
   # adjusting replicated contacts
    same.age.grp = case_when(
    contact_location %in% c("Home", "Work","School") ~  same.age.grp, # for these layers, a replicated contact is counted as unique contact
    contact_location %in% c("Nonhome" ) & fromdayone == "Both days" ~ same.age.grp*2, # for non-home layer, a replicated contact is counted as two contact
    contact_location %in% c("Nonhome" ) & fromdayone %in% c("Day 1", "Day 2") ~ same.age.grp, # for non-home layer, a unique contact is counted as one contact
    T ~ same.age.grp # for observation with fromdayone information missed, we return the original same.age.grp
    )  
    ) %>%
  select(rec_id,  contact_location, participant_age, contact_age, same.age.grp
         )
  # Given nodematch is defined at the edge, I think the following code with 0 contact (i.e., w/o edge) don't need to be accounted
  # rbind(., 
  #       data.frame(
  #         rec_id = rep(as.character(id_no_contact.site$rec_id), each = length(locations)),
  #         contact_location= rep(locations, 
  #                               nrow(id_no_contact.site)
  #                               ),
  #          same.age.grp=rep(0,  nrow(id_no_contact.site)*length(locations)),
  #         contact_age =NA
  #       )
  #       )%>%

 # Replicate each observation/row w/ same.age.grp == 2 twice and recode these observations' same.age.grp to 1; for observations w/ same.age.grp = 1/0, we treat them as-is
same.age.grp_degree <- 
  same.age.grp_degree %>% filter(same.age.grp==2) %>% slice(rep(1:n(), each = 2)) %>% mutate(same.age.grp=1) %>% 
    rbind(., same.age.grp_degree %>% filter(same.age.grp !=2)
          ) 


#### Status of whether one group matched to another, for nodemix ####
age.grp_mix <- 
india_mix.site %>% 
  # select subset of variables for ouput
  select(rec_id, contact_location, participant_age, contact_age, fromdayone) %>% 
  
  # The following levels are used to code the age groups "0-9y"~1, "10-19y"~2, "20-29y"~3, "30-39y"~4, "40-59y"~5, "60+y"~6. 
  # If an edge/contact's age groups matched with one of the 36 patterns, it will be assigned 1 for the corresponding matching pattern
  mutate(age.grp1_1 = ifelse(participant_age == "0-9y" & contact_age ==  "0-9y", 1, 0),
         age.grp1_2 = ifelse(participant_age == "0-9y" & contact_age ==  "10-19y", 1, 0),
         age.grp1_3 = ifelse(participant_age == "0-9y" & contact_age ==  "20-29y" , 1, 0),
         age.grp1_4 = ifelse(participant_age == "0-9y" & contact_age ==  "30-39y" , 1, 0),
         age.grp1_5 = ifelse(participant_age == "0-9y" & contact_age ==  "40-59y", 1, 0),
         age.grp1_6 = ifelse(participant_age == "0-9y" & contact_age ==  "60+y", 1, 0),
         
         age.grp2_1 = ifelse(participant_age == "10-19y" & contact_age ==  "0-9y", 1, 0),
         age.grp2_2 = ifelse(participant_age == "10-19y" & contact_age ==  "10-19y", 1, 0),
         age.grp2_3 = ifelse(participant_age == "10-19y" & contact_age ==  "20-29y" , 1, 0),
         age.grp2_4 = ifelse(participant_age == "10-19y" & contact_age ==  "30-39y" , 1, 0),
         age.grp2_5 = ifelse(participant_age == "10-19y" & contact_age ==  "40-59y", 1, 0),
         age.grp2_6 = ifelse(participant_age == "10-19y" & contact_age ==  "60+y", 1, 0),
         
         age.grp3_1 = ifelse(participant_age == "20-29y" & contact_age ==  "0-9y", 1, 0),
         age.grp3_2 = ifelse(participant_age == "20-29y" & contact_age ==  "10-19y", 1, 0),
         age.grp3_3 = ifelse(participant_age == "20-29y" & contact_age ==  "20-29y" , 1, 0),
         age.grp3_4 = ifelse(participant_age == "20-29y" & contact_age ==  "30-39y" , 1, 0),
         age.grp3_5 = ifelse(participant_age == "20-29y" & contact_age ==  "40-59y", 1, 0),
         age.grp3_6 = ifelse(participant_age == "20-29y" & contact_age ==  "60+y", 1, 0),
         
         age.grp4_1 = ifelse(participant_age == "30-39y" & contact_age ==  "0-9y", 1, 0),
         age.grp4_2 = ifelse(participant_age == "30-39y" & contact_age ==  "10-19y", 1, 0),
         age.grp4_3 = ifelse(participant_age == "30-39y" & contact_age ==  "20-29y" , 1, 0),
         age.grp4_4 = ifelse(participant_age == "30-39y" & contact_age ==  "30-39y" , 1, 0),
         age.grp4_5 = ifelse(participant_age == "30-39y" & contact_age ==  "40-59y", 1, 0),
         age.grp4_6 = ifelse(participant_age == "30-39y" & contact_age ==  "60+y", 1, 0),
         
         age.grp5_1 = ifelse(participant_age == "40-59y" & contact_age ==  "0-9y", 1, 0),
         age.grp5_2 = ifelse(participant_age == "40-59y" & contact_age ==  "10-19y", 1, 0),
         age.grp5_3 = ifelse(participant_age == "40-59y" & contact_age ==  "20-29y" , 1, 0),
         age.grp5_4 = ifelse(participant_age == "40-59y" & contact_age ==  "30-39y" , 1, 0),
         age.grp5_5 = ifelse(participant_age == "40-59y" & contact_age ==  "40-59y", 1, 0),
         age.grp5_6 = ifelse(participant_age == "40-59y" & contact_age ==  "60+y", 1, 0),
         
         age.grp6_1 = ifelse(participant_age == "60+y"  & contact_age ==  "0-9y", 1, 0),
         age.grp6_2 = ifelse(participant_age == "60+y"  & contact_age ==  "10-19y", 1, 0),
         age.grp6_3 = ifelse(participant_age == "60+y"  & contact_age ==  "20-29y" , 1, 0),
         age.grp6_4 = ifelse(participant_age == "60+y"  & contact_age ==  "30-39y" , 1, 0),
         age.grp6_5 = ifelse(participant_age == "60+y"  & contact_age ==  "40-59y", 1, 0),
         age.grp6_6 = ifelse(participant_age == "60+y"  & contact_age ==  "60+y", 1, 0)
         
           ) %>% 
 mutate(
   # adjusting for replicated contacts
    across(
      c(age.grp1_1:age.grp6_6),
      ~case_when(
    contact_location %in% c("Home", "Work","School") ~  ., # for these layers, a replicated contact is counted as unique contact
    contact_location %in% c("Nonhome" ) & fromdayone == "Both days" ~ .*2, # for non-home layer, a replicated contact is counted as two contact
    contact_location %in% c("Nonhome" ) & fromdayone %in% c("Day 1", "Day 2") ~ ., # for non-home layer, a unique contact is counted as one contact
    T ~ . # for observation with fromdayone information missed, we return the original data
    )  )
    )
# for each mixing, we replicate contact with count == 2 into two rows and save each mixing as a component in list
age.grp_mix_degree <- list()

  for (i in 6:ncol(age.grp_mix)
       ) {
    age.grp_single_mix <- 
      age.grp_mix%>% select(rec_id:fromdayone, all_of(i)) %>% 
      rename(mix_count =ncol(.) # give a temporal col name to facilitate data manipulation
             )  
     # Replicate each observation/row w/ mix_count == 2 twice and recode these observations' mix_count to 1; for observations w/ mix_count = 1/0, we treat them as-is
  age.grp_single_mix <- 
    age.grp_single_mix %>% 
  filter(mix_count==2) %>% slice(rep(1:n(), each = 2)) %>% mutate(mix_count=1) %>%
   rbind(., age.grp_single_mix %>% filter(mix_count !=2)
         ) 
  
  colnames(age.grp_single_mix)[length(colnames(age.grp_single_mix))] <- colnames(age.grp_mix)[i] # rename col back to its original name
  
  age.grp_mix_degree[[i-5]] <- age.grp_single_mix %>% select(-fromdayone) # store output in each iteration into a list
  }

names(age.grp_mix_degree)<- colnames(age.grp_mix %>% select(age.grp1_1:age.grp6_6)) # adding mixing as name to the list

# we remove the mixing of the same age group from the directional mixing proportion for nodemix
age.grp_mix_degree$age.grp1_1 <- age.grp_mix_degree$age.grp2_2 <- age.grp_mix_degree$age.grp3_3 <- age.grp_mix_degree$age.grp4_4 <- 
  age.grp_mix_degree$age.grp5_5 <- age.grp_mix_degree$age.grp6_6 <- NULL

 out <-list(contact_count, same.age.grp_degree, age.grp_mix_degree
            );
 names(out) <- c("contact_degree", "same.age.grp_degree" , "age.grp_mix_degree"
                 )
  
  out

}

contact_count_rural <- # rural mixing
contact_freq_site(india_mix. = india_mix, 
           india_participant. = india_participant, 
           india_contact. = india_contact,
           study_site. ="Rural") 



contact_count_urban  <- # urban mixing
contact_freq_site(india_mix. = india_mix , 
           india_participant. = india_participant, 
           
           india_contact. = india_contact,
           study_site. ="Urban") 


# Function calculating directional mixing proportion for single mixing at the age group level, with age.grp.a as the age group of the egocentric population
mix_prop <- # discuss with Sam
function(mix_degree, age.grp.a, age.grp.b, contact_loc){

dir_1 <-   paste0("age.grp", age.grp.a, "_",age.grp.b) # contact direction between participant (i.e., egocentric node) in age group a and contact in age group b
dir_2 <-   paste0("age.grp", age.grp.b, "_", age.grp.a)# contact direction between participant (i.e., egocentric node) in age group b and contact in age group a 

age_cats <- # age categories
mix_degree[[dir_1]] %>% filter(contact_location == contact_loc) %>% pull(participant_age) %>% levels()

df_dir_1 <- # rename the last column to "degree"
mix_degree[[dir_1]] %>% filter(contact_location == contact_loc) %>% rename_at(ncol(.), ~ "degree")

df_dir_2 <-  # rename the last column to "degree"
mix_degree[[dir_2]] %>% filter(contact_location == contact_loc) %>% rename_at(ncol(.), ~ "degree")

# Calculating matched proportion for age.grp a - if there isn't participant in an age group, we skip calculating the proportion for that age group
if(
sum(df_dir_1$participant_age == age_cats[age.grp.a]) >0 # if there is no participant of this age group, an NA will be returned for the proportion
){
  # regressing degree on age groups
glm_nmix_dir_1 <-
df_dir_1 %>% 
  glm(degree ~ -1+ participant_age,
               data = ., family = "binomial"
              )  %>% summary()

 # retrieving the estimated proportion
prop_dir_1 <- glm_nmix_dir_1$coefficients %>% as.data.frame() %>% rownames_to_column(var = "age.grp") %>% 
  mutate(age.grp = str_replace(age.grp, "participant_age", "")) %>% filter(age.grp == age_cats[age.grp.a]) %>% pull(Estimate) %>% expit()/2 # the reason 2 is here is because we convert 2 day to one day statistics
} else{
  prop_dir_1 <- NA
}

# Calculating matched proportion for age.grp b - if there isn't participant in an age group, we skip calculating the proportion for that age group
if(
sum(df_dir_2$participant_age == age_cats[age.grp.b])>0 # if there is no participant of this age group, an NA will be returned for the proportion
){
  
glm_nmix_dir_2 <-
df_dir_2 %>%
  glm(degree ~ -1+ participant_age,
               data = ., family = "binomial"
              )  %>% summary()

prop_dir_2 <- glm_nmix_dir_2$coefficients %>% as.data.frame() %>% rownames_to_column(var = "age.grp") %>% 
  mutate(age.grp = str_replace(age.grp, "participant_age", "")) %>% filter(age.grp == age_cats[age.grp.b]) %>% pull(Estimate) %>% expit()/2 # the reason 2 is here is because we convert 2 day to one day statistics
} else{
  prop_dir_2 <- NA 
}
  
data.frame(matrix(c(prop_dir_1, prop_dir_2), nrow =1, ncol =2)) %>% setNames(c(dir_1, dir_2)) # putting the two characterized proportions together


}


# Function calculating 
avg_mix_prop_all_layers <- 
function(mix_degree_site){
 mix_matrices <- list()
 layers <- c("Home", "School", "Work", "Nonhome")
 
# calculating for each layer
for (i in 1:4) { 
  print(layers[i])

# empty dataframe to store result 
mix_matrix <- 
  matrix(NA, nrow = 6, ncol = 6) %>% 
    as.data.frame(., 
    row.names = c("0-9y", "10-19y", "20-29y", "30-39y", "40-59y", "60+y")
    ) %>% rename("0-9y"=1, "10-19y"=2, "20-29y"=3, "30-39y"=4, "40-59y"=5, "60+y"=6)
    
# of each layer, calculation for  participant age.group == "0-9y"    
for (j in 2:6) {
  
  directional_prop <- 
   mix_prop(mix_degree = mix_degree_site, age.grp.a = 1, age.grp.b = j, contact_loc = layers[i]) 
  
  print(directional_prop)
  
   mix_matrix[1, j] <-  directional_prop %>% as.numeric() %>% mean(., na.rm = T) # mean proportion of a mixing
 
 
}

# of each layer, calculation for participant age.group == "10-19y"    
for (j in 3:6) {
  
  
  directional_prop <- 
   mix_prop(mix_degree = mix_degree_site, age.grp.a = 2, age.grp.b = j, contact_loc = layers[i]) 
  
  print(directional_prop)
  
   mix_matrix[2, j] <-  directional_prop %>% as.numeric() %>% mean(., na.rm = T) # mean proportion of a mixing
  
}

# of each layer, calculation for participant age.group == "20-29y"
for (j in 4:6) {
  
    directional_prop <- 
   mix_prop(mix_degree = mix_degree_site, age.grp.a = 3, age.grp.b = j, contact_loc = layers[i]) 
  
  print(directional_prop)
  
   mix_matrix[3, j] <-  directional_prop %>% as.numeric() %>% mean(., na.rm = T) # mean proportion of a mixing
  
  
}

# of each layer, calculation for participant age.group == "30-39y"
for (j in 5:6) {
   directional_prop <- 
   mix_prop(mix_degree = mix_degree_site, age.grp.a = 4, age.grp.b = j, contact_loc = layers[i]) 
  
  print(directional_prop)
  
   mix_matrix[4, j] <-  directional_prop %>% as.numeric() %>% mean(., na.rm = T) # mean proportion of a mixing
}

# of each layer, calculation for participant age.group == "40-59y"
  directional_prop <- 
   mix_prop(mix_degree = mix_degree_site, age.grp.a = 5, age.grp.b = 6, contact_loc = layers[i]) 
  
  print(directional_prop)
  
   mix_matrix[5, 6] <-  directional_prop %>% as.numeric() %>% mean(., na.rm = T) # mean proportion of a mixing

 directional_prop <- NULL # remove this intermediate df when calculation is done

  mix_matrices[[i]] <-  mix_matrix 
 
# # script for QC calculation in the function for nodemix stat
# mix_degree_site$age.grp1_2 %>% filter(contact_location == "Home") %>% group_by(participant_age) %>% 
#    summarize(avg = mean(age.grp1_2), sum= sum(age.grp1_2), n = n()) 
# mix_degree_site$age.grp2_1 %>% filter(contact_location == "Home") %>% group_by(participant_age) %>% 
#    summarize(avg = mean(age.grp2_1), sum= sum(age.grp2_1), n = n()) 
}
 names(mix_matrices) <- layers
 
 mix_matrices
}

rural_mix_prop <- avg_mix_prop_all_layers(mix_degree_site = contact_count_rural$age.grp_mix_degree)
 
rural_mix_prop

urban_mix_prop <- avg_mix_prop_all_layers(mix_degree_site = contact_count_urban$age.grp_mix_degree)
 
urban_mix_prop


# Function characterizing network statistics
network_stats <- function(contact_count_site){

  output <- list()
  
# Edges 
fit_edge <- 
  contact_count_site$contact_degree %>% 
  glm(n_contacts~ -1+contact_location, data=., family = poisson) %>% summary() # coefficient for two-day contact rate

fit_edge <- fit_edge$coefficients%>% as.data.frame()  # the two is averaging two-day's contact rate to one-day

n_participants_site <- 
contact_count_site$contact_degree$rec_id %>% unique() %>% length()  # number of participants of a network
 
fit_edge <- 
fit_edge %>% 
            mutate(
              # single-day mean degree, original scale
              single_day_md = exp(Estimate)/2,
              
              # calculation, log-link scale
              two_day_sd_link = `Std. Error`*sqrt(n_participants_site), # two-day standard deviation for the coefficient at the log scale
              single_day_sd_link = two_day_sd_link/2,  # single-day standard deviation for the coefficient at the log scale
              single_day_se_link = single_day_sd_link/sqrt(n_participants_site), # single-day standard error for the coefficient at the log scale
              single_day_md_link = log(single_day_md),
              
               # uncertainties, original scale
              single_day_lower95ci = exp(single_day_md_link -1.96*single_day_se_link),
              single_day_upper95ci =  exp(single_day_md_link +1.96*single_day_se_link)
                    ) %>% select(single_day_md, single_day_lower95ci, single_day_upper95ci
                                 )



output[[1]] <- fit_edge %>% rownames_to_column(var="contact_location") %>%
  mutate(contact_location=str_remove(contact_location, "contact_location")
         )


# nodefactor - age.grp
n_participants_nf_site <- # number of participants in each age.grp in a network
contact_count_site$contact_degree %>% group_by( participant_age) %>% 
  summarize(n_participants_nf_site = n_distinct(rec_id)) %>% mutate(participant_age = as.character(participant_age))

nf <- data.frame() 
for (i in 1:4 # characterize mean degree and uncertainties for each layer
     ) {
  fit_nf_single <- 
  contact_count_site$contact_degree %>% filter(contact_location == levels(contact_count_site$contact_degree$contact_location)[i]) %>% 
  glm(n_contacts~ -1+participant_age, data=., family = poisson) %>% summary() # coefficients for two-day contact rate
  
  fit_nf_single <- fit_nf_single$coefficients %>% as.data.frame()
  
  fit_nf_single <-
  fit_nf_single%>% rownames_to_column() %>% 
    rename(participant_age=1) %>% mutate(participant_age= str_remove(participant_age, "participant_age") 
                                 ) %>% 
    left_join(
      n_participants_nf_site
    )
  
  fit_nf_single <- 
  fit_nf_single %>% 
            mutate(
              # single-day mean degree, original scale
              single_day_nf_md = exp(Estimate)/2,
              
              # calculation, log-link scale
              two_day_nf_sd_link = `Std. Error`*sqrt(n_participants_nf_site), # two-day standard deviation for the coefficient at the log scale
              single_day_nf_sd_link = two_day_nf_sd_link/2,  # single-day standard deviation for the coefficient at the log scale
              single_day_nf_se_link = single_day_nf_sd_link/sqrt(n_participants_nf_site), # single-day standard error for the coefficient at the log scale
              single_day_nf_md_link = log(single_day_nf_md), # single-day mean degree, log scale
              
               # uncertainties, original scale
              single_day_nf_lower95ci = exp(single_day_nf_md_link -1.96*single_day_nf_se_link),
              single_day_nf_upper95ci =  exp(single_day_nf_md_link +1.96*single_day_nf_se_link)
                    ) %>% select(participant_age, single_day_nf_md, single_day_nf_lower95ci, single_day_nf_upper95ci
                                 ) %>% 
           mutate(contact_location = levels(contact_count_site$contact_degree$contact_location)[i]) # specify layer

  
  
  
  
  nf <- 
  rbind(nf, fit_nf_single)

}


output[[2]] <- nf


# nodematch - porportion of matched edges of each age group among all the edges

nm <- data.frame() #matrix(NA, nrow = length(locations), ncol = length(levels(contact_count$participant_age)))
for (i in 1:4 #length(locations)
     ) {
  
 
  data_nm <- 
  contact_count_site$same.age.grp_degree %>% filter(contact_location == levels(contact_count_site$same.age.grp_degree$contact_location)[i]) 
    
  n_obs_age.grp <- data_nm %>% group_by(participant_age) %>% summarize(n=n()) %>% mutate(participant_age = as.character(participant_age)
                                                                                         ) # "n" is the total number of edges in each age agoup in a network
  
    
  fit_nm_single <- 
    data_nm %>% 
  glm(same.age.grp ~ -1+ participant_age,
               data = ., family = "binomial"
              )  %>% summary() # coefficients for two-day contact rate
  
  fit_nm_single <- fit_nm_single$coefficients %>% as.data.frame()
  
  fit_nm_single <-
  fit_nm_single%>% rownames_to_column() %>% 
    rename(participant_age=1) %>% mutate(participant_age= str_remove(participant_age, "participant_age") 
                                 ) %>% 
    left_join(
      n_obs_age.grp
    )
  
  fit_nm_single <- 
  fit_nm_single %>% 
            mutate(
              # single-day mean degree, original scale
              single_day_nm_md = expit(Estimate)/2, # the reason 2 is here is because we convert 2 day to one day statistics
              
              # calculation, logit-link scale
              two_day_nm_sd_link = `Std. Error`*sqrt(n), # two-day standard deviation for the coefficient at the logit scale. HEre should be updated
              single_day_nm_sd_link = two_day_nm_sd_link/2,  # single-day standard deviation for the coefficient at the logit scale
              single_day_nm_se_link = single_day_nm_sd_link/sqrt(n), # single-day standard error for the coefficient at the logit scale
              single_day_nm_md_link = logit(single_day_nm_md), # single-day mean degree, logit scale
              
               # uncertainties, original scale
              single_day_nm_lower95ci = expit(single_day_nm_md_link -1.96*single_day_nm_se_link),
              single_day_nm_upper95ci =  expit(single_day_nm_md_link +1.96*single_day_nm_se_link)
                    ) %>% select(participant_age, single_day_nm_md, single_day_nm_lower95ci, single_day_nm_upper95ci
                                 ) %>% 
           mutate(contact_location = levels(contact_count_site$same.age.grp_degree$contact_location)[i]) # specify layer
  
  nm <- 
  rbind(nm, fit_nm_single)

}

output[[3]] <- nm


#### nodemix TB finished - porportion of edges of specific mixing among all the edges ###


names(output) <- c("edge", "nf.age.grp", "nm.age.grp")

output
}

network_stats_rural <- network_stats(contact_count_site = contact_count_rural)


network_stats_urban <- network_stats(contact_count_site = contact_count_urban)

network_stats_rural$nodemix <- rural_mix_prop
network_stats_urban$nodemix <- urban_mix_prop

network_stats <- 
list(network_stats_rural, network_stats_urban)
names(network_stats) <- c("rural", "urban")


```

## Correlation between layers
We tabulated the degrees between layers. In both the rural and urban networks, the contacts at school and work are relatively separated
```{r}
# Getting individual-level contact count at different locations by row through converting long format data to wide format 
## rural 
contact_count_wide_rural  <- 
contact_count_rural$contact_degree %>% data.frame()%>% 
  tidyr::pivot_wider(names_from = "contact_location", values_from = "n_contacts"
                     ) %>%  # 608 rows, each row for a participant
  as.data.frame()
 
## urban
 contact_count_wide_urban  <- 
contact_count_urban$contact_degree %>% data.frame()%>% 
  tidyr::pivot_wider(names_from = "contact_location", values_from = "n_contacts"
                     ) %>%  # 624 rows, each row for a participant
  as.data.frame()

# Visally evaluation correlation between layers
## spearman correlation,rural
contact_count_wide_rural %>% select(-c(rec_id, participant_age)) %>% ggpairs(upper = list(continuous = wrap("cor", method = "spearman")
                                                                                          )
                                                                             )

## spearman correlation,urban
contact_count_wide_urban %>% select(-c(rec_id, participant_age)) %>% ggpairs(upper = list(continuous = wrap("cor", method = "spearman")))



# Function to conduction bivariate Poisson regression for associations of degree between layers
assoc_btw_layers <- function(contact_count_wide, category_type, output_type){

  output_model <-   list()
  
# Create degree category - binarized, or ordinal
  
  if(category_type != "binary"){
 
    # With the degree distribution, the degree can be categorized into the categories of 0, 1-2, 3-5, and 6+.
contact_count_wide <- 
contact_count_wide %>% mutate(
  Nonhome_cat = case_when(Nonhome==0 ~ "0",
                          Nonhome %in% c(1:2) ~ "1-2",
                          Nonhome %in% c(3:5) ~ "3-5",
                          Nonhome >=6 ~ "6+"),
  Nonhome_cat = factor( Nonhome_cat),
  
  Home_cat = case_when(Home==0 ~ "0",
                          Home %in% c(1:2) ~ "1-2",
                          Home %in% c(3:5) ~ "3-5",
                          Home >=6 ~ "6+"),
  Home_cat = factor( Home_cat),
  
  School_cat = case_when(School==0 ~ "0",
                          School %in% c(1:2) ~ "1-2",
                          School %in% c(3:5) ~ "3-5",
                          School >=6 ~ "6+"),
  School_cat = factor( School_cat),
  
  Work_cat = case_when(Work==0 ~ "0",
                          Work %in% c(1:2) ~ "1-2",
                          Work %in% c(3:5) ~ "3-5",
                          Work >=6 ~ "6+"),
  Work_cat = factor( Work_cat)
  )
  
  

} else{ # binarized coefficient
  contact_count_wide <- 
contact_count_wide %>% mutate(
  Nonhome_cat = case_when(Nonhome==0 ~ 0,
                          Nonhome >0 ~ 1),
  Nonhome_cat = factor( Nonhome_cat),
  
    Home_cat = case_when(Home==0 ~ 0,
                          Home >0 ~ 1),
  Home_cat = factor( Home_cat),
  
    School_cat = case_when(School==0 ~ 0,
                          School >0 ~ 1),
  School_cat = factor( School_cat),
  
    Work_cat = case_when(Work==0 ~ 0,
                          Work >0 ~ 1),
  Work_cat = factor( Work_cat)
)
}
  

# Effects of other layers on home 
output_model[[1]] <- 
contact_count_wide %>% 
  glm(Home~ Work_cat, data=., family = poisson(link=log))

output_model[[2]] <- 
contact_count_wide %>% 
  glm(Home~ Nonhome_cat, data=., family = poisson(link=log)) 

output_model[[3]] <- 
contact_count_wide %>% 
  glm(Home~ School_cat, data=., family = poisson(link=log))


# Effects of other layers on Nonhome
output_model[[4]] <- 
contact_count_wide %>% 
  glm(Nonhome~ Home_cat, data=., family = poisson(link=log))

output_model[[5]] <- 
contact_count_wide %>% 
  glm(Nonhome~ School_cat , data=., family = poisson(link=log))

output_model[[6]] <- 
contact_count_wide %>% 
  glm(Nonhome~ Work_cat , data=., family = poisson(link=log))


# Effects of other layers on School
output_model[[7]] <- 
contact_count_wide %>% 
  glm(School~ Home_cat, data=., family = poisson(link=log))

output_model[[8]] <- 
contact_count_wide %>% 
  glm(School~ Nonhome_cat , data=., family = poisson(link=log))

output_model[[9]] <- 
contact_count_wide %>% 
  glm(School~ Work_cat , data=., family = poisson(link=log))

# Effects of other layers on work 
output_model[[10]] <- 
contact_count_wide %>% 
  glm(Work~ Home_cat, data=., family = poisson(link=log))

output_model[[11]] <- 
contact_count_wide %>% 
  glm(Work~ School_cat , data=., family = poisson(link=log))

output_model[[12]] <- 
contact_count_wide %>% 
  glm(Work~ Nonhome_cat , data=., family = poisson(link=log))



names(output_model) <- c(  "h_w", "h_nh", "h_s",  "nh_h", "nh_s", "nh_w", "s_h", "s_nh", "s_w", "w_h", "w_s", "w_nh")

if (output_type == "summary"){

output_model_summary <- rbind(c("h", rep(NA,3)),
               summary(output_model[[1]])$coefficients %>% round(.,2),  summary(output_model[[2]])$coefficients %>% round(.,2) ,  summary(output_model[[3]])$coefficients %>% round(.,2)  ,
                              c("nh", rep(NA,3)),
                               summary(output_model[[4]])$coefficients %>% round(.,2) ,  summary(output_model[[5]])$coefficients %>% round(.,2) , summary(output_model[[6]])$coefficients %>% round(.,2) , 
                              c("s", rep(NA,3)),
                               summary(output_model[[7]])$coefficients %>% round(.,2) ,  summary(output_model[[8]])$coefficients %>% round(.,2) ,  summary(output_model[[9]])$coefficients %>% round(.,2) ,
                              c("w", rep(NA,3)),
                               summary(output_model[[10]])$coefficients %>% round(.,2) ,  summary(output_model[[11]])$coefficients %>% round(.,2) ,  summary(output_model[[12]])$coefficients %>% round(.,2) )
} else if (output_type == "model") {
output_model
} else if (output_type == "data") { # categorized data
contact_count_wide
}
}

# Rural, Bivariate predictors, assessing association between layers
layer_rural_assoc_bi <- 
assoc_btw_layers(contact_count_wide = contact_count_wide_rural, category_type = "binary", output_type = "model")
layer_rural_assoc_bi_summary <- 
assoc_btw_layers(contact_count_wide = contact_count_wide_rural, category_type = "binary", output_type = "summary")
layer_rural_assoc_bi_summary[-c(2,4,6, 9,11,13, 16, 18, 20, 23, 25, 27),]


## Effect of the work layer on home layer
#### The following script is adapted from "NetParams.R" in ARTnet
h_w <- predict(layer_rural_assoc_bi$h_w, newdata = data.frame(Work_cat = factor(1) # characterize the MD of home explained by work contact 
                                                 ), 
                type = "response", interval = "confidence") %>% as.numeric()/2 # we add 2 here to covert the two-day MD to single-day MD


## effect of the work and non-home layers on home layer 
###Given the non home layer is also significant, we use a multivariate model to adjust for the effects of work and nonhome on home
 layer_rural_assoc_bi_data <- 
 assoc_btw_layers(contact_count_wide = contact_count_wide_rural, category_type = "binary", output_type = "data")
layer_rural_assoc_h_w_nh <- 
layer_rural_assoc_bi_data %>% 
  glm(Home~ Work_cat + Nonhome_cat, data=., family = poisson(link=log)
      ) 

layer_rural_assoc_h_w_nh %>% summary() # both layer predictors are significant and negative in the multivariate model

#### characterize the MD of home explained by work and nonhome contacts 
h_w_nh <-  predict(layer_rural_assoc_h_w_nh, 
                   newdata = data.frame(Work_cat = factor(1), 
                                        Nonhome_cat = factor(1)
                                                 ), 
                type = "response", interval = "confidence") %>% as.numeric()/2

#### compare h_w and h_w_nh to the observed overall MD at home
network_stats_rural$edge %>% filter(contact_location == "Home") ; h_w; h_w_nh # as expected, the MD adjusting for the two other layers is lower. 

# Characterize target stats 
## When the predictor is one layer
deg.h_w.dist <- prop.table(table(layer_rural_assoc_bi_data$Work_cat))
##  nodefactor("deg.work") under 1 predictor, the proportion is (total nodes)*prop(==1)*(predicted MD)
1e4*deg.h_w.dist[-1]*h_w

## When the predictors are two layers
### line 419 -428 
### line 427 get a proportion of in both home and work? seems hard to adapt as the two layers are not the same as the causal attribute and geography in ARTnet


## Urban, Bivariate predictors, assessing all association between layers
layer_urban_assoc_bi <- 
assoc_btw_layers(contact_count_wide = contact_count_wide_urban, category_type = "binary", output_type = "model")
layer_urban_assoc_bi_summary <- 
assoc_btw_layers(contact_count_wide = contact_count_wide_urban, category_type = "binary", output_type = "summary")
layer_urban_assoc_bi_summary[-c(2,4,6, 9,11,13, 16, 18, 20, 21, 23, 25, 27),]


# Multivariate predictors
layer_rural_assoc_multi  <- 
assoc_btw_layers(contact_count_wide = contact_count_wide_rural, category_type = "nonbinary", output_type = "summary"
                 )


layer_urban_assoc_multi  <- 
assoc_btw_layers(contact_count_wide = contact_count_wide_urban, category_type = "nonbinary", output_type = "summary")






```



```{r}

network_stats$rural$correlate$h_w <- h_w
network_stats$rural$correlate$deg_w_dist <- deg.h_w.dist 

network_stats$rural$nodemix$Home
network_stats_1$rural$nodemix$Home


saveRDS(network_stats, file = "~/Documents/GitHub/COVID-GlobalMix/data/network_params/formation_stats.RData")


```

## Contact durations
For duration at the home layer, we assume it to be non-dissolving so it would be a large number. For duration at the nonhome layer, we assume it refreshes daily. The duration of the school and work layer is characterized in the following way. We tabulate time of knowing a contact and contact frequency to retrieve the distribution of daily contact under categories of the duration of knowing the contact. For a contact is known less than ≤ 10 years, we took the mid point of each know contact category as the duration. For a contact is know > 10 years, we the population average of the mid point between participant's age and 10 year as the duration. We multiple the proportion of daily contact (as weight) and the duration to calculate the known duration. There are few contact whose participants' age is less than the reported know contact duration of > 10 yrs, randering the characterized duration to be <0; we used the participant's age as the duration for these observations.
```{r}

know_dur <- function(india_mix.){
  
  #  Characterize the known duration for known_contact >10 yrs
known_dur_gt_10yr <- india_mix. %>% 
  filter(known_contact == ">10 yrs" & contact_location %in% c( "School", "Work" )
                                  ) %>%
  #  the known duration is the middle point between 10 yrs and participants age
    mutate(known_duration = (participant_ageyr - 10)/2
           ) %>% 
  # for participants whose characterized know duration < 0, we consider the known duration the same as participant's age.
    mutate(
      known_duration = case_when(known_duration <= 0 ~ participant_ageyr,
                                 known_duration > 0 ~ known_duration) 
    )

  # Avg. known duration of contact in days by network and layer
known_dur_gt_10yr <- 
known_dur_gt_10yr %>% 
  group_by(study_site, contact_location) %>% 
  summarize(known_contact_avg = mean(known_duration)*365) %>% ungroup()

known_duration <-
india_mix. %>% 
  # characterize  frequency of daily contact 
  filter(contact_location %in% c("School", "Work")) %>% 
  group_by(study_site, contact_location, frequency_contact, known_contact) %>% 
  tally() %>% 
  spread(frequency_contact,n) %>% data.frame() %>% rename(daily = Daily..almost.daily) %>% 
  select(study_site, contact_location, known_contact, daily ) %>% 
  filter(!is.na(known_contact)) %>% # filter out the empty category
  ungroup() %>% 
  # characterize mid point for known duration for categories except <= 10yrs
    mutate(know_contact_d = # median duration in days
           case_when(known_contact=="Never met before" ~0, 
                     known_contact=="<1 yr" ~182, # mid. point
                     known_contact=="1-2 yrs" ~ 548,# mid. point
                     known_contact=="3-5 yrs" ~ 1460,# mid. point
                     known_contact=="6-10 yrs" ~ 2922,# mid. point
                     # Avg. know duration of contact for known_contact >10 yrs
                     known_contact==">10 yrs" & study_site == "Rural" & contact_location == "School" ~ 
                       known_dur_gt_10yr %>% filter( study_site == "Rural" & contact_location == "School") %>% 
                       select(known_contact_avg) %>% as.numeric(),
                      known_contact==">10 yrs" & study_site == "Rural" & contact_location == "Work" ~ 
                       known_dur_gt_10yr %>% filter( study_site == "Rural" & contact_location == "Work") %>% 
                       select(known_contact_avg) %>% as.numeric(),
                      known_contact==">10 yrs" & study_site == "Urban" & contact_location == "School" ~ 
                       known_dur_gt_10yr %>% filter( study_site == "Urban" & contact_location == "School") %>% 
                       select(known_contact_avg) %>% as.numeric(),
                      known_contact==">10 yrs" & study_site == "Urban" & contact_location == "Work" ~ 
                       known_dur_gt_10yr %>% filter( study_site == "Urban" & contact_location == "Work") %>% 
                       select(known_contact_avg) %>% as.numeric(),
                     )
           ) %>% 
  group_by(study_site, contact_location) %>% 
  
  mutate(
     daily_prop = daily/sum(daily, na.rm = T), # proportion of daily contact under each know_contact cateogry
     weighted_known_contact_d = know_contact_d*daily_prop # duration of known contact weighted by daily contact proportion
  ) %>%   
  # weighted avg. of duration of contact
  summarize(know_contact_duration_avg = sum(weighted_known_contact_d, na.rm = T)
            ) %>% ungroup()
  
}
known_duration <- know_dur(india_mix. = india_mix)

#saveRDS(known_duration, file = "~/Documents/GitHub/COVID-GlobalMix/data/network_params/known_dur_school_work.RData")







```



