---
title: "Network Modeling for GlobalMix India Data"
author: "Billy Dehao Chen"
date: "9/8/2023"
output: word_document
editor_options: 
  chunk_output_type: console
---

# Background
This is a living document for network modeling of the India GlobalMix diary data. For practice, the current modeling focuses on the setting of home mixing in the rural area and will be expanded to other networks later.

# Method
We adopted the approaches for calculating target statistics in Corp Mix in this analysis. 

```{r, echo=F, warning=F, message=FALSE}
lapply(c("tidyverse", "EpiModel", "ggpubr", "knitr", "svglite", "kableExtra"), require, character.only = TRUE)


# load contact data----------------------------------------

# 'raw'  mixing data by mean degree for one day
gm.raw <- readRDS("../data/network_params/india_mix.sum.no15.RData")
# daily mixing matrix
matrices <- readRDS("../data/network_params/avg.matrices.india.RData") 

#  daily mixing matrix by mean degree


# function to calculate degree information for later deriving of target statistics
md.info <- function(raw_contact,sym.matrix){ # it'd be better to organize things in list for this.
  
  output <- list()
  
  # mean degree by network layer (contact location)
  output[[1]] <- raw_contact  %>% group_by(contact_location, participant_age, n_participants) %>% 
  summarise(n_contacts = sum(n_contacts)) %>%
  ungroup() %>%
  group_by(contact_location) %>%
  summarise(n_contacts = sum(n_contacts),
            n_participants = sum(n_participants)) %>%
  mutate(md = (n_contacts/n_participants)/2)
  
  # total daily degree of edges per age group for nodefactor()
  output[[2]] <- 
  rbind(
  sym.matrix %>%
  filter(contact_location == "Home") %>%
  select(total_degree) %>%
  as_vector() %>%
  as.numeric(),
  
  sym.matrix %>%
  filter(contact_location == "Nonhome") %>%
  select(total_degree) %>%
  as_vector() %>%
  as.numeric(),
  
  sym.matrix %>%
  filter(contact_location == "School") %>%
  select(total_degree) %>%
  as_vector() %>%
  as.numeric(),
  
  sym.matrix %>%
  filter(contact_location == "Work") %>%
  select(total_degree) %>%
  as_vector() %>%
  as.numeric()
  
  
  )
  row.names(output[[2]]) <- c("Home", "Nonhome", "School", "Work"); colnames(output[[2]]) <- levels(sym.matrix$age); 
  output[[2]] <- as.data.frame(output[[2]])
  
  # proportion of daily within-age-group matching by contact_location
  output[[3]] <- sym.matrix  %>% 
  mutate(within_age_edges = total_degree*prop_match) %>% # at the daily scale
  select(contact_location,age,total_degree,within_age_edges) %>%
  group_by(contact_location) %>%
  summarise(total_degree = sum(total_degree),
            within_age_edges = sum(within_age_edges)) %>%
  mutate(match = within_age_edges/total_degree) %>% as.data.frame() # at the daily scale
  
  names(output) <- c("md.layer", # md by contact location
                     "md.ag", # md by age group
                     "within.ag.match.prop")
  
  output
}

md.info.rural <-md.info(raw_contact = gm.raw$india_mix.sum.no15.rural.6age.grps,
                        sym.matrix = matrices$avg.matrix.india.rural$avg.matrix %>%
                         ungroup()
                        ) ## rural


md.info.urban <- md.info(raw_contact = gm.raw$india_mix.sum.no15.urban.6age.grps,
                         sym.matrix =  matrices$avg.matrix.india.urban$avg.matrix %>%
                         ungroup()
                         ) ## urban



```

## Age distribution of target population
```{r, warning=F, message=FALSE, echo=T, fig.height=7}
# age group of GM

target_age_grp <- matrices$avg.matrix.india.rural.6age.grps$avg.matrix$age %>% levels()
total_pop_rural <- c(199+750+933,1017+958,1196+1195,1309+1272,1215+1088+1067+876,777+626+499+321+437)
total_pop_urban <-c(309+1144+1458,1474+1814,1805+1731,1740+1669,1471+1395+1206+975,891+572+412+236+245)
target_age_dist <- data.frame(target_age_grp=rep(target_age_grp,2),
                              total_pop=c(total_pop_rural, total_pop_urban),
                              network=rep(c("rural", "urban"), each = length(target_age_grp))
                              )

# proportion of target population in each age group by network
target_age_dist$prop <- c(target_age_dist[target_age_dist$network=="rural", ]$total_pop/sum(total_pop_rural),                                    target_age_dist[target_age_dist$network=="urban", ]$total_pop/sum(total_pop_urban)
                                                              )

ggarrange(
target_age_dist %>% ggplot(aes(x=target_age_grp, y=total_pop))+geom_bar(stat = "identity")+facet_wrap(~network)+
  geom_text(aes(label=total_pop), vjust=-0.3, size=3.5)+
  theme_classic()+ylab("Population")+xlab("Age group"),
target_age_dist %>% ggplot(aes(x=target_age_grp, y=prop))+geom_bar(stat = "identity")+facet_wrap(~network)+
  geom_text(aes(label=round(prop,2)), vjust=-0.3, size=3.5)+
  theme_classic()+ylab("Population proportion")+xlab("Age group"),
nrow = 2
)
```




## Set up model attribute and characterize target statistics
```{r, warning=F, message=FALSE, echo=T}
############## Set up vertex attribute ##############
# nodes
n <- 10000 #each for the two networks
nw_rural <- nw_urban <- network_initialize(n)

## nodes in rural network
n_pop_rural <- 
(n*target_age_dist$prop[target_age_dist$network == "rural"]) %>% round() # number of nodes in each age group for the target population

## age attribute
age.grp_rural <- c(rep(1, n_pop_rural[1]), rep(2, n_pop_rural[2]), rep(3, n_pop_rural[3]), rep(4, n_pop_rural[4]),rep(5, n_pop_rural[5]),rep(6, n_pop_rural[6])) # single nodes indicated by age group; use 1 to 6 to represent nodes in each age group

min_age <- c(0,10,20,30,40,60); max_age <- c(9,19,29,39,59,100) # age ranges

## Number of target population within each age group
age.grp.num_rural <- as.numeric(table(age.grp_rural)
                                ) 

age_rural <- c()
for (i in 1:6) {
  age_rural <-
    c(
    age.grp.num_rural[i],
  runif(n= sum(age.grp_rural ==i),# the number of node to simulate in each group equals to the number of target target population in each group
      min=min_age[i], max=max_age[i]) # age range in each age group
  )
}

cbind(age.grp_rural, age_rural)  %>% View()                                           
                                          
## nodes in urban network
# n_pop_urban <- 
# (n*target_age_dist$prop[target_age_dist$network == "urban"]) %>% round()
# 
# age.grp_urban <- c(rep(1, n_pop_urban[1]), rep(2, n_pop_urban[2]), rep(3, n_pop_urban[3]), rep(4, n_pop_urban[4]),rep(5, n_pop_urban[5]),rep(6, n_pop_urban[6]))

### Initialize a rural network, home layer
nw_rural <- set_vertex_attribute(nw_rural, "age", age_rural)
nw_rural <- set_vertex_attribute(nw_rural, "age.grp", age.grp_rural)

############## Model target statistics ##############
# within home network

### Total Edges
md.h <- md.info.rural$md.layer %>% filter(contact_location == "Home") %>% select(md) %>% as.numeric() # mean degree of all contact
edges.h <- md.h * n/2 # the reason /2 is used here is because this is a edge-level statistic

### Number of edges per age group
md.h.ag_rural <- # mean degree of edge in each age group
  matrices$avg.matrix.india.rural.6age.grps$avg.matrix %>% filter(contact_location == "Home")%>% 
  select(total_degree) %>%
  as_vector() %>%
  as.numeric()
nf.h.ag <- md.h.ag_rural * age.grp.num_rural # daily total degree * total number of people in each age group = number of edges per age group

###  Number of edges involved in within-group mixing
#### Proportion of daily within-group mixing 
match.h.ag <-
  md.info.rural$within.ag.match.prop %>% filter(contact_location == "Home") %>% 
  select(match) %>%
  as.numeric()

nm.hh.ag <- edges.h * match.h.ag # number of matched nodes in the target population

```

## Model fitting and simulation
```{r, warning=F, message=FALSE, echo=T}
#### Model's formulation
formation.edge <- ~edges 
formation.edge.nf <- ~edges + nodefactor("age.grp" , levels = 2:6) 
formation.edge.nf.nm <- ~edges + nodefactor("age.grp" , levels = 2:6) + nodematch("age.grp")
coef.diss.h <- dissolution_coefs(dissolution = ~offset(edges), duration = 1e6) 

#### Compiling target statistics
target.stats.edges.h <- c(edges.h)
target.stats.edges.nf.h <- c(edges.h, nf.h.ag[2:6]) # excluded the first group
target.stats.edges.nf.nm.h <-  c(edges.h, nf.h.ag[2:6], nm.hh.ag) 



```


```{r, warning=F, message=FALSE, echo=T}
# Edge-only model
## Fit edge-only model to data
est.h.edges <- netest(nw_rural, formation.edge, target.stats.edges.h, coef.diss.h,
                 set.control.ergm = control.ergm(MCMLE.maxit = 500)
                 )

## Simulate based on the edge model for only the edge effect
dx.h.edges_obs<- netdx(est.h.edges, nsims = 100, ncores = 8, 
                   nsteps = 1000, dynamic = T,
               set.control.ergm = control.simulate.formula(MCMC.burnin = 1e6),
               nwstats.formula = ~edges  , 
               keep.tedgelist = TRUE)

## Extract summary statistics from simulation
dx.h.edges_obs$stats.table.formation %>% select(2, 4) %>%
  #filter(!row_number() %in% c(1)) %>% 
  mutate(Sim_mean_ci_low = `Sim Mean` -1.96*`Sim SE`,
         Sim_mean_ci_up = `Sim Mean` +1.96*`Sim SE`) %>% 
  rownames_to_column(var= "age.grp") %>% 
  
 select(-`Sim SE`)%>% cbind(., observed_nf =target.stats.edges.h) %>% select(1,5,2:4)
 
print(dx.h.edges_obs)

```

```{r, warning=F, message=FALSE, echo=T}
## Simulate based on the edge model adding an extra term, 
dx.h.edges.nf_sim<- netdx(est.h.edges, nsims = 100, ncores = 8, 
                   nsteps = 1000, dynamic = T,
               set.control.ergm = control.simulate.formula(MCMC.burnin = 1e6),
               nwstats.formula = ~edges  + nodefactor("age.grp"), 
               keep.tedgelist = TRUE)
print(dx.h.edges.nf_sim)

## Extract summary statistics from simulation
dx.h.edges.nf_sim$stats.table.formation %>% select(2, 4) %>%
  #filter(!row_number() %in% c(1)) %>% 
  mutate(Sim_mean_ci_low = `Sim Mean` -1.96*`Sim SE`,
         Sim_mean_ci_up = `Sim Mean` +1.96*`Sim SE`) %>% 
  rownames_to_column(var= "age.grp") %>% 
  mutate(age.grp=str_replace(age.grp,  "nodefactor.age.grp.", "")
  ) %>% 
 select(-`Sim SE`)%>% cbind(., observed_nf =target.stats.edges.nf.h)%>% select(1,5,2:4)

dx.h.edges.nf_sim %>% plot()

```

The table below suggests the edge statistics is still more biased than the edge-only simulation after included the observed nodefactor data
```{r, warning=F, message=FALSE, echo=T}
# Model with target statistics of edge and node factor
## Fit  model to data
est.h.edges.nf <- netest(nw_rural, formation.edge.nf, target.stats.edges.nf.h, coef.diss.h,
                 set.control.ergm = control.ergm(MCMLE.maxit = 500)
                 )
## Simulate 
dx.h.edges.nf_obs <- netdx(est.h.edges.nf, nsims = 100, ncores = 8, 
                   nsteps = 1000, dynamic = T,
               set.control.ergm = control.simulate.formula(MCMC.burnin = 1e6),
               nwstats.formula = ~edges  + nodefactor("age.grp"), 
               keep.tedgelist = TRUE)

dx.h.edges.nf_obs %>% print()
## Extract summary statistics from simulation
dx.h.edges.nf_obs$stats.table.formation %>% select(2, 4) %>%
 # filter(!row_number() %in% c(1)) %>% 
  mutate(Sim_mean_ci_low = `Sim Mean` -1.96*`Sim SE`,
         Sim_mean_ci_up = `Sim Mean` +1.96*`Sim SE`) %>% 
  rownames_to_column(var= "age.grp") %>% 
  mutate(age.grp=str_replace(age.grp,  "nodefactor.age.grp.", "")
  ) %>% 
 select(-`Sim SE`) %>% cbind(., observed_nf =target.stats.edges.nf.h ) %>% select(1,5,2:4)

```

After adding the nodematch term in the simulation, the bias of the edge effect is lower than the edge-only model. Is this a conincendence?
```{r, warning=F, message=FALSE, echo=T}
## Simulate w/ node match
dx.h.edges.nf.nm_sim <- 
  netdx(est.h.edges.nf, nsims = 100, ncores = 8, 
                   nsteps = 1000, dynamic = T,
               set.control.ergm = control.simulate.formula(MCMC.burnin = 1e6),
               nwstats.formula = ~edges  + nodefactor("age.grp") + nodematch("age.grp"), 
               keep.tedgelist = TRUE)

dx.h.edges.nf.nm_sim$stats.table.formation %>% select(2, 4) %>%
  #filter(!row_number() %in% c(1)) %>% 
  mutate(Sim_mean_ci_low = `Sim Mean` -1.96*`Sim SE`,
         Sim_mean_ci_up = `Sim Mean` +1.96*`Sim SE`) %>% 
  rownames_to_column(var= "age.grp") %>% 
  mutate(age.grp=str_replace(age.grp,  "nodefactor.age.grp.", "")
  ) %>% 
 select(-`Sim SE`) %>% cbind(., observed_nf = target.stats.edges.nf.nm.h
                             ) %>% select(1,5,2:4)


```

Now the bias of the edge effect is bigger again after including the observed nodematch data.
```{r, warning=F, message=FALSE, echo=T}
# Model with target statistics of edge and node factor and node match

## Fit  model to data
est.h.edges.nf.nm <- netest(nw_rural, formation.edge.nf.nm, target.stats.edges.nf.nm.h, coef.diss.h,
                 set.control.ergm = control.ergm(MCMLE.maxit = 500)
                 )
## Simulate 
dx.h.edges.nf.nm_obs<- netdx(est.h.edges.nf.nm, nsims = 100, ncores = 8, 
                   nsteps = 1000, dynamic = T,
               set.control.ergm = control.simulate.formula(MCMC.burnin = 1e6),
               nwstats.formula = ~edges  + nodefactor("age.grp") + nodematch("age.grp"), 
               keep.tedgelist = TRUE
               )

dx.h.edges.nf.nm_obs %>% print()
dx.h.edges.nf.nm_obs$stats.table.formation %>% select(2, 4) %>%
  #filter(!row_number() %in% c(1)) %>% 
  mutate(Sim_mean_ci_low = `Sim Mean` -1.96*`Sim SE`,
         Sim_mean_ci_up = `Sim Mean` +1.96*`Sim SE`) %>% 
  rownames_to_column(var= "age.grp") %>% 
  mutate(age.grp=str_replace(age.grp,  "nodefactor.age.grp.", "")
  ) %>% 
 select(-`Sim SE`) %>% cbind(., observed_nf = target.stats.edges.nf.nm.h
                             )%>% select(1,5,2:4)

```














