---
title: "Network Modeling for GlobalMix India Data"
author: "Billy Dehao Chen"
date: "7/6/2023"
output: word_document
---

# Background
This is a living document for network modeling of the India GlobalMix diary data. For practice, the current modeling focuses on the the mixing at home and will be expanded to other settings later (nonhome, rural, urban) (discussion point).

# Method
## Retrieving degree information from the India data
We used the daily mean degree data by network predictor (e.g., contact location), participant's age group, and contact's age group to calculate the total mean degree by network predictor's category (home/nonhome). We retrieved the total daily degree of each age group from the symmetric contact matrix, from which we also calculated the proportion of within-age-group matching by network predictor.

```{r, echo=F, warning=F, message=FALSE}
library(tidyverse)
library(socialmixr)
library(EpiModel)
library(ggpubr)
library(knitr)

# things to be completed - sync to git, average age of participants


# load contact data----------------------------------------

# 'raw'  mixing data by mean degree for one day
gm <- readRDS("../output/data/india_mix.sum.no15.RData")[[2]] # mixing degree by contact location
# daily mixing matrix
matrix <- readRDS("../output/data/avg.matrix.india.predictors.RData") 

#  daily mixing matrix by mean degree
gm2 <- matrix$avg.matrix.india.contact_location$avg.matrix %>%
  rename(contact_location = predictor_contact) %>% # for now, we will initiate the model by contact location
  ungroup()
rm(matrix)

# total mean degree by contact location using raw data
md <- gm %>%
  group_by(contact_location,p_age,n_participants) %>%
  summarise(n_contacts = sum(n_contacts)) %>% # the sum of two-day contacts
  ungroup() %>%
  group_by(contact_location) %>%
  summarise(n_contacts = sum(n_contacts), #  total contacts over two days
            n_participants = sum(n_participants)) %>%
  mutate(md.daily = (n_contacts/n_participants)/2) # mean degree at daily scale

# Total daily mean degree from the global mix data
md.h <- md %>%
  filter(contact_location == "Home") %>%
  select(md.daily) %>%
  as.numeric()

#  total daily degree of edges per age group for nodefactor()
md.h.ag <- gm2 %>%
  filter(contact_location == "Home") %>%
  select(total_degree) %>%
  as_vector() %>%
  as.numeric()

# proportion of daily within-age-group matching by contact_location
md.match <- gm2  %>% 
  mutate(within_age_edges = total_degree*prop_match) %>% # at the daily scale
  select(contact_location,age,total_degree,within_age_edges) %>%
  group_by(contact_location) %>%
  summarise(total_degree = sum(total_degree),
            within_age_edges = sum(within_age_edges)) %>%
  mutate(match = within_age_edges/total_degree) # at the daily scale


```

### Total mean degree of the whole network by contact location.
```{r, warning=F, message=FALSE, echo=F}
kable(md)
```

### Total daily degree of edges from age groups 1 to 10
```{r, warning=F, message=FALSE, echo=F}
md.h.ag
```

### Proportion of daily within-age-group matching by contact location
```{r, warning=F, message=FALSE, echo=F}
kable(md.match)
```

## Modeling
### Network set-up
As a start, we set up the network in the following way. The following distribution for age was chosen arbitrary for practice, so this needs to be strengthened by better knowing the age distribution of the target population (discussion point).

```{r, warning=F, message=FALSE, echo=T}
### nodes
n <- 10000 

### age group
age <- round(rnorm(n, mean = 39, sd = 21), 1) # arbitrary select mean and sd to Define age.
age <- pmax(age, 0) # if an obs. w/ age < 0, assign 0 to this obs.
age <- pmin(age, 99)

age.breaks <- seq(0, 100, 10)
age.grp <- cut(age, age.breaks, labels = FALSE, right = FALSE) # divide age into 10 even groups

nw <- network.initialize(n)
nw <- set_vertex_attribute(nw, "age.grp", age.grp)
hist(age)
```

### Models
#### Formation model
We explored the following model. For the model adjusting for heterogeneity by age group, we excluded the 10th group to make the model runnable. This age group has the lowest target statistic of 381. The ten age groups refer to those of the study population, i.e., "<6mo", "6-11mo", "1-4y", "5-9y", "10-14y", "15-19y", "20-29y", "30-39y", "40-59y", "60+y".
```{r, warning=F, message=FALSE, echo=T}
formation.edge <- ~edges 
formation.edge.nf <- ~edges + nodefactor("age.grp" , levels = 1:9) # dropping the 10th age group
```

#### Dissolution model
```{r, warning=F, message=FALSE, echo=T}
coef.diss.hh <- dissolution_coefs(dissolution = ~offset(edges), duration = 100000) 
```

#### Calculating target statistics
We used the following script to calculate the target statstics. The target statistics for the model with "edges" and "nodefactor" terms is shown at the bottom of the following output.
```{r, warning=F, message=FALSE, echo=T}
### Total Edges, at daily scale
edges.h <- md.h * n/2 

### Number of edges per age group, at daily scale
#### Number of target population within each age group
age.grp.num <- as.numeric(table(age.grp)) 
#### Number of edges per age group for nodefactor(), at daily scale
nf.h.ag <- md.h.ag * age.grp.num # daily total degree * total number of people in each age group = number of edges per age group

###  Number of edges involved in within-group mixing
#### Proportion of daily within-group mixing 
#match.h.ag <- md.match$match[md.match$contact_location == "Home"]
#### for nodematch()
#nm.hh.ag <- edges.h * match.h.ag
target.stats.edges.h <- c(edges.h)
target.stats.edges.nf.h <- c(edges.h, nf.h.ag[1:9]) # excluded group 10 with the lowest degree
target.stats.edges.nf.h
```

#### Edge-only model
We fitted an edge-only model and encountered the following warning (discussion point). Based on its estimates, we simulated networks with edges and nodefactor. The simulation for nodefactor is based on model's guessing.
```{r, warning=F, message=T, echo=T}
## Fit edge-only model to data
est.h.edges <- netest(nw, formation.edge, target.stats.edges.h, coef.diss.hh,
                 set.control.ergm = control.ergm(MCMLE.maxit = 500)
                 )
#### Simulate based on the edge model adding an extra term, 
dx.h.edges.age.grp.est <- netdx(est.h.edges, nsims = 1, ncores = 1, nsteps = 1000, dynamic = T,
               set.control.ergm = control.simulate.formula(MCMC.burnin = 1e6),
               nwstats.formula = ~edges  + 
                 nodefactor("age.grp"), 
               keep.tedgelist = TRUE)
```

```{r, warning=F, message=FALSE, echo=F}
#### Extract summary statistics from simulation
dx.h.edges.age.grp <- 
dx.h.edges.age.grp.est$stats.table.formation %>% select(2, 4) %>%
  filter(!row_number() %in% c(1)) %>% 
  mutate(Sim_mean_ci_low = `Sim Mean` -1.96*`Sim SE`,
         Sim_mean_ci_up = `Sim Mean` +1.96*`Sim SE`) %>% 
  rownames_to_column(var= "age.grp") %>% 
  mutate(age.grp=str_replace(age.grp,  "nodefactor.age.grp.", "")
  ) %>% 
 select(-`Sim SE`)
```

#### Model with edges and nodefactor
We fitted a model with edges and nodefactor and simulated networks with these two terms. The simulation of nodefactor is based on estimates from the observed data.
```{r, warning=F, message=FALSE, echo=T}
## Fit model with edge and nodefactor to data
est.h.edges.nf <- netest(nw, formation.edge.nf, target.stats.edges.nf.h, coef.diss.hh,
                      set.control.ergm = control.ergm(MCMLE.maxit = 500)
                      )
dx.h.edges.age.grp.obs.est <- netdx(est.h.edges.nf, nsims = 1, ncores = 1, nsteps = 1000, dynamic = T,
                            set.control.ergm = control.simulate.formula(MCMC.burnin = 1e6),
                            nwstats.formula = ~edges  + 
                              nodefactor("age.grp", levels =1:9), 
                            #nodefactor("age.grp",levels = NULL), 
                            keep.tedgelist = TRUE) 
```

```{r, warning=F, message=FALSE, echo=F}
dx.h.edges.age.grp.obs <- 
dx.h.edges.age.grp.obs.est$stats.table.formation %>% select(2, 4) %>%
  filter(!row_number() %in% c(1)) %>% 
  mutate(Sim_mean_ci_low_obs = `Sim Mean` -1.96*`Sim SE`,
         Sim_mean_ci_up_obs = `Sim Mean` +1.96*`Sim SE`) %>% 
  rownames_to_column(var= "age.grp") %>% 
  mutate(age.grp=str_replace(age.grp,  "nodefactor.age.grp.", "")
  ) %>%  rename(Sim_mean_obs = `Sim Mean`) %>% select(-`Sim SE`)
```

# Result
We compared the simulated and observed target statistics of age groups. In the following figure, the observed degrees are indicated by black dots. The simulated degrees and their 95% confidence intervals (CIs), based on the edge-only model, are listed in gray. The simulated degrees and their 95% confidence intervals, based on the model with edge and nodefactor, estimated from the observed target statistics, are listed in green. Given the target statistics vary across the age groups, the y axes were plotted at different scale to allow the comparison of the observed and simulated statistics within each age group. Neither the simulated target statistics, based on the model's random guess, nor the ones simulated based on the observed data, have their 95% CIs cover the observed target statistics.

```{r, warning=F, message=FALSE, echo=F, fig.width=7, fig.height=7}
dx.h.edges.age.grp.merge <- 
  full_join(dx.h.edges.age.grp, dx.h.edges.age.grp.obs, by = "age.grp")  %>% 
  mutate(age.grp = as.numeric(age.grp)) %>% 
  arrange(age.grp) %>% 
  mutate(age.grp = factor(age.grp)) %>% 
  bind_cols(target_pop_mean =nf.h.ag)

target.stat.plots <- list()
for (i in 1:length(dx.h.edges.age.grp.merge$age.grp)) {
  
target.stat.plots[[i]] <- 
  dx.h.edges.age.grp.merge %>% filter(age.grp == dx.h.edges.age.grp.merge$age.grp[i]
                                      ) %>% 
  #mutate(as.numeric(as.character(age.grp))) %>% 
  ggplot(aes(x= age.grp, y = `Sim Mean`))+
    geom_point(color = "gray")+
  geom_errorbar(aes(ymin = Sim_mean_ci_low,
                    ymax = Sim_mean_ci_up ), color = "gray")+
  geom_point(aes(x= age.grp, y = Sim_mean_obs), color = "forestgreen")+ # since the 10th age group has the lowest target statistics, it's treated as reference group
  geom_errorbar(aes(ymin = Sim_mean_ci_low_obs,
                    ymax = Sim_mean_ci_up_obs), color = "forestgreen")+
  geom_point(aes(x= age.grp, y = target_pop_mean), color = "black"
  ) + ylab("") +  xlab("") + theme_classic() 
}
annotate_figure(
ggarrange(
target.stat.plots[[1]], target.stat.plots[[2]],target.stat.plots[[3]],target.stat.plots[[4]],target.stat.plots[[5]],
target.stat.plots[[6]],target.stat.plots[[7]],target.stat.plots[[8]], target.stat.plots[[9]],target.stat.plots[[10]],
nrow = 2, ncol = 5
),
bottom = "age.grp", left = "Number of edges"
)
# Note: Given the simulated target statistics of age.group differ from the counterparts of the target population, 
# there is a need to account for this attribute in model estimation.



```

The following table compares the absolute and relative differences between simulated and the observed target statistics by age group; and the comparisons were made for the simulated target statistics based on 1) model's guessing (i.e., "model-guessed simulated target stats"), and 2) estimated target statistics (i.e., "simulated target stats") from the observed data. As the first and last (with the lowest degree) age groups were accordingly chosen by the model as reference groups for 1) and 2), there comparisons were not available.

For 1), we observed the relative difference were less than 10% in groups 3 and 4, while the absolute difference was relative smaller for group 10. The observed and absolute differences for other age groups were large. For 2), we observed biases across age groups reduced after including the observed data in estimation. Nevertheless, given none of the observed target statistics fall within the 95% CIs of their simulated counterparts. The model still needs to be improved. 


```{r, , warning=F, message=FALSE, echo=F}
diff.sim_target <- 
 abs(dx.h.edges.age.grp.merge$`Sim Mean` - dx.h.edges.age.grp.merge$target_pop_mean )  # absolute difference


diff.sim_obs_target <- 
 abs(dx.h.edges.age.grp.merge$Sim_mean_obs - dx.h.edges.age.grp.merge$target_pop_mean) # absolute difference


  table_compare_sim_obs <- 
  as.data.frame(
  rbind(
    round(diff.sim_target),
    paste0(round((diff.sim_target/dx.h.edges.age.grp.merge$target_pop_mean)*100, 2), "%") %>% str_replace("NA%", NA_character_),
    round(diff.sim_obs_target),
    paste0(round((diff.sim_obs_target/dx.h.edges.age.grp.merge$target_pop_mean)*100, 2), "%") %>% str_replace("NA%", NA_character_)
  ),
  row.names = c("Absolute difference btw. model-guessed simulated target stats. & obs. target stats",
                "Relative difference btw. model-guessed simulated target stats. & obs. target stats",
                "Absolute difference btw. simulated target stats. & obs. target stats",
                "Relative difference btw. simulated target stats. & obs. target stats"
                )
  ) 

colnames(table_compare_sim_obs) <- dx.h.edges.age.grp.merge$age.grp


kable(table_compare_sim_obs)

```



# Questions
1. For the India data, the 10 age groups of the data have uneven age gaps while the 10 age groups for the target population have even age gaps. Also, based on the discussion with Moses on 7/10, the age distribution of the study and target populations may not match. How we can resolve these discrepancies?
2. For the dissolution model, it seems duration, a parameter without time unit, can be randomly selected?
3. For the edge-level edge, node-level nodefactor, and edge-level nodematch terms, how the counting twice of edge for nodefactor and counting once for nodematch be reflected in target statistics for estimation and in simulation outputs?
4. Currently, the contacts at home and at other home are combined as contact at home. Is there any issue with this?





