---
title: "Descriptive Degree Summary of GlobalMix India Data"
author: "Billy Dehao Chen"
date: "08/21/2023"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

# Background
This is a descriptive summary of contact degree of the India GlobalMix diary data.

# Method
We adapted the code Maria developed for the CorporateMix data to the GlobalMix data to calculate degree information. The degree information was summarized into four separate networks for two different epidemic models (one rural, one urban). We consider the mixing occurs within locations (urban, rural) and across two types of network layers (home/school/work/nonhome [other than school/work], indoors/outdoors). We do not model contacts across layers, as we assume they are mutually exclusive across environments. We regrouped the age categories in the first two decades of life by decade.


We excluded contacts lasted ≤ 15 mins in analysis. The degree information was summarized as the arithmetic mean of signle-day degrees of contact between group A and group B and between group B and group A of the two-day visits. Given the data were egocentric, we use $M.D.=\frac{edges}{n}$ for the relationship between mean degree ($M.D.$) and the number of edges.


```{r, echo=F, warning=F, message=FALSE, include = FALSE}
# Load libraries and data  ------------------------------------------------
lapply(c("ggpubr", "statnet", "EpiModel", "tidyverse", "socialmixr", "knitr",  "sjlabelled", "kableExtra", "broom"), require, character.only = TRUE)


## participant data
india_participant <- 
#readRDS("~/Documents/GitHub/COVID-GlobalMix/data/participant_contact/india_participant_data_aim1.RDS")%>% rename(id = rec_id)
readRDS("../data/participant_contact/india_participant_data_aim1.RDS")%>% rename(id = rec_id)


## contact data 
india_contact <- 
 #readRDS("~/Documents/GitHub/COVID-GlobalMix/data/participant_contact/india_contact_data_aim1.RDS")%>% rename(id = rec_id)
readRDS("../data/participant_contact/india_contact_data_aim1.RDS")%>% rename(id = rec_id)

# Note - validated study_site of participant is exactly the same as those in contact

# Reclassifying participant's and contact's age groups into 0-9 years old, 10-19 years old, while treating other age groups as is.
## participant
india_participant <- 
india_participant %>% 
  mutate(
      participant_age_reclass = case_when(
        participant_age %in% c("<6mo", "6-11mo",   "1-4y",   "5-9y") ~ "0-9y",
        participant_age %in% c("10-14y", "15-19y") ~ "10-19y",
        .default =  participant_age
      )
    )%>% 
  mutate(participant_age_reclass= factor(participant_age_reclass, levels=c("0-9y", "10-19y", "20-29y", "30-39y", "40-59y",   "60+y")
                                         )
         ) 

## contact
india_contact <- 
india_contact %>%     
  mutate(
      contact_age_reclass = case_when(
        contact_age %in% c("<6mo", "6-11mo",   "1-4y",   "5-9y") ~ "0-9y",
        contact_age %in% c("10-14y", "15-19y") ~ "10-19y",
        .default =  contact_age
      )
    )%>% 
    mutate(contact_age_reclass= factor(contact_age_reclass, levels=c("0-9y", "10-19y", "20-29y", "30-39y", "40-59y",   "60+y")
                                         )
         )

# merge participants and contact datasets and process data  and basic data processing ------------------------------------------------
india_mix <- india_participant %>%
  dplyr::select(id,participant_age, participant_age_reclass) %>%
  right_join(india_contact,
            by = "id") %>% 
  # characterization of home/nonhome status
   mutate(contact_location = case_when(location_contact___0 == 1  ~ "Home", # 0 - "My home"
                                            location_contact___2 == 1 & location_contact___0 == 0 ~ "School", # "School" but not "my home"
                                             location_contact___3 == 1 & location_contact___0 == 0 ~ "Work", # "work" but not "my home"
                                       
                                       
                                       (
                                       location_contact___1 == 1 | location_contact___4 == 1 | # "Other home",  "Transport/Hub"
                                       location_contact___5 == 1 | location_contact___6 == 1 | # "Market/Shop", "Street"
                                       location_contact___7 == 1 | location_contact___8 == 1 | # "Playground", "Well"
                                       location_contact___9 == 1 | location_contact___10 == 1 | # "Agricultural Field", "Market/Shop"
                                       location_contact___11 == 1 | location_contact___12 == 1 | # "Restaurant", "Religious centre"
                                       location_contact___13 == 1 | location_contact___14 == 1 | # "Govt offices", "Health center"
                                       location_contact___15 == 1 | location_contact___16 == 1 | # "Bank", "Movie theatre"
                                       location_contact___17 == 1 | location_contact___18 == 1 | location_contact___19 == 1 #"Exhibition", "Social hall", "Other"
                                       ) &
                                         !(location_contact___3 == 1 | location_contact___2 == 1) # Excluding work/school
                                       
                                       ~ "Nonhome") # assign contacts into home or nonhome layer
         )  %>% 
  mutate(contact_location = factor(contact_location,
                                   # levels = c("Home","Nonhome"),
                                    ordered = TRUE)
         ) %>% 
  mutate(duration_contact = case_when(duration_contact == ">4 hrs" ~ "4+ hrs",
                                      .default = duration_contact),
         duration_contact = factor(duration_contact,
                                    levels = c("<5 mins", "5-15 mins", "16-30 mins",  
                                               "31 mins-1 hr", "1-4 hrs", "4+ hrs", "Unknown"),
                                    ordered = TRUE)
         )

```
## Characterization of network layers
The network layers is processed from multiple questions asking contact locations. Given these questions are not mutually exclusive due to the check-box design in REDCap, a contact is characterized as at home when any contact with a participant reportedly occurred at the participant's home (i.e., "my home")  regardless of the responses for other contact location types. The contacts occurred at other's home is considered as a non-home contact: given the sociological contact pattern in a participant's residence and other’s home is likely vary, we consider contacts occurring at home and others' home separately.
For contacts occurred at work or school, we assigned them into one of these categories. For the two contacts (shown below) that occurred at both work (location 3 in REDCap) and school (location 2), we categorized them as at school, considering the contacts were at school age.
For non-home contacts excluding work and school, we categorize them into the non-home category.
For a contact checked non of the categories, we assigned an NA to this contact.

```{r, echo=F, warning=F, message=FALSE}
india_mix %>% select(participant_age, contact_age, location_contact___2, location_contact___3) %>% mutate(sum = location_contact___2+location_contact___3) %>% filter(sum==2) %>% select(-sum)%>%  kable() %>%  kableExtra::kable_classic(full_width = F, html_font = "Cambria")
```

Below is a breakdown of the frequency of contact. We excluded contacts of the NA category in analysis.
```{r, echo=F, warning=F, message=FALSE}
india_mix %>% 
  group_by( contact_location, study_site) %>%
  tally() %>%  spread(study_site, n) %>% kable()%>%
   kableExtra::kable_classic(full_width = F, html_font = "Cambria")
```

## Distribution of indoor/outdoor status
The following is a break down of the observed categories of the variable "where_contact" indicating in- and out-door status. In the original data, there is a "Both" category indicates a participant contacted with a contact both in- and out-doors.  Since the "Both" category could have a higher transmission potential similar to the "Indoors" category, we merge the "Both" into the "Indoors" category. We will adjust for this status as a nodefactor. For building the transmission model, we will assign lower risk for the "Outdoors" category during simulation.


```{r, echo=F, warning=F, message=FALSE}
# merge the both and indoor categories into the latter.
india_mix <-
india_mix %>% mutate(where_contact2=case_when(where_contact %in% c("Indoors", "Both") ~ "Indoors",
                                              .default = where_contact)
                     )

india_mix %>% 
  group_by( where_contact2, study_site) %>%
  tally() %>%  spread(study_site, n) %>% kable()%>%
   kableExtra::kable_classic(full_width = F, html_font = "Cambria")

#chisq.test(table(india_mix$contact_location, india_mix$study_site))
```

## Repeated contacts
For repeated contacts at the home layer, we deduplicate them in the analysis. Current investigation is ongoing to decide how to deal with replicated contact in the other layers.
### Distribution of unique/repeated contacts
The following table shows the distribution of repeated/unique contact by network layers of each network. The levels of replicated contact is high across layers in both networks.
```{r, echo=F, warning=F, message=FALSE}

kbl(list(
           india_mix %>% filter(study_site == "Rural") %>% #drop_na(fromdayone, contact_location) %>%
             group_by(fromdayone, contact_location) %>% tally() %>%
  spread(contact_location, n) ,
           
           india_mix %>% filter(study_site == "Urban") %>% #drop_na(fromdayone, contact_location) %>% 
    group_by(fromdayone, contact_location) %>% tally() %>%
  spread(contact_location, n)
           )
      ) %>% kable_classic(full_width = F, html_font = "Cambria") %>%
  footnote(general = "The left and right tables are for the rural and urban networks, respectively.")

```
### Descriptive analysis of repeated/unique contacts in the school, work, and other non-home category
```{r, echo=F, warning=F, message=FALSE}
nonhome_dup_descib <- function(mix, network){
  
  output <- list()
  
#india_mix_nonhome <- # later, we may account for rural/urban status
output$overall_freq <- 
  mix %>% filter(study_site==network & contact_location %in% c( "Nonhome",  "School",    "Work" )) %>% group_by(fromdayone) %>% 
  summarize(n=n()
            ) %>% 
  mutate(prop = n/sum(n)) %>% # ~2/3 of the contacts in the nonhome category were duplicated 
  mutate_if(is.numeric, round, 3)


#india_mix_nonhome_bothdays <- # nonhome contacts spanning two days. 
location_labs <- as.character(get_label(mix))
location_labs <-as.character(location_labs)[which(location_labs=="My home"):which(location_labs=="Other")]

location_freq <- 
mix %>% filter(study_site==network & contact_location %in% c( "Nonhome",  "School",    "Work" ) & fromdayone == "Both days")%>%
  select(location_contact___0:location_contact___19) %>% `colnames<-`(location_labs)  %>% colSums() %>% sort(., decreasing =T) # most contacts occurred at school, street, and other's home 
 
output$location_freq <- 
location_freq[location_freq>100] 

output

}


nonhome_dup_rural <- 
nonhome_dup_descib(mix = india_mix, network = "Rural")


nonhome_dup_urban <- 
nonhome_dup_descib(mix = india_mix, network = "Urban")
```

The following figure shows the frequency of duplicated non-home contacts by contact location of the two-day study period. Contact locations with frequencies > 100 were shown.
```{r, echo=F, warning=F, message=FALSE, fig.width==10, fig.height=10}
par(mfrow = c(1, 2), mar=c(5, 4, 4, 2) + 0.5) 
barplot(nonhome_dup_rural$location_freq, main = "Rural", ylab = "Frequency", ylim = c(0, 1100),
        las = 2, 
        cex.names = 1)

barplot(nonhome_dup_urban$location_freq, main = "Urban", ylim = c(0,1100),
        las = 2, cex.names = 1)



```

```{r, echo=F, warning=F, message=FALSE}
# split data into urban and rural networks using study site, and get the number of participants with 0 contact in specified age groups

data_split <- function(india_mix., india_participant., india_contact., study_site., age.grp){
 out <-  list()
 out[[1]] <-
 india_mix. %>% filter(!is.na(contact_location) # complete-case analysis - exclude contacts didn't have a contact location from analysis
                      ) %>% 
  filter(study_site == study_site.) # here we split the dataset into urban or rural samples


out[[2]] <- # participants with 0 contacts by study site in India
  india_participant. %>%
  filter(!(id %in% india_contact.$id)) %>%
  filter(study_site == study_site.) %>% # here we split the dataset into urban or rural samples
  group_by(participant_age) %>%
  tally(name = "n_participants0")

names(out) <-  c(paste0("india_mix.", tolower(study_site.), age.grp), 
                 paste0("india.no.contacts.",  tolower(study_site.), age.grp)
                 )

out
} 

# india_mix.rural.10age.grps <- # rural mixing, original age groups
# data_split(india_mix. = india_mix %>% select(-participant_age_reclass, -contact_age_reclass), 
#            india_participant. = india_participant %>% select(-participant_age_reclass), 
#            india_contact. = india_contact %>% select( -contact_age_reclass),
#            study_site. ="Rural", age.grp = ".10age.grps") # 
# 
# india_mix.urban.10age.grps <- # urban mixing, original age groups
# data_split(india_mix. = india_mix %>% select(-participant_age_reclass, -contact_age_reclass), 
#            india_participant. = india_participant %>% select(-participant_age_reclass), 
#            india_contact. = india_contact %>% select( -contact_age_reclass),
#            study_site. ="Urban", age.grp = ".10age.grps") # .10age.grps


india_mix.rural.6age.grps <- # rural mixing, six age groups
data_split(india_mix. = india_mix %>% 
             select(-c(participant_age,contact_age)) %>% 
             rename(participant_age = participant_age_reclass,
                    contact_age = contact_age_reclass
                    ), 
           india_participant. = india_participant %>% 
             select(-participant_age) %>% 
             rename(participant_age = participant_age_reclass), 
           
           india_contact. = india_contact%>% 
             select(-contact_age) %>% 
             rename(contact_age = contact_age_reclass),
           study_site. ="Rural", age.grp = ".6age.grps") # .6age.grps


india_mix.urban.6age.grps <- # urban mixing, six age groups
data_split(india_mix. = india_mix %>% 
             select(-c(participant_age,contact_age)) %>% 
             rename(participant_age = participant_age_reclass,
                    contact_age = contact_age_reclass
                    ), 
           india_participant. = india_participant %>% 
             select(-participant_age) %>% 
             rename(participant_age = participant_age_reclass), 
           
           india_contact. = india_contact%>% 
             select(-contact_age) %>% 
             rename(contact_age = contact_age_reclass),
           study_site. ="Urban", age.grp = ".6age.grps") # .6age.grps


# function to compile data by participant's and contact's age groups and estimate mean degree (duplicated contacts/dyads at home were counted once)------
summariseContacts <- function(df,
                              filter.duration_contact, 
                              no.contacts
                          
) { 
  
 df %>%
  select(id,participant_age, fromdayone,contact_age,contact_location, duration_contact) %>% # summarizing degree by contact location
  group_by(participant_age) %>%
  mutate(n_participants = n_distinct(id)) %>%  # total number of participants by age group
  ungroup() %>%
  filter(!(duration_contact %in% filter.duration_contact)) %>% # filter out contact with duration ≤ 15 mins
  group_by(contact_location,participant_age,contact_age,n_participants, fromdayone, .drop = FALSE) %>%
  summarise(n_contacts = n()) %>%  # total number of contacts reported over the 2 study days, by contact_location, participant's age group, contact's age group, total number of participants in each age group
  mutate(n_contacts = case_when(contact_location == "Home" & fromdayone == "Both days" ~ n_contacts/2, # for repeated home contacts over two days, we count them once
                                TRUE ~ n_contacts)
         ) %>%
  filter(!is.na(fromdayone)) %>% # complete case analysis for fromdayone
  group_by(contact_location,participant_age,contact_age,n_participants, .drop = FALSE) %>%
  summarise(n_contacts = sum(n_contacts)) %>% # summ all the contacts in all categories of "fromdayone" together
  ungroup() %>%
  complete(contact_location,participant_age,contact_age) %>% # complete-case analysis
  group_by(contact_location,participant_age) %>%
  fill(n_participants,.direction = "downup") %>% # filling n_participants in groups with 0 contact
  mutate(degree = (n_contacts/n_participants)/2) %>%   # average mean degree for 1 day, the 2 here is to average 2-day degree
  mutate(total_degree = sum(degree)) %>%  # total degree by contact_location and participant age group
  mutate(prop_degree = degree/total_degree)  %>% # age distribution of contacts by contact_location and participant age
  ungroup() %>%  
  ## add participants with 0 contacts to update n_participants and degree-----------------------------
left_join(no.contacts ,by = c("participant_age")
) %>%
  mutate(n_participants = rowSums(.[c("n_participants", "n_participants0")], na.rm = TRUE)) %>%  # update n_participants; replacing script mutate(n_participants_test = n_participants + n_participants0) from CorporateMix, given NA in n_participants0 caused by fewer categories w/ zero contact
  select(-n_participants0) %>% 
  group_by(contact_location,participant_age)  %>%
  mutate(degree = (n_contacts/n_participants)/2) %>%   # average mean degree for 1 day
  mutate(total_degree = sum(degree)) %>%  # total degree by contact_location and participant age
  mutate(prop_degree = degree/total_degree) %>%   # age distribution of contacts by contact_location and participant age
  ungroup()

  
}

india_mix.sum.no15 <- list() # degree for each study site is outputted separately

# india_mix.sum.no15[[1]] <- 
#   summariseContacts(df = india_mix.rural.10age.grps$india_mix.rural.10age.grps %>% rename(predictor_contact = contact_location), 
#                     filter.duration_contact = c("<5 mins", "5-15 mins"),
#                     no.contacts = india_mix.rural.10age.grps$india.no.contacts.rural.10age.grps
#                     ) %>% rename( contact_location=predictor_contact )
# 
# india_mix.sum.no15[[2]] <- 
#   summariseContacts(df = india_mix.urban.10age.grps$india_mix.urban.10age.grps %>% rename(predictor_contact = contact_location), 
#                     filter.duration_contact = c("<5 mins", "5-15 mins"),
#                     no.contacts = india_mix.urban.10age.grps$india.no.contacts.urban.10age.grps
#                     ) %>% rename( contact_location=predictor_contact )

india_mix.sum.no15[[1]] <- 
  summariseContacts(df = india_mix.rural.6age.grps$india_mix.rural.6age.grps , 
                    filter.duration_contact = c("<5 mins", "5-15 mins"),
                    no.contacts = india_mix.rural.6age.grps$india.no.contacts.rural.6age.grps
                    ) %>% rename( contact_location=contact_location )

india_mix.sum.no15[[2]] <- 
  summariseContacts(df = india_mix.urban.6age.grps$india_mix.urban.6age.grps, 
                    filter.duration_contact = c("<5 mins", "5-15 mins"),
                    no.contacts = india_mix.urban.6age.grps$india.no.contacts.urban.6age.grps
                    ) %>% rename( contact_location=contact_location )



names(india_mix.sum.no15) <- c(#"india_mix.sum.no15.rural.10age.grps", "india_mix.sum.no15.urban.10age.grps",
                               "india_mix.sum.no15.rural.6age.grps", "india_mix.sum.no15.urban.6age.grps"
                               )
```

```{r, echo=F, warning=F, message=FALSE}

#saveRDS(india_mix.sum.no15, file = "./data/network_params/india_mix.sum.no15.RData")


# create symmetrical social mixing matrix by average degree and its proportion ----
avg.matrices.india <- list() # single-day symmetric matrices separately for urban and rural populations
avg.matrix.fun <- 
  function(mix.sum, age_grp_count){
    
    if (age_grp_count == 10){
    avg.mix <- mix.sum %>%   # average mean degree for 1 day
      select(-c("total_degree", "prop_degree")) %>% 
      mutate(mix = case_when(participant_age == "<6mo" & contact_age == "<6mo" ~ "0s-0s",
                             (participant_age == "<6mo" & contact_age == "6-11mo") |
                               (participant_age == "6-11mo" & contact_age == "<6mo") ~ "0s-0.49s",
                             (participant_age == "<6mo" & contact_age == "1-4y") |
                               (participant_age == "1-4y" & contact_age == "<6mo") ~ "0s-1s",
                             (participant_age == "<6mo" & contact_age == "5-9y") |
                               (participant_age == "5-9y" & contact_age == "<6mo") ~ "0s-5s",
                             (participant_age == "<6mo" & contact_age == "10-14y") |
                               (participant_age == "10-14y" & contact_age == "<6mo") ~ "0s-10s",
                             (participant_age == "<6mo" & contact_age == "15-19y") |
                               (participant_age == "15-19y" & contact_age == "<6mo") ~ "0s-14.9s",
                             (participant_age == "<6mo" & contact_age == "20-29y") |
                               (participant_age == "20-29y" & contact_age == "<6mo") ~ "0s-20s",
                             (participant_age == "<6mo" & contact_age == "30-39y") |
                               (participant_age == "30-39y" & contact_age == "<6mo") ~ "0s-30s",
                             (participant_age == "<6mo" & contact_age == "40-59y") |
                               (participant_age == "40-59y" & contact_age == "<6mo") ~ "0s-40s",
                             (participant_age == "<6mo" & contact_age == "60+y") |
                               (participant_age == "60+y" & contact_age == "<6mo") ~ "0s-60s",
                             
                             participant_age == "6-11mo" & contact_age == "6-11mo" ~ "0.49s-0.49s",
                             (participant_age == "6-11mo" & contact_age == "1-4y") |
                               (participant_age == "1-4y" & contact_age == "6-11mo") ~ "0.49s-1s",
                             (participant_age == "6-11mo" & contact_age == "5-9y") |
                               (participant_age == "5-9y" & contact_age == "6-11mo") ~ "0.49s-5s",
                             (participant_age == "6-11mo" & contact_age == "10-14y") |
                               (participant_age == "10-14y" & contact_age == "6-11mo") ~ "0.49s-10s",
                             (participant_age == "6-11mo" & contact_age == "15-19y") |
                               (participant_age == "15-19y" & contact_age == "6-11mo") ~ "0.49s-14.9s",
                             (participant_age == "6-11mo" & contact_age == "20-29y") |
                               (participant_age == "20-29y" & contact_age == "6-11mo") ~ "0.49s-20s",
                             (participant_age == "6-11mo" & contact_age == "30-39y") |
                               (participant_age == "30-39y" & contact_age == "6-11mo") ~ "0.49s-30s",
                             (participant_age == "6-11mo" & contact_age == "40-59y") |
                               (participant_age == "40-59y" & contact_age == "6-11mo") ~ "0.49s-40s",
                             (participant_age == "6-11mo" & contact_age == "60+y") |
                               (participant_age == "60+y" & contact_age == "6-11mo") ~ "0.49s-60s",
                             
                             participant_age == "1-4y" & contact_age == "1-4y" ~ "1s-1s",
                             (participant_age == "1-4y" & contact_age == "5-9y") |
                               (participant_age == "5-9y" & contact_age == "1-4y") ~ "1s-5s",
                             (participant_age == "1-4y" & contact_age == "10-14y") |
                               (participant_age == "10-14y" & contact_age == "1-4y") ~ "1s-10s",
                             (participant_age == "1-4y" & contact_age == "15-19y") |
                               (participant_age == "15-19y" & contact_age == "1-4y") ~ "1s-14.9s",
                             (participant_age == "1-4y" & contact_age == "20-29y") |
                               (participant_age == "20-29y" & contact_age == "1-4y") ~ "1s-20s",
                             (participant_age == "1-4y" & contact_age == "30-39y") |
                               (participant_age == "30-39y" & contact_age == "1-4y") ~ "1s-30s",
                             (participant_age == "1-4y" & contact_age == "40-59y") |
                               (participant_age == "40-59y" & contact_age == "1-4y") ~ "1s-40s",
                             (participant_age == "1-4y" & contact_age == "60+y") |
                               (participant_age == "60+y" & contact_age == "1-4y") ~ "1s-60s",
                             
                             participant_age == "5-9y" & contact_age == "5-9y" ~ "5s-5s",
                             (participant_age == "5-9y" & contact_age == "10-14y") |
                               (participant_age == "10-14y" & contact_age == "5-9y") ~ "5s-10s",
                             (participant_age == "5-9y" & contact_age == "15-19y") |
                               (participant_age == "15-19y" & contact_age == "5-9y") ~ "5s-14.9s",
                             (participant_age == "5-9y" & contact_age == "20-29y") |
                               (participant_age == "20-29y" & contact_age == "5-9y") ~ "5s-20s",
                             (participant_age == "5-9y" & contact_age == "30-39y") |
                               (participant_age == "30-39y" & contact_age == "5-9y") ~ "5s-30s",
                             (participant_age == "5-9y" & contact_age == "40-59y") |
                               (participant_age == "40-59y" & contact_age == "5-9y") ~ "5s-40s",
                             (participant_age == "5-9y" & contact_age == "60+y") |
                               (participant_age == "60+y" & contact_age == "5-9y") ~ "5s-60s",
                             
                             participant_age == "10-14y" & contact_age == "10-14y" ~ "10s-10s",
                             (participant_age == "10-14y" & contact_age == "15-19y") |
                               (participant_age == "15-19y" & contact_age == "10-14y") ~ "10s-14.9s",
                             (participant_age == "10-14y" & contact_age == "20-29y") |
                               (participant_age == "20-29y" & contact_age == "10-14y") ~ "10s-20s",
                             (participant_age == "10-14y" & contact_age == "30-39y") |
                               (participant_age == "30-39y" & contact_age == "10-14y") ~ "10s-30s",
                             (participant_age == "10-14y" & contact_age == "40-59y") |
                               (participant_age == "40-59y" & contact_age == "10-14y") ~ "10s-40s",
                             (participant_age == "10-14y" & contact_age == "60+y") |
                               (participant_age == "60+y" & contact_age == "10-14y") ~ "10s-60s",                         
                             
                             participant_age == "15-19y" & contact_age == "15-19y" ~ "14.9s-14.9s",
                             (participant_age == "15-19y" & contact_age == "20-29y") |
                               (participant_age == "20-29y" & contact_age == "15-19y") ~ "14.9s-20s",
                             (participant_age == "15-19y" & contact_age == "30-39y") |
                               (participant_age == "30-39y" & contact_age == "15-19y") ~ "14.9s-30s",
                             (participant_age == "15-19y" & contact_age == "40-59y") |
                               (participant_age == "40-59y" & contact_age == "15-19y") ~ "14.9s-40s",
                             (participant_age == "15-19y" & contact_age == "60+y") |
                               (participant_age == "60+y" & contact_age == "15-19y") ~ "14.9s-60s", 
                             
                             participant_age == "20-29y" & contact_age == "20-29y" ~ "20s-20s",
                             (participant_age == "20-29y" & contact_age == "30-39y") |
                               (participant_age == "30-39y" & contact_age == "20-29y") ~ "20s-30s",
                             (participant_age == "20-29y" & contact_age == "40-59y") |
                               (participant_age == "40-59y" & contact_age == "20-29y") ~ "20s-40s",
                             (participant_age == "20-29y" & contact_age == "60+y") |
                               (participant_age == "60+y" & contact_age == "20-29y") ~ "20s-60s",   
                             
                             participant_age == "30-39y" & contact_age == "30-39y" ~ "30s-30s",
                             (participant_age == "30-39y" & contact_age == "40-59y") |
                               (participant_age == "40-59y" & contact_age == "30-39y") ~ "30s-40s",
                             (participant_age == "30-39y" & contact_age == "60+y") |
                               (participant_age == "60+y" & contact_age == "30-39y") ~ "30s-60s", 
                             
                             participant_age == "40-59y" & contact_age == "40-59y" ~ "40s-40s",
                             (participant_age == "40-59y" & contact_age == "60+y") |
                               (participant_age == "60+y" & contact_age == "40-59y") ~ "40s-60s", 
                             
                             participant_age == "60+y" & contact_age == "60+y" ~ "60s-60s"
                             
                             
      )
      ) %>%
      ungroup() %>%
      group_by(contact_location,mix) %>%
      summarise(degree = mean(degree))
    
    avg.matrix <- avg.mix %>%
      separate(mix,c("age1","age2"), sep = "-") %>% # age 1 is for participant, age 2 is for contact
      mutate(age1 = factor(age1, levels = c("0s",  "0.49s",  "1s",  "5s", "10s", "14.9s", "20s", "30s", "40s", "60s" )
      ),
      age2 = factor(age2, levels = c("0s",  "0.49s",  "1s",  "5s", "10s", "14.9s", "20s", "30s", "40s", "60s" )
      )
      ) %>% 
      arrange(age1, age2) %>% 
      pivot_wider(names_from = "age1",values_from = "degree") # the matrix pivoted by "age2" is the same but the degrees are in the other side of the diagnoal
    
     #total degree of mixing by age group; On 20230731, we validated the below code with the total degree calculation based on mix.sum using the following script and confirm that the total_degree in avg.total is correct
      #mix.sum %>% filter(contact_location =="Nonhome" & ((contact_age == "1-4y"|participant_age == "1-4y") & !(contact_age == "1-4y"& participant_age == "1-4y"))) %>% select(degree)  %>% summarize(sum(degree)/2)+mix.sum %>% filter(contact_location =="Nonhome" & ( (contact_age == "1-4y"& participant_age == "1-4y"))) %>% select(degree) %>% as.numeric()
    avg.total <- avg.mix %>%
      ungroup() %>%
      mutate(
        age0s = ifelse((
          (grepl("0s-",mix)|grepl("-0s",mix)) & 
            !(grepl("10s-",mix)| grepl("20s-",mix)|grepl("30s-",mix)| # these age groups are considered as 0s by grepl so we excluded them 
                grepl("40s-",mix)|grepl("60s-",mix)) # these age groups are considered as 0s by grepl so we excluded them 
        ),
        degree,NA
        ),
        age0.49s = ifelse(grepl("0.49s",mix),degree,NA),
        age1s = ifelse(grepl("1s",mix),degree,NA),
        age5s = ifelse(grepl("5s",mix),degree,NA),
        age10s = ifelse(grepl("10s",mix),degree,NA),
        age14.9s = ifelse(grepl("14.9s",mix),degree,NA),
        age20s = ifelse(grepl("20s",mix),degree,NA),
        age30s = ifelse(grepl("30s",mix),degree,NA),
        age40s = ifelse(grepl("40s",mix),degree,NA),
        age60s = ifelse(grepl("60s",mix),degree,NA)
      ) %>%
      select(-mix,-degree) %>%
      group_by(contact_location) %>%
      summarise(age0s = sum(age0s, na.rm = T),
                age0.49s = sum(age0.49s, na.rm = T),
                age1s = sum(age1s, na.rm = T),
                age5s = sum(age5s, na.rm = T),
                age10s = sum(age10s, na.rm = T),
                age14.9s = sum(age14.9s, na.rm = T),
                age20s = sum(age20s, na.rm = T),
                age30s = sum(age30s, na.rm = T),
                age40s = sum(age40s, na.rm = T),
                age60s = sum(age60s, na.rm = T)
      ) %>%
      pivot_longer(cols = -contact_location,names_to = "age2", values_to = "total_degree") %>% # same result if pivoted by age1
      mutate(age2 = substr(age2,4,8)
      ) %>% 
      mutate(
        age2 = factor(age2, levels = c("0s",  "0.49s",  "1s",  "5s", "10s", "14.9s", "20s", "30s", "40s", "60s" )
        )
      )
    
    
    avg.matrix <- avg.matrix %>%
      left_join(avg.total, by = c("contact_location","age2")) %>%
      rename(age = age2) %>%
      mutate(prop_match = case_when(age == "0s" ~ `0s`/total_degree,
                                    age == "0.49s" ~ `0.49s`/total_degree,
                                    age == "1s" ~ `1s`/total_degree,
                                    age == "5s" ~ `5s`/total_degree,
                                    age == "10s" ~ `10s`/total_degree,
                                    age == "14.9s" ~ `14.9s`/total_degree,
                                    age == "20s" ~ `20s`/total_degree,
                                    age == "30s" ~ `30s`/total_degree,
                                    age == "40s" ~ `40s`/total_degree,
                                    age == "60s" ~ `60s`/total_degree
                                    
                                    
      )
      ) %>% 
      mutate(age = as.character(age)) %>% 
      mutate(age = recode(age, 
                          "0s"="<6mo", "0.49s"="6-11mo", "1s"= "1-4y", "5s"="5-9y",
                          "10s"="10-14y", "14.9s"="15-19y", "20s"= "20-29y", "30s"="30-39y",
                          "40s"="40-59y", "60s"="60+y"
      )
      ) %>% 
      mutate(age = factor(age, levels = c("<6mo","6-11mo","1-4y","5-9y", "10-14y","15-19y","20-29y", "30-39y", "40-59y", "60+y")
      )
      ) %>% 
      rename(`<6mo`=`0s`, `6-11mo`=`0.49s`, `1-4y`=`1s`, `5-9y`=`5s`,
             `10-14y`=`10s`, `15-19y`=`14.9s`,  `20-29y` = `20s`, `30-39y`=`30s`,
             `40-59y`=`40s`, `60+y`=`60s`
      )#matrix with mean degree in each cell
    
    # matrix with proportion
    avg.matrix.prop <- avg.matrix %>% mutate( 
      `<6mo` = `<6mo`/total_degree,
      `6-11mo` = `6-11mo`/total_degree,
      `1-4y` = `1-4y`/total_degree,
      `5-9y` = `5-9y`/total_degree,
      `10-14y` = `10-14y`/total_degree,
      `15-19y` = `15-19y`/total_degree,
      `20-29y` = `20-29y`/total_degree,
      `30-39y` = `30-39y`/total_degree,
      `40-59y` = `40-59y`/total_degree,
      `60+y` = `60+y`/total_degree)
    
    } 
    else if (age_grp_count == 6){
      
      avg.mix <- mix.sum %>%   # average mean degree for 1 day
        select(-c("total_degree", "prop_degree")) %>% 
        mutate(mix = case_when(
          
                               participant_age == "0-9y" & contact_age == "0-9y" ~ "0s-0s",
                               (participant_age == "0-9y" & contact_age == "10-19y") |
                                 (participant_age == "10-19y" & contact_age == "0-9y") ~ "0s-10s",
                               (participant_age == "0-9y" & contact_age == "20-29y") |
                                 (participant_age == "20-29y" & contact_age == "0-9y") ~ "0s-20s",
                               (participant_age == "0-9y" & contact_age == "30-39y") |
                                 (participant_age == "30-39y" & contact_age == "0-9y") ~ "0s-30s",
                               (participant_age == "0-9y" & contact_age == "40-59y") |
                                 (participant_age == "40-59y" & contact_age == "0-9y") ~ "0s-40s",
                               (participant_age == "0-9y" & contact_age == "60+y") |
                                 (participant_age == "60+y" & contact_age == "0-9y") ~ "0s-60s",
                               
                               participant_age == "10-19y" & contact_age == "10-19y" ~ "10s-10s",
                               (participant_age == "10-19y" & contact_age == "20-29y") |
                                 (participant_age == "20-29y" & contact_age == "10-19y") ~ "10s-20s",
                               (participant_age == "10-19y" & contact_age == "30-39y") |
                                 (participant_age == "30-39y" & contact_age == "10-19y") ~ "10s-30s",
                               (participant_age == "10-19y" & contact_age == "40-59y") |
                                 (participant_age == "40-59y" & contact_age == "10-19y") ~ "10s-40s",
                               (participant_age == "10-19y" & contact_age == "60+y") |
                                 (participant_age == "60+y" & contact_age == "10-19y") ~ "10s-60s",
                               
                               
                               participant_age == "20-29y" & contact_age == "20-29y" ~ "20s-20s",
                               (participant_age == "20-29y" & contact_age == "30-39y") |
                                 (participant_age == "30-39y" & contact_age == "20-29y") ~ "20s-30s",
                               (participant_age == "20-29y" & contact_age == "40-59y") |
                                 (participant_age == "40-59y" & contact_age == "20-29y") ~ "20s-40s",
                               (participant_age == "20-29y" & contact_age == "60+y") |
                                 (participant_age == "60+y" & contact_age == "20-29y") ~ "20s-60s",                         
                               
                               participant_age == "30-39y" & contact_age == "30-39y" ~ "30s-30s",
                               (participant_age == "30-39y" & contact_age == "40-59y") |
                                 (participant_age == "40-59y" & contact_age == "30-39y") ~ "30s-40s",
                               (participant_age == "30-39y" & contact_age == "60+y") |
                                 (participant_age == "60+y" & contact_age == "30-39y") ~ "30s-60s",     
                               
                               participant_age == "40-59y" & contact_age == "40-59y" ~ "40s-40s",
                               (participant_age == "40-59y" & contact_age == "60+y") |
                                 (participant_age == "60+y" & contact_age == "40-59y") ~ "40s-60s",     
                               
                               participant_age == "60+y" & contact_age == "60+y" ~ "60s-60s"
                               
            
                               
        )
        ) %>%
        ungroup() %>%
        group_by(contact_location,mix) %>%
        summarise(degree = mean(degree))
      
      avg.matrix <- avg.mix %>%
        separate(mix,c("age1","age2"), sep = "-") %>% # age 1 is for participant, age 2 is for contact
        mutate(age1 = factor(age1, levels = c("0s", "10s",  "20s", "30s", "40s", "60s" )
        ),
        age2 = factor(age2, levels = c("0s", "10s",  "20s", "30s", "40s", "60s" )
        )
        ) %>% 
        arrange(age1, age2) %>% 
        pivot_wider(names_from = "age1",values_from = "degree") # the matrix pivoted by "age2" is the same but the degrees are in the other side of the diagnoal
      
      
      avg.total <- avg.mix %>% #total degree of mixing by age group
        ungroup() %>%
        mutate(
          age0s = ifelse((
            (grepl("0s-",mix)|grepl("-0s",mix)) & 
              !(grepl("10s-",mix)| grepl("20s-",mix)|grepl("30s-",mix)| # these age groups are considered as 0s by grepl so we excluded them 
                  grepl("40s-",mix)|grepl("60s-",mix)) # these age groups are considered as 0s by grepl so we excluded them 
          ),
          degree,NA
          ),
          age10s = ifelse(grepl("10s",mix),degree,NA),
          age20s = ifelse(grepl("20s",mix),degree,NA),
          age30s = ifelse(grepl("30s",mix),degree,NA),
          age40s = ifelse(grepl("40s",mix),degree,NA),
          age60s = ifelse(grepl("60s",mix),degree,NA)
        ) %>%
        select(-mix,-degree) %>%
        group_by(contact_location) %>%
        summarise(age0s = sum(age0s, na.rm = T),
                  age10s = sum(age10s, na.rm = T),
                  age20s = sum(age20s, na.rm = T),
                  age30s = sum(age30s, na.rm = T),
                  age40s = sum(age40s, na.rm = T),
                  age60s = sum(age60s, na.rm = T)
        ) %>%
        pivot_longer(cols = -contact_location,names_to = "age2", values_to = "total_degree") %>% # same result if pivoted by age1
        mutate(age2 = substr(age2,4,8)
        ) %>% 
        mutate(
          age2 = factor(age2, levels = c("0s", "10s",  "20s", "30s", "40s", "60s")
          )
        ) # In Aug 2023, this script was validated by calculation using the symmetrical mixing matrix - total degree of group i =avg.matrix[,i]+avg.matrix[i,]-avg.matrix[i,i]. The script is fine based on the validation.
      
      
      avg.matrix <- avg.matrix %>%
        left_join(avg.total, by = c("contact_location","age2")) %>%
        rename(age = age2) %>%
        mutate(prop_match = case_when(age == "0s" ~ `0s`/total_degree,
                                      age == "10s" ~ `10s`/total_degree,
                                      age == "20s" ~ `20s`/total_degree,
                                      age == "30s" ~ `30s`/total_degree,
                                      age == "40s" ~ `40s`/total_degree,
                                      age == "60s" ~ `60s`/total_degree
                                      
                                      
        )
        ) %>% 
        mutate(age = as.character(age)) %>% 
        mutate(age = recode(age, 
                            "0s"="0-9y", 
                            "10s"="10-19y", "20s"= "20-29y", "30s"="30-39y",
                            "40s"="40-59y", "60s"="60+y"
        )
        ) %>% 
        mutate(age = factor(age, levels = c("0-9y", "10-19y","20-29y", "30-39y", "40-59y", "60+y")
        )
        ) %>% 
        rename(`0-9y`=`0s`, `10-19y`=`10s`, `20-29y` = `20s`, `30-39y`=`30s`,
               `40-59y`=`40s`, `60+y`=`60s`
        )#matrix with mean degree in each cell
      
      # matrix with proportion
      avg.matrix.prop <- avg.matrix %>% mutate( 
        
        `0-9y` = `0-9y`/total_degree,
        `10-19y` = `10-19y`/total_degree,
        `20-29y` = `20-29y`/total_degree,
        `30-39y` = `30-39y`/total_degree,
        `40-59y` = `40-59y`/total_degree,
        `60+y` = `60+y`/total_degree)
    
        
    }
    
    avg.matrix.list <- list()
    avg.matrix.list[[1]] <- avg.matrix %>% ungroup()
    avg.matrix.list[[2]] <- avg.matrix.prop %>% ungroup()
    names(avg.matrix.list) <- c("avg.matrix", "avg.matrix.prop")
    
    avg.matrix.list
  }

# # Rural symmetric mixing matrices, 10 age groups
# avg.matrices.india$avg.matrix.india.rural.10age.grps <- 
# avg.matrix.fun(mix.sum = india_mix.sum.no15$india_mix.sum.no15.rural.10age.grps  %>% rename(predictor_contact = contact_location),
#            age_grp_count =10
#            )
# 
# # Urban symmetric mixing matrices, 10 age groups
# avg.matrices.india$avg.matrix.india.urban.10age.grps <- 
# avg.matrix.fun(mix.sum = india_mix.sum.no15$india_mix.sum.no15.urban.10age.grps  %>% rename(predictor_contact = contact_location),
#            age_grp_count = 10
#            )


# Rural symmetric mixing matrices, 6 age groups
avg.matrices.india$avg.matrix.india.rural.6age.grps <- 
avg.matrix.fun(mix.sum = india_mix.sum.no15$india_mix.sum.no15.rural.6age.grps  ,
           age_grp_count = 6
           )

# Urban symmetric mixing matrices, 6 age groups
avg.matrices.india$avg.matrix.india.urban.6age.grps <- 
avg.matrix.fun(mix.sum = india_mix.sum.no15$india_mix.sum.no15.urban.6age.grps ,
           age_grp_count = 6
           )


#saveRDS(avg.matrices.india, file = "./data/network_params/avg.matrices.india.RData")



```

## Total degree by contact location 
```{r pressure, echo=F, fig.width=6, fig.height=6}
rbind(
avg.matrices.india$avg.matrix.india.rural.6age.grps$avg.matrix %>% group_by(contact_location) %>% 
    summarise(tot_mean_degree = mean(total_degree)) %>% mutate(network="Rural"),

avg.matrices.india$avg.matrix.india.urban.6age.grps$avg.matrix %>% group_by(contact_location) %>% 
    summarise(tot_mean_degree = mean(total_degree)) %>% mutate(network="Urban")
) %>% 
  ggplot(mapping = 
    aes(x=contact_location, y=tot_mean_degree)
  ) + 
 geom_col(aes(fill=network), position = position_dodge()
          )+
  theme_classic()+
  xlab("Contact location")+ylab("Mean degree")+
    geom_text(aes(label = format(round(tot_mean_degree,1), nsmall=1, fontface= "bold"#, size=6
                   ), group = network), 
            colour = "black" ,  vjust = -0.1, position = position_dodge(0.8)
            )+
  theme(legend.position = "top")+
   guides(fill=guide_legend(title=""))
  
  
```

## Total degree by age group 
Previously, the raw total degree (by participants' age group) was plotted. Since the total degree for each age group will be instead used for analysis, we plot the latter moving forward. Note that repeated contacts in the home category were de-duplicated.

```{r pressure, echo=F, fig.width=12, fig.height=12}
# add back to text after revision - The total degree peaked in the age group of 10-14 years old and gradually became lower in the adjacent age groups. For participants < 1 year old in the rural population, the total degree of 6-11 months old #was lower than those < 6 months old.
#The participant's total degree tended to be higher at home than non-home locations among those that were not teenagers (10-19y). 


max_total_deg <- ceiling(max( avg.matrices.india$avg.matrix.india.rural.6age.grps$avg.matrix$total_degree, avg.matrices.india$avg.matrix.india.urban.6age.grps$avg.matrix$total_degree))
  

total_degree_plot <- # this replaced the function plotting the raw total degree
function(total_degree, network_name, max_total_degree){
  total_degree %>% 
  #select(contact_location,participant_age,total_degree) %>%
  #distinct() %>% 
  ggplot( mapping = aes(x = age,y = total_degree)
        )+ 
  geom_col(aes(fill = contact_location) , position = position_dodge()
           )+
  theme_classic()+
  geom_text(aes(label = format(round(total_degree,2), nsmall=2, fontface= "bold", size=6
                   ), group = contact_location), 
            colour = "black" ,  vjust = -0.2,position = position_dodge(0.8)
            )+
  labs(x = "", y = "", color = "contact_location")+theme(legend.position = "top")+
  guides(fill=guide_legend(title=""))+
  ggtitle(network_name) +
  theme(plot.title = element_text(hjust = 0.5),
        text = element_text(size=15)
        )+ scale_y_continuous(limits = c(0, max_total_degree))
  
}


annotate_figure(
  
ggarrange(
# Total degree by participant age group and network layer
# total_degree_plot(total_degree = avg.matrices.india$avg.matrix.india.rural.10age.grps$avg.matrix %>% rename(contact_location = predictor_contact), 
#                   network_name = "Rural", max_total_degree=max_total_deg)+
#   theme(axis.text.x=element_blank()),
total_degree_plot(total_degree = avg.matrices.india$avg.matrix.india.rural.6age.grps$avg.matrix , 
                  network_name = "Rural", max_total_degree=max_total_deg-0.5),
# total_degree_plot(total_degree = avg.matrices.india$avg.matrix.india.urban.10age.grps$avg.matrix %>% rename(contact_location = predictor_contact), 
#                   network_name = "Urban", max_total_degree=max_total_deg),
total_degree_plot(total_degree = avg.matrices.india$avg.matrix.india.urban.6age.grps$avg.matrix , 
                  network_name = "Urban", max_total_degree=max_total_deg-0.5),
ncol = 1, nrow = 2,
labels = c("A", "B"),
align = "h",
legend = "top",
common.legend = T
),

left = "Mean degree",
bottom = "Age"
)

```

## Symmetrical mixing matrices, by degree
The high level of assortaive mixing in the age group of 10-19 years old in the original non-home layers is explained by mixing at school.
For school mixing, the oldest age group(s) were not involved. For the mixing at work, the youngest age group(s) were not involved.

### Mixing by layers in the rural and urban networks
```{r, echo=F, warning=F, message=FALSE, error =F, fig.width=10, fig.height=6}

max.degree. <- # max degree across all setting to define the upper bound of color legend
ceiling(
  max(
max(avg.matrices.india$avg.matrix.india.rural.6age.grps$avg.matrix  %>% select(`0-9y`:`60+y`), na.rm = T),
max(avg.matrices.india$avg.matrix.india.urban.6age.grps$avg.matrix %>% select(`0-9y`:`60+y`), na.rm = T)
))


# function to visualize symmetric mixing matrix
symmetric_contactmatrix_viz <- function(matrix_wide, network_layer, max.degree, panel_title, metric){
  
  matrix_long <- 
  matrix_wide  %>% ungroup() %>% filter(contact_location == network_layer) %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `0-9y`:`60+y`, names_to = "vertical_age_grp", values_to = "degree")%>% 
    mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_mix$contact_age_reclass)
    )
    )
  
  ggplot(data = matrix_long, aes(x=vertical_age_grp, y=age, fill=degree)) +  
    geom_raster(hjust = 0.5, vjust = 0.5, show.legend=T) +
    scale_colour_discrete(na.translate = F) + 
    geom_text(aes(label = round(degree, 1),
                  fontface= "bold"
    ), size= 3
    )+
    
    # for degree
    {if (metric == "degree") {
      scale_fill_gradient2(low="#0571b0", mid="#92c5de", high="#ca0020" , limit = c(0, max.degree), 
                           breaks = 0 :max.degree.
                           #breaks = c(0,0.5, 1:max.degree.)
      )
    } else {
      # for proportion
      scale_fill_gradient2(low="#0571b0", mid="#92c5de", high="#ca0020" , limit = c(0, 1), 
                           breaks = c(0,0.2,0.4,0.6,0.8,1)
                           #breaks = c(0,0.5, 1:max.degree.)
      )
    }
    }+
    
    theme_classic() +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 7),
          legend.justification = "right",
          legend.position = "right") +
    theme(plot.title = element_text(size = 10), 
          axis.title.x = element_text(size=10, face="bold", angle=0),
          axis.title.y = element_text(size=10, face="bold"),
          axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size= 10))+
    xlab("")+ylab("")+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+ 
    labs(fill="Degree")+ggtitle(panel_title)
}


 


```

#### Rural networks
```{r, echo=F, warning=F, message=FALSE, error =F, fig.width=12, fig.height=9}
# Add back to text after revision - The mixing matrices in the home and nonhome settings in the urban network are generally similar to those in the rural network.



annotate_figure(
  
ggarrange(
  
symmetric_contactmatrix_viz(matrix_wide = avg.matrices.india$avg.matrix.india.rural.6age.grps$avg.matrix, network_layer = "Home", max.degree = max.degree., 
                            panel_title = "Home, Rural", metric = "degree")+
  theme(axis.text.x=element_blank()),

symmetric_contactmatrix_viz(matrix_wide = avg.matrices.india$avg.matrix.india.rural.6age.grps$avg.matrix, network_layer = "Nonhome", max.degree = max.degree., 
                            panel_title = "Nonhome, Rural", metric = "degree")+
  theme(axis.text.y=element_blank())+theme(axis.text.x=element_blank()),

symmetric_contactmatrix_viz(matrix_wide = avg.matrices.india$avg.matrix.india.rural.6age.grps$avg.matrix, network_layer = "School", max.degree = max.degree., 
                            panel_title = "School, Rural", metric = "degree"),

symmetric_contactmatrix_viz(matrix_wide = avg.matrices.india$avg.matrix.india.rural.6age.grps$avg.matrix, network_layer = "Work", max.degree = max.degree., 
                            panel_title = "Work, Rural", metric = "degree")+
  theme(axis.text.y=element_blank()),


ncol = 2, nrow = 2,
labels = c("A", "B", "C", "D"),
align = "h",
legend = "top",
common.legend = T
),

left = "Age",
bottom = "Age"
)

```

#### Urban networks
```{r, echo=F, warning=F, message=FALSE, error =F, fig.width=12, fig.height=9}

annotate_figure(
  
ggarrange(
  
symmetric_contactmatrix_viz(matrix_wide = $avg.matrix.india.urban.6age.grps$avg.matrix, network_layer = "Home", max.degree = max.degree., 
                            panel_title = "Home, Urban", metric = "degree")+
  theme(axis.text.x=element_blank()),

symmetric_contactmatrix_viz(matrix_wide = avg.matrices.india$avg.matrix.india.urban.6age.grps$avg.matrix, network_layer = "Nonhome", max.degree = max.degree., 
                            panel_title = "Nonhome, Urban", metric = "degree")+
  theme(axis.text.y=element_blank())+theme(axis.text.x=element_blank()),

symmetric_contactmatrix_viz(matrix_wide = avg.matrices.india$avg.matrix.india.urban.6age.grps$avg.matrix, network_layer = "School", max.degree = max.degree., 
                            panel_title = "School, Urban", metric = "degree"),

symmetric_contactmatrix_viz(matrix_wide = avg.matrices.india$avg.matrix.india.urban.6age.grps$avg.matrix, network_layer = "Work", max.degree = max.degree., 
                            panel_title = "Work, Urban", metric = "degree")+
  theme(axis.text.y=element_blank()),


ncol = 2, nrow = 2,
labels = c("A", "B", "C", "D"),
align = "h",
legend = "top",
common.legend = T
),

left = "Age",
bottom = "Age"
)



```

## Symmetrical mixing matrices, by proportion
The proportions below are calculated by dividing the mean degree ($MD_{ij}$) in each cell ($i,j$) by the total degree of each age group ($j$) it belonged to. The total degree of each age group is summarized above. In a symmetrical mixing matrix ($sym.matrix$), the total degree of age group $j = sym.matrix[,j]+sym.matrix[j,]-sym.matrix[j,j]$. So the proportion of $MD_{ij}$, denoted as $MD.prop_{ij}$, can be expressed as the following. Given $sym.matrix[j,]$ was included in the denominator, the row-wise sum of the proportion is less than one.

$$
MD.prop_{ij}=\frac{sym.matrix[i,j]}{sym.matrix[,j]+sym.matrix[j,]-sym.matrix[j,j]}
$$


### Mixing by layers in the rural network
```{r, echo=F, warning=F, message=FALSE, error =F, fig.width=10, fig.height=6}

annotate_figure(
  
ggarrange(
  
symmetric_contactmatrix_viz(matrix_wide = avg.matrices.india$avg.matrix.india.rural.6age.grps$avg.matrix.prop, network_layer = "Home", max.degree = 1, 
                            panel_title = "Home, Rural", metric = "prop")+
  theme(axis.text.x=element_blank()),

symmetric_contactmatrix_viz(matrix_wide = avg.matrices.india$avg.matrix.india.rural.6age.grps$avg.matrix.prop, network_layer = "Nonhome", max.degree = 1, 
                            panel_title = "Nonhome, Rural", metric = "prop")+
  theme(axis.text.y=element_blank())+theme(axis.text.x=element_blank()),

symmetric_contactmatrix_viz(matrix_wide = avg.matrices.india$avg.matrix.india.rural.6age.grps$avg.matrix.prop, network_layer = "School", max.degree = 1, 
                            panel_title = "School, Rural", metric = "prop"),

symmetric_contactmatrix_viz(matrix_wide = avg.matrices.india$avg.matrix.india.rural.6age.grps$avg.matrix.prop, network_layer = "Work", max.degree = 1, 
                            panel_title = "Work, Rural", metric = "prop")+
  theme(axis.text.y=element_blank()),


ncol = 2, nrow = 2,
labels = c("A", "B", "C", "D"),
align = "h",
legend = "top",
common.legend = T
),

left = "Age",
bottom = "Age"
)

```

### Mixing by layers in the urban network
The mixing matrices in the home and nonhome settings in the urban network are generally similar to those in the rural network.
```{r, echo=F, warning=F, message=FALSE, error =F, fig.width=10, fig.height=6}
annotate_figure(
  
ggarrange(
  
symmetric_contactmatrix_viz(matrix_wide = avg.matrices.india$avg.matrix.india.urban.6age.grps$avg.matrix.prop, network_layer = "Home", max.degree = 1, 
                            panel_title = "Home, Urban", metric = "prop")+
  theme(axis.text.x=element_blank()),

symmetric_contactmatrix_viz(matrix_wide = avg.matrices.india$avg.matrix.india.urban.6age.grps$avg.matrix.prop, network_layer = "Nonhome", max.degree = 1, 
                            panel_title = "Nonhome, Urban", metric = "prop")+
  theme(axis.text.y=element_blank())+theme(axis.text.x=element_blank()),

symmetric_contactmatrix_viz(matrix_wide = avg.matrices.india$avg.matrix.india.urban.6age.grps$avg.matrix.prop, network_layer = "School", max.degree = 1, 
                            panel_title = "School, Urban", metric = "prop"),

symmetric_contactmatrix_viz(matrix_wide = avg.matrices.india$avg.matrix.india.urban.6age.grps$avg.matrix.prop, network_layer = "Work", max.degree = 1, 
                            panel_title = "Work, Urban", metric = "prop")+
  theme(axis.text.y=element_blank()),


ncol = 2, nrow = 2,
labels = c("A", "B", "C", "D"),
align = "h",
legend = "top",
common.legend = T
),

left = "Age",
bottom = "Age"
)


```

## Uncertainties of network statistics
The following characterization of network statistics is adapted from ARTnet. We summarize the number of contact at the individual level, which is regressed on categories of terms (edge, nodefactor, nodematch) of the formation model using Poisson regression.
```{r, echo=F, warning=F, message=FALSE, error =F}
ci <- 
function(df, filter.duration_contact){

  out <- list()
  
# Pending: participants w/ 0 contacts is to be adjusted
# use GLM method to estimate network statistics
library(broom)
# india_mix %>% 
#   filter(study_site == "Rural") %>% 
#   group_by(id) %>%
#   summarize(n = n()) %>% ungroup() %>% 
#   do(tidy( glm(n ~ 1, data = ., family = poisson())))

# edge
## glm mestimate
  out[[1]] <- df %>%
  filter(!(duration_contact %in% filter.duration_contact)) %>% # filter out contact with duratioin ≤ 15 mins
  #filter(study_site == "Rural") %>% 
  group_by(id,  contact_location, fromdayone) %>%
  summarize(n = n()) %>% ungroup() %>% 
  mutate(n = case_when(contact_location == "Home" & fromdayone == "Both days" ~ n/2, # for repeated home contacts over two days, we count them once
                                TRUE ~ n)
  ) %>% 
  group_by(id,  contact_location) %>% 
  summarize(n = sum(n)) %>% ungroup() %>% 
  mutate(n= round(n)) %>% # round non-integer to integer for poisson regression
  group_by( contact_location) %>% 
  do(tidy( glm(n ~ 1, data = ., family = poisson())
  )
  ) %>% 
  mutate(lo= estimate-1.96*std.error, up=estimate+1.96*std.error) %>% 
  mutate(md = exp(estimate), md_lo = exp(lo), md_up = exp(up)
  ) 

# nodefactor
## glm mestimate
  out[[2]] <-df %>%
  filter(!(duration_contact %in% filter.duration_contact)) %>% # filter out contact with duratioin ≤ 15 mins
  group_by(id,  contact_location, participant_age, fromdayone) %>%
  summarize(n = n()) %>% ungroup() %>% 
  mutate(n = case_when(contact_location == "Home" & fromdayone == "Both days" ~ n/2, # for repeated home contacts over two days, we count them once
                       TRUE ~ n)
  ) %>% 
  group_by( id, contact_location, participant_age) %>% # covariate should be the age group of the egocentric population (participant)
  summarize(n = sum(n)) %>% ungroup() %>% 
  mutate(n= round(n)) %>% # round non-integer to integer for poisson regression
     group_by(contact_location) %>% 
  do(tidy( glm(n ~ -1+ participant_age, data = ., family = poisson())
  )
  ) %>% 
  mutate(lo= estimate-1.96*std.error, up=estimate+1.96*std.error) %>% 
  mutate(md = exp(estimate), md_lo = exp(lo), md_up = exp(up)
  ) %>% 
  mutate(term = str_remove(term, "participant_age")
  ) %>% 
  rename(participant_age=term) 

# nodematch

# Proportion of partnerships in same age group
df$same.age.grp <- ifelse(df$participant_age == df$contact_age, 1, 0)

# Model
out[[3]] <-df %>% 
  filter(!(duration_contact %in% filter.duration_contact)) %>% # filter out contact with duration ≤ 15 mins
  group_by(id,  contact_location, participant_age, fromdayone) %>%
  summarize(n = sum(same.age.grp )
            ) %>% ungroup() %>% 
  mutate(n = case_when(contact_location == "Home" & fromdayone == "Both days" ~ n/2, # for repeated home contacts over two days, we count them once
                       TRUE ~ n)
  ) %>% 
  group_by(id, contact_location, participant_age) %>% 
  summarize(n = sum(n )
  ) %>% ungroup() %>% 
  group_by(contact_location) %>% 
  mutate(n= round(n)) %>% # round non-integer to integer for poisson regression
  do(tidy( glm(n ~ -1+ participant_age, data = ., family = poisson())
  )
  )%>% 
  mutate(lo= estimate-1.96*std.error, up=estimate+1.96*std.error) %>% 
  mutate(md.match = exp(estimate), md_lo = exp(lo), md_up = exp(up)
  ) %>% 
  mutate(term = str_remove(term, "participant_age")
         ) %>% 
  rename(participant_age=term) 

names(out) <- c("edges", "nodefactor", "nodematch")

out

}

ci_rural <- 
ci(df=india_mix.rural.6age.grps$india_mix.rural.6age.grps, filter.duration_contact = c("<5 mins", "5-15 mins"))

ci_urban <- 
ci(df=india_mix.urban.6age.grps$india_mix.urban.6age.grps, filter.duration_contact = c("<5 mins", "5-15 mins"))




```

### Total edges in each network layer
```{r,echo=F, warning=F, message=FALSE, error =F}
rbind(
ci_rural$edges %>% mutate(network="rural"),
ci_urban$edges %>% mutate(network="urban")
) %>% 
  as.data.frame() %>% 
  ggplot( aes(x=contact_location, y=md, fill=network#, color=contact_location
              )
          ) + 
   geom_bar( stat = "identity", position = position_dodge()
  )+
  geom_errorbar(aes(x=contact_location, ymin=md_lo, ymax=md_up), width=.2,
                 position = position_dodge(width=0.9)
                )+
  #facet_wrap(vars(network))+
  theme_classic()+
  xlab("Contact location")+ylab("Number of contact (95% CI)")
  
```

### Number of edges in each age group
```{r,echo=F, warning=F, message=FALSE, error =F, fig.width=11, fig.height=6}
rbind(
ci_rural$nodefactor %>% select(participant_age, contact_location,  md, md_lo, md_up)%>% mutate(network="rural"),
ci_urban$nodefactor %>% select(participant_age, contact_location, md, md_lo, md_up)%>% mutate(network="urban")
) %>% 
  as.data.frame() %>% 
  ggplot( aes(x=participant_age, y=md, color=contact_location
              )
          ) + 
  geom_point(position = position_dodge(0.5))+
  geom_errorbar(aes(ymin=md_lo, ymax=md_up), width=.2,
                position = position_dodge(0.5),
                )+facet_wrap(vars(network))+theme_classic()+
    labs(col="")+
  xlab("Age group")+ylab("Number of contact (95% CI)")
```

### Number of matched ties of each age group
```{r,echo=F, warning=F, message=FALSE, error =F, fig.width=11, fig.height=6}
rbind(
ci_rural$nodematch %>% select(participant_age, contact_location,  md.match, md_lo, md_up)%>% mutate(network="rural"),
ci_urban$nodematch %>% select(participant_age, contact_location, md.match, md_lo, md_up)%>% mutate(network="urban")
) %>% 
  as.data.frame() %>% 
  filter(!md.match<0.01) %>% 
  ggplot( aes(x=participant_age, y=md.match, color=contact_location
              )
          ) + 
  geom_point(position = position_dodge(0.5))+
  geom_errorbar(aes(ymin=md_lo, ymax=md_up), width=.2,
                position = position_dodge(0.5),
                )+facet_wrap(vars(network))+theme_classic()+
    labs(col="")+
  xlab("Age group")+ylab("Number of matched contact (95% CI)")
```


