---
title: "Descriptive Degree Summary of GlobalMix India Data"
author: "Billy Dehao Chen"
date: "7/17/2023"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

# Background
This is a descriptive summary of contact degree of the India GlobalMix diary data.

# Method
We adapted the code Maria developed for the CorporateMix data to the GlobalMix data to calculate degree information. The degree information was summarized into four separate networks for two different epidemic models (one rural, one urban). We consider the mixing occurs within locations (urban, rural) and across two network layers (home, nonhome). We do not model contacts across layers, as we assume they are mutually exclusive across environments.


We excluded contacts lasted ≤ 15 mins in analysis. The degree information was summarized as the average degree of the two-day visits. Given the data were egocentric, we use $M.D.=\frac{edges}{n}$ for the relationship between mean degree ($M.D.$) and the number of edges.


```{r, echo=F, warning=F, message=FALSE}
library(ggpubr)
library(statnet)
library(EpiModel)
library(tidyverse)
library(socialmixr)
library(knitr)

# Load libraries and data  ------------------------------------------------


## participant data
india_participant <- 
  readRDS("../data/participant_contact/india_participant_data_aim1.RDS")%>% rename(id = rec_id)



## contact data 
india_contact <- 
  readRDS("../data/participant_contact/india_contact_data_aim1.RDS") %>% rename(id = rec_id)

# Note - validated study_site of participant is exactly the same as contact


# merge participants and contact datasets  ------------------------------------------------
india_mix <- india_participant %>%
  dplyr::select(id,participant_age) %>%
  right_join(india_contact,by = "id") %>% 
  mutate(contact_location2 = case_when(location_contact___0 == 1 | location_contact___1 == 1 ~ "Home", # 0 - "My home", 1 - "Other home"
                                       
                                       location_contact___2 == 1 | location_contact___3 == 1 | location_contact___4 == 1 | # "School", "Work", "Transport/Hub"
                                       location_contact___5 == 1 | location_contact___6 == 1 | # "Market/Shop", "Street"
                                       location_contact___7 == 1 | location_contact___8 == 1 | # "Playground", "Well"
                                       location_contact___9 == 1 | location_contact___10 == 1 | # "Agricultural Field", "Market/Shop"
                                       location_contact___11 == 1 | location_contact___12 == 1 | # "Restaurant", "Religious centre"
                                       location_contact___13 == 1 | location_contact___14 == 1 | # "Govt offices", "Health center"
                                       location_contact___15 == 1 | location_contact___16 == 1 | # "Bank", "Movie theatre"
                                       location_contact___17 == 1 | location_contact___18 == 1 | location_contact___19 == 1 #"Exhibition", "Social hall", "Other"
                                       ~ "Nonhome")
         ) 

tb_contact_location <-  
  table(india_mix$contact_location2, useNA = c("always")
             ) 
```
## Characterization of home-nonhome status
The home-nonhome status is processed from multiple questions asking contact location; given these questions are not mutually exclusive due to the check-box design in REDCap, a contact is characterized as at home when any contact with a participant reportedly occurred at the contact's home or other's home, regardless of the responses for other contact locations. For contacts did not occurred at home, they were characterized as occurring in a nonhome location if any of the nonhome locations were checked. For a contact checked neither home nor nonhome location, we assigned an NA to this contact. Below is a breakdown of the frequency of contact, in which there was `r paste0(as.numeric(round(tb_contact_location[3]/nrow(india_mix)*100)), "%")` of contact did not check any of the contact locations. We excluded these contacts in analysis.
```{r, echo=F, warning=F, message=FALSE}
kable(tb_contact_location, col.names = c("Contact location", "Freq."))
```

## Contact frequency of each network
We cross tabulated study location with network layer, and chi-square test suggests the two are not independent (P value <0.05). This supports the necessity of accounting each cell in the below table as a separate network.
```{r, echo=F, warning=F, message=FALSE}
kable(table(india_mix$contact_location2, india_mix$study_site))
#chisq.test(table(india_mix$contact_location2, india_mix$study_site))
```

```{r, echo=F, warning=F, message=FALSE}
## split data into urban and rural locations using study site

data_split <- function(india_mix., india_participant., india_contact., study_site.){
 out <-  list()
 out[[1]] <-
 india_mix. %>% filter(!is.na(contact_location2) # exclude contacts didn't have a contact location from analysis
                      ) %>% 
  mutate(contact_location2 = factor(contact_location2,
                                    levels = c("Home","Nonhome"),
                                    ordered = TRUE)
         ) %>% 
  mutate(duration_contact = case_when(duration_contact == ">4 hrs" ~ "4+ hrs",
                                      .default = duration_contact),
         duration_contact = factor(duration_contact,
                                    levels = c("<5 mins", "5-15 mins", "16-30 mins",  
                                               "31 mins-1 hr", "1-4 hrs", "4+ hrs", "Unknown"),
                                    ordered = TRUE)
         ) %>% rename(contact_duration = duration_contact) %>% 
  filter(study_site == study_site.) # here we split the dataset into urban or rural samples

# participants with 0 contacts by study site in India
out[[2]] <-
  india_participant. %>%
  filter(!(id %in% india_contact.$id)) %>%
  filter(study_site == study_site.) %>% # here we split the dataset into urban or rural samples
  group_by(participant_age) %>%
  tally(name = "n_participants0")

names(out) <-  c(paste0("india_mix.", tolower(study_site.)), paste0("india.no.contacts.",  tolower(study_site.)))

out
} 

india_mix.rural <- # rural mixing
data_split(india_mix. = india_mix, 
           india_participant. = india_participant, 
           india_contact. = india_contact,
           study_site. ="Rural")

india_mix.urban <- # urban mixing
data_split(india_mix. = india_mix, 
           india_participant. = india_participant, 
           india_contact. = india_contact,
           study_site. ="Urban")



## function to collapse data and estimate mean degree------
summariseContacts <- function(df,
                              filter.contact_duration, 
                              no.contacts
) { # adapt function to India data
  
  df %>%
    select(id,participant_age,contact_age,predictor_contact, contact_duration) %>% # summarizing degree by contact location
    rename(p_age = participant_age) %>%
    group_by(p_age) %>%
    mutate(n_participants = n_distinct(id)) %>%  # total number of participants by age group
    ungroup() %>%
    filter(!(contact_duration %in% filter.contact_duration)) %>% # filter out contact with duratioin ≤ 15 mins
    group_by(predictor_contact,p_age,contact_age,n_participants,.drop = FALSE) %>%
    summarise(n_contacts = n()) %>%  # total number of contacts reported over the 2 study days, by predictor_contact, participant's age group, contact's age group, total number of participants in each age group
    ungroup() %>%
    complete(predictor_contact,p_age,contact_age) %>%
    group_by(predictor_contact,p_age) %>%
    fill(n_participants,.direction = "downup") %>%
    mutate(degree = (n_contacts/n_participants)/2) %>%   # average mean degree for 1 day
    mutate(total_degree = sum(degree)) %>%  # total degree by predictor_contact and participant age group
    mutate(prop_degree = degree/total_degree)  %>% # age distribution of contacts by predictor_contact and participant age
    ungroup() %>%  
    ## add participants with 0 contacts to update n_participants and degree-----------------------------
  left_join(no.contacts %>% rename("p_age" = "participant_age"),by = c("p_age")
  ) %>%
    mutate(n_participants = rowSums(.[c("n_participants", "n_participants0")], na.rm = TRUE)) %>%  # replacing script mutate(n_participants_test = n_participants + n_participants0) from CorporateMix, given NA in n_participants0 caused by fewer categories w/ zero contact
    select(-n_participants0) %>% 
    group_by(predictor_contact,p_age)  %>%
    mutate(degree = (n_contacts/n_participants)/2) %>%   # average mean degree for 1 day
    mutate(total_degree = sum(degree)) %>%  # total degree by predictor_contact and participant age
    mutate(prop_degree = degree/total_degree) %>%   # age distribution of contacts by predictor_contact and participant age
    ungroup()
  
}

india_mix.sum.no15 <- list() # degree for each study site is outputted separately

india_mix.sum.no15[[1]] <- 
  summariseContacts(df = india_mix.rural$india_mix.rural %>% rename(predictor_contact = contact_location2), 
                    filter.contact_duration = c("<5 mins", "5-15 mins"),
                    no.contacts = india_mix.rural$india.no.contacts.rural
                    ) %>% rename( contact_location=predictor_contact )

india_mix.sum.no15[[2]] <- 
  summariseContacts(df = india_mix.urban$india_mix.urban %>% rename(predictor_contact = contact_location2), 
                    filter.contact_duration = c("<5 mins", "5-15 mins"),
                    no.contacts = india_mix.urban$india.no.contacts.urban
                    ) %>% rename( contact_location=predictor_contact )
names(india_mix.sum.no15) <- c("india_mix.sum.no15.rural", "india_mix.sum.no15.urban")
#saveRDS(india_mix.sum.no15, file = "../data/network_params/india_mix.sum.no15.RData")


## create symmetrical social mixing matrix by average degree and its proportion ----
avg.matrices.india <- list() # single-day symmetric matrices separately for urban and rural populations
avg.matrix <- 
function(mix.sum){
  
avg.mix <- mix.sum %>%   # average mean degree for 1 day
  select(-c("total_degree", "prop_degree")) %>% 
  mutate(mix = case_when(p_age == "<6mo" & contact_age == "<6mo" ~ "0s-0s",
                         (p_age == "<6mo" & contact_age == "6-11mo") |
                           (p_age == "6-11mo" & contact_age == "<6mo") ~ "0s-0.49s",
                         (p_age == "<6mo" & contact_age == "1-4y") |
                           (p_age == "1-4y" & contact_age == "<6mo") ~ "0s-1s",
                         (p_age == "<6mo" & contact_age == "5-9y") |
                           (p_age == "5-9y" & contact_age == "<6mo") ~ "0s-5s",
                         (p_age == "<6mo" & contact_age == "10-14y") |
                           (p_age == "10-14y" & contact_age == "<6mo") ~ "0s-10s",
                         (p_age == "<6mo" & contact_age == "15-19y") |
                           (p_age == "15-19y" & contact_age == "<6mo") ~ "0s-14.9s",
                         (p_age == "<6mo" & contact_age == "20-29y") |
                           (p_age == "20-29y" & contact_age == "<6mo") ~ "0s-20s",
                         (p_age == "<6mo" & contact_age == "30-39y") |
                           (p_age == "30-39y" & contact_age == "<6mo") ~ "0s-30s",
                         (p_age == "<6mo" & contact_age == "40-59y") |
                           (p_age == "40-59y" & contact_age == "<6mo") ~ "0s-40s",
                         (p_age == "<6mo" & contact_age == "60+y") |
                           (p_age == "60+y" & contact_age == "<6mo") ~ "0s-60s",
                         
                         p_age == "6-11mo" & contact_age == "6-11mo" ~ "0.49s-0.49s",
                         (p_age == "6-11mo" & contact_age == "1-4y") |
                           (p_age == "1-4y" & contact_age == "6-11mo") ~ "0.49s-1s",
                         (p_age == "6-11mo" & contact_age == "5-9y") |
                           (p_age == "5-9y" & contact_age == "6-11mo") ~ "0.49s-5s",
                         (p_age == "6-11mo" & contact_age == "10-14y") |
                           (p_age == "10-14y" & contact_age == "6-11mo") ~ "0.49s-10s",
                         (p_age == "6-11mo" & contact_age == "15-19y") |
                           (p_age == "15-19y" & contact_age == "6-11mo") ~ "0.49s-14.9s",
                         (p_age == "6-11mo" & contact_age == "20-29y") |
                           (p_age == "20-29y" & contact_age == "6-11mo") ~ "0.49s-20s",
                         (p_age == "6-11mo" & contact_age == "30-39y") |
                           (p_age == "30-39y" & contact_age == "6-11mo") ~ "0.49s-30s",
                         (p_age == "6-11mo" & contact_age == "40-59y") |
                           (p_age == "40-59y" & contact_age == "6-11mo") ~ "0.49s-40s",
                         (p_age == "6-11mo" & contact_age == "60+y") |
                           (p_age == "60+y" & contact_age == "6-11mo") ~ "0.49s-60s",
                         
                         p_age == "1-4y" & contact_age == "1-4y" ~ "1s-1s",
                         (p_age == "1-4y" & contact_age == "5-9y") |
                           (p_age == "5-9y" & contact_age == "1-4y") ~ "1s-5s",
                         (p_age == "1-4y" & contact_age == "10-14y") |
                           (p_age == "10-14y" & contact_age == "1-4y") ~ "1s-10s",
                         (p_age == "1-4y" & contact_age == "15-19y") |
                           (p_age == "15-19y" & contact_age == "1-4y") ~ "1s-14.9s",
                         (p_age == "1-4y" & contact_age == "20-29y") |
                           (p_age == "20-29y" & contact_age == "1-4y") ~ "1s-20s",
                         (p_age == "1-4y" & contact_age == "30-39y") |
                           (p_age == "30-39y" & contact_age == "1-4y") ~ "1s-30s",
                         (p_age == "1-4y" & contact_age == "40-59y") |
                           (p_age == "40-59y" & contact_age == "1-4y") ~ "1s-40s",
                         (p_age == "1-4y" & contact_age == "60+y") |
                           (p_age == "60+y" & contact_age == "1-4y") ~ "1s-60s",
                         
                         p_age == "5-9y" & contact_age == "5-9y" ~ "5s-5s",
                         (p_age == "5-9y" & contact_age == "10-14y") |
                           (p_age == "10-14y" & contact_age == "5-9y") ~ "5s-10s",
                         (p_age == "5-9y" & contact_age == "15-19y") |
                           (p_age == "15-19y" & contact_age == "5-9y") ~ "5s-14.9s",
                         (p_age == "5-9y" & contact_age == "20-29y") |
                           (p_age == "20-29y" & contact_age == "5-9y") ~ "5s-20s",
                         (p_age == "5-9y" & contact_age == "30-39y") |
                           (p_age == "30-39y" & contact_age == "5-9y") ~ "5s-30s",
                         (p_age == "5-9y" & contact_age == "40-59y") |
                           (p_age == "40-59y" & contact_age == "5-9y") ~ "5s-40s",
                         (p_age == "5-9y" & contact_age == "60+y") |
                           (p_age == "60+y" & contact_age == "5-9y") ~ "5s-60s",
                         
                         p_age == "10-14y" & contact_age == "10-14y" ~ "10s-10s",
                         (p_age == "10-14y" & contact_age == "15-19y") |
                           (p_age == "15-19y" & contact_age == "10-14y") ~ "10s-14.9s",
                         (p_age == "10-14y" & contact_age == "20-29y") |
                           (p_age == "20-29y" & contact_age == "10-14y") ~ "10s-20s",
                         (p_age == "10-14y" & contact_age == "30-39y") |
                           (p_age == "30-39y" & contact_age == "10-14y") ~ "10s-30s",
                         (p_age == "10-14y" & contact_age == "40-59y") |
                           (p_age == "40-59y" & contact_age == "10-14y") ~ "10s-40s",
                         (p_age == "10-14y" & contact_age == "60+y") |
                           (p_age == "60+y" & contact_age == "10-14y") ~ "10s-60s",                         
                         
                         p_age == "15-19y" & contact_age == "15-19y" ~ "14.9s-14.9s",
                         (p_age == "15-19y" & contact_age == "20-29y") |
                           (p_age == "20-29y" & contact_age == "15-19y") ~ "14.9s-20s",
                         (p_age == "15-19y" & contact_age == "30-39y") |
                           (p_age == "30-39y" & contact_age == "15-19y") ~ "14.9s-30s",
                         (p_age == "15-19y" & contact_age == "40-59y") |
                           (p_age == "40-59y" & contact_age == "15-19y") ~ "14.9s-40s",
                         (p_age == "15-19y" & contact_age == "60+y") |
                           (p_age == "60+y" & contact_age == "15-19y") ~ "14.9s-60s", 
                         
                         p_age == "20-29y" & contact_age == "20-29y" ~ "20s-20s",
                         (p_age == "20-29y" & contact_age == "30-39y") |
                           (p_age == "30-39y" & contact_age == "20-29y") ~ "20s-30s",
                         (p_age == "20-29y" & contact_age == "40-59y") |
                           (p_age == "40-59y" & contact_age == "20-29y") ~ "20s-40s",
                         (p_age == "20-29y" & contact_age == "60+y") |
                           (p_age == "60+y" & contact_age == "20-29y") ~ "20s-60s",   
                         
                         p_age == "30-39y" & contact_age == "30-39y" ~ "30s-30s",
                         (p_age == "30-39y" & contact_age == "40-59y") |
                           (p_age == "40-59y" & contact_age == "30-39y") ~ "30s-40s",
                         (p_age == "30-39y" & contact_age == "60+y") |
                           (p_age == "60+y" & contact_age == "30-39y") ~ "30s-60s", 
                         
                         p_age == "40-59y" & contact_age == "40-59y" ~ "40s-40s",
                         (p_age == "40-59y" & contact_age == "60+y") |
                           (p_age == "60+y" & contact_age == "40-59y") ~ "40s-60s", 
                         
                         p_age == "60+y" & contact_age == "60+y" ~ "60s-60s",
                         
                         
                         )
         ) %>%
  ungroup() %>%
  group_by(predictor_contact,mix) %>%
  summarise(degree = mean(degree))

avg.matrix <- avg.mix %>%
  separate(mix,c("age1","age2"), sep = "-") %>% # age 1 is for participant, age 2 is for contact
  mutate(age1 = factor(age1, levels = c("0s",  "0.49s",  "1s",  "5s", "10s", "14.9s", "20s", "30s", "40s", "60s" )
  ),
  age2 = factor(age2, levels = c("0s",  "0.49s",  "1s",  "5s", "10s", "14.9s", "20s", "30s", "40s", "60s" )
  )
  ) %>% 
  arrange(age1, age2) %>% 
  pivot_wider(names_from = "age1",values_from = "degree") # the matrix pivoted by age2" is the same but the degrees are in the other side of the diagnoal
  

avg.total <- avg.mix %>% #total degree of mixing by age group
  ungroup() %>%
  mutate(
  age0s = ifelse((
    (grepl("0s-",mix)|grepl("-0s",mix)) & 
      !(grepl("10s-",mix)| grepl("20s-",mix)|grepl("30s-",mix)| # these age groups are considered as 0s by grepl
          grepl("40s-",mix)|grepl("60s-",mix)) # these age groups are considered as 0s by grepl
  ),
  degree,NA
  ),
  age0.49s = ifelse(grepl("0.49s",mix),degree,NA),
  age1s = ifelse(grepl("1s",mix),degree,NA),
  age5s = ifelse(grepl("5s",mix),degree,NA),
  age10s = ifelse(grepl("10s",mix),degree,NA),
  age14.9s = ifelse(grepl("14.9s",mix),degree,NA),
  age20s = ifelse(grepl("20s",mix),degree,NA),
  age30s = ifelse(grepl("30s",mix),degree,NA),
  age40s = ifelse(grepl("40s",mix),degree,NA),
  age60s = ifelse(grepl("60s",mix),degree,NA)
  ) %>%
  select(-mix,-degree) %>%
  group_by(predictor_contact) %>%
  summarise(age0s = sum(age0s, na.rm = T),
            age0.49s = sum(age0.49s, na.rm = T),
            age1s = sum(age1s, na.rm = T),
            age5s = sum(age5s, na.rm = T),
            age10s = sum(age10s, na.rm = T),
            age14.9s = sum(age14.9s, na.rm = T),
            age20s = sum(age20s, na.rm = T),
            age30s = sum(age30s, na.rm = T),
            age40s = sum(age40s, na.rm = T),
            age60s = sum(age60s, na.rm = T)
  ) %>%
  pivot_longer(cols = -predictor_contact,names_to = "age2", values_to = "total_degree") %>% # same result if pivoted by age1
  mutate(age2 = substr(age2,4,8)
  ) %>% 
  mutate(
    age2 = factor(age2, levels = c("0s",  "0.49s",  "1s",  "5s", "10s", "14.9s", "20s", "30s", "40s", "60s" )
    )
  )

 
  avg.matrix <- avg.matrix %>%
  left_join(avg.total, by = c("predictor_contact","age2")) %>%
  rename(age = age2) %>%
  mutate(prop_match = case_when(age == "0s" ~ `0s`/total_degree,
                                age == "0.49s" ~ `0.49s`/total_degree,
                                age == "1s" ~ `1s`/total_degree,
                                age == "5s" ~ `5s`/total_degree,
                                age == "10s" ~ `10s`/total_degree,
                                age == "14.9s" ~ `14.9s`/total_degree,
                                age == "20s" ~ `20s`/total_degree,
                                age == "30s" ~ `30s`/total_degree,
                                age == "40s" ~ `40s`/total_degree,
                                age == "60s" ~ `60s`/total_degree
                                
                                
  )
  ) %>% 
    mutate(age = as.character(age)) %>% 
    mutate(age = recode(age, 
                        "0s"="<6mo", "0.49s"="6-11mo", "1s"= "1-4y", "5s"="5-9y",
                        "10s"="10-14y", "14.9s"="15-19y", "20s"= "20-29y", "30s"="30-39y",
                        "40s"="40-59y", "60s"="60+y"
                        )
           ) %>% 
    mutate(age = factor(age, levels = c("<6mo","6-11mo","1-4y","5-9y", "10-14y","15-19y","20-29y", "30-39y", "40-59y", "60+y")
                           )
           ) %>% 
    rename(`<6mo`=`0s`, `6-11mo`=`0.49s`, `1-4y`=`1s`, `5-9y`=`5s`,
                        `10-14y`=`10s`, `15-19y`=`14.9s`,  `20-29y` = `20s`, `30-39y`=`30s`,
                        `40-59y`=`40s`, `60+y`=`60s`
           )#matrix with mean degree in each cell
  
  # matrix with proportion
  avg.matrix.prop <- avg.matrix %>% mutate( 
                                     `<6mo` = `<6mo`/total_degree,
                                   `6-11mo` = `6-11mo`/total_degree,
                                   `1-4y` = `1-4y`/total_degree,
                                   `5-9y` = `5-9y`/total_degree,
                                   `10-14y` = `10-14y`/total_degree,
                                   `15-19y` = `15-19y`/total_degree,
                                   `20-29y` = `20-29y`/total_degree,
                                   `30-39y` = `30-39y`/total_degree,
                                   `40-59y` = `40-59y`/total_degree,
                                   `60+y` = `60+y`/total_degree)
  avg.matrix.list <- list()
  avg.matrix.list[[1]] <- avg.matrix %>% ungroup()
  avg.matrix.list[[2]] <- avg.matrix.prop %>% ungroup()
  names(avg.matrix.list) <- c("avg.matrix", "avg.matrix.prop")
  
  avg.matrix.list
} 


avg.matrices.india$avg.matrix.india.rural <- 
avg.matrix(mix.sum = india_mix.sum.no15$india_mix.sum.no15.rural  %>% rename(predictor_contact = contact_location)
           )

avg.matrices.india$avg.matrix.india.urban <- 
avg.matrix(mix.sum = india_mix.sum.no15$india_mix.sum.no15.urban  %>% rename(predictor_contact = contact_location)
           )


#saveRDS(avg.matrices.india, file = "../data/network_params/avg.matrices.india.RData")


```

## Total degree by participants' age group
The below figure shows the total degree of contact in each participant's age group by the type (urban/rural) of study population and network layer (home/nonhome). 

The total degree peaked in the age group of 10-14 years old and gradually became lower in the adjacent age groups. For participants < 1 year old in the rural population, the total degree of 6-11 months old was lower than those < 6 months old.

The participant's total degree tended to be higher at home than non-home locations among those that were not teenagers (10-19y). 


```{r pressure, echo=FALSE}
annotate_figure(
  
ggarrange(
# Total degree by participant age group and network predictor
india_mix.sum.no15$india_mix.sum.no15.rural %>%
  select(contact_location,p_age,total_degree) %>%
  distinct() %>% 
  ggplot( mapping = aes(x = p_age,y = total_degree ,fill = contact_location)
        )+
  geom_bar(stat="identity")+
  theme_classic()+
  labs(x = "", y = "", color = "contact_location")+theme(legend.position = "top")+
  guides(fill=guide_legend(title=""))+
  ggtitle("Rural") +
  theme(plot.title = element_text(hjust = 0.5))+ scale_y_continuous(limits = c(0, 15)),

india_mix.sum.no15$india_mix.sum.no15.urban %>%
  select(contact_location,p_age,total_degree) %>%
  distinct() %>% 
  ggplot( mapping = aes(x = p_age,y = total_degree ,fill = contact_location)
        )+
  geom_bar(stat="identity")+
  theme_classic()+
  labs(x = "", y = "", color = "contact_location")+theme(legend.position = "top")+
  guides(fill=guide_legend(title=""))+
  ggtitle("Urban") +
  theme(plot.title = element_text(hjust = 0.5))+ scale_y_continuous(limits = c(0, 15)),
ncol = 1, nrow = 2,
labels = c("A", "B"),
align = "h",
legend = "top",
common.legend = T
),

left = "Total degree",
bottom = "Participant's age group"
)

```

## Symmetrical mixing matrices
### Home/nonhome mixing in the rural population
In the rural setting, the mixings at home were generally more heterogeneous than nonhome settings. In nonhome settings, the degrees of mixing for those < one year old were generally lower than home settings and close to zero.  The higest degrees were observed in the mixing within the same age groups of 5-9 years old and 10-14 years old in the nonhome settings.  

```{r, echo=F, warning=F, message=FALSE, error =F, fig.width=6, fig.height=6}
# symmetric home matrix, rural
avg.matrix.india.rural.home <- 
avg.matrices.india$avg.matrix.india.rural$avg.matrix  %>% ungroup() %>% filter(predictor_contact == "Home") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `<6mo`:`60+y`, names_to = "vertical_age_grp", values_to = "degree") %>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_contact$contact_age)
                                                                                                                                                                                                                                                                       )
                                                                                                                                                                                                                                             )

# symmetric non-home matrix, rural
avg.matrix.india.rural.nonhome <- 
avg.matrices.india$avg.matrix.india.rural$avg.matrix  %>% ungroup() %>% filter(predictor_contact == "Nonhome") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `<6mo`:`60+y`, names_to = "vertical_age_grp", values_to = "degree")%>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_contact$contact_age)
                                                                                                                                                                                                                                                                       ))
                                                                        
max.degree. <- # max degree across all setting to define the upper bound of color legend
ceiling(
  max(
max(avg.matrices.india$avg.matrix.india.rural$avg.matrix %>% select(`<6mo`:`60+y`), na.rm = T),
max(avg.matrices.india$avg.matrix.india.urban$avg.matrix %>% select(`<6mo`:`60+y`), na.rm = T)
))

symmetric_contactmatrix_viz <- function(matrix_long, max.degree, panel_title){ #title, txt_size, mid, max, legendpos) {
  ggplot(data = matrix_long, aes(x=vertical_age_grp, y=forcats::fct_rev(age), fill=degree)) +  
    geom_raster(hjust = 0.5, vjust = 0.5, show.legend=T) +
    scale_colour_discrete(na.translate = F) +
    scale_fill_gradient2(low="#0571b0", mid="#92c5de", high="#ca0020" , limit = c(0, max.degree),  midpoint =  max.degree/2)+
                       
    theme_classic() +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 10),
          legend.justification = "right",
          legend.position = "right") +
    theme(plot.title = element_text(size = 10), 
          axis.title.x = element_text(size=10, face="bold", angle=0),
          axis.title.y = element_text(size=10, face="bold"),
          axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size= 10))+
    xlab("")+ylab("")+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+ 
    labs(fill="Degree")+ggtitle(panel_title)
 }
 
annotate_figure(
  
ggarrange(
symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.rural.home, max.degree = max.degree., 
                            panel_title = "Home, Rural")+
  theme(axis.text.x=element_blank()),
      

symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.rural.nonhome, max.degree = max.degree., 
                            panel_title = "Nonhome, Rural"),

ncol = 1, nrow = 2,

align = "h",
legend = "top",
common.legend = T
),

left = "Age",
bottom = "Age"
)




```

### Home/nonhome mixing in the urban population
The mixing matrices in the home and nonhome settings in the urban population are generally similar to those in the rural population.
```{r, echo=F, warning=F, message=FALSE, error =F, fig.width=6, fig.height=6}
# symmetric home matrix, urban
avg.matrix.india.urban.home <- 
avg.matrices.india$avg.matrix.india.urban$avg.matrix  %>% ungroup() %>% filter(predictor_contact == "Home") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `<6mo`:`60+y`, names_to = "vertical_age_grp", values_to = "degree") %>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_contact$contact_age)
                                                                                                                                                                                                                                                                       )
                                                                                                                                                                                                                                             )

# symmetric non-home matrix, urban
avg.matrix.india.urban.nonhome <- 
avg.matrices.india$avg.matrix.india.urban$avg.matrix  %>% ungroup() %>% filter(predictor_contact == "Nonhome") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `<6mo`:`60+y`, names_to = "vertical_age_grp", values_to = "degree")%>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_contact$contact_age)
                                                                                                                                                                                                                                                                       )
                                                                                                                                                                                                                                             )

annotate_figure(
  
ggarrange(

symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.urban.home, max.degree = max.degree., 
                            panel_title = "Home, Urban")+
  theme(axis.text.x=element_blank()),
symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.urban.nonhome, max.degree = max.degree., 
                            panel_title = "Nonhome, Urban"),


ncol = 1, nrow = 2,

align = "h",
legend = "top",
common.legend = T
),

left = "Age",
bottom = "Age"
)



```

## Degree proportion of contact age by participant age
The following plots consider the direction of contact (between participants and contacts) and were presented to validate the symmetry mixing matrices. Overall, the proportion distributions mirror the degree distributions in the symmetric mixing matrices. Notably, for participants < one year old, they had non-home contacts with more age groups in urban than rural setting. The patterns were similar across network layers (home/nonhome) and study populations (urban/rual) for age groups ≥ one year old.

### Proportion of the study population in rural areas
```{r, echo=F, warning=F, message=FALSE, error =F, fig.width=7, fig.height=7}



degree.proportion.age <- function(mix.sum, panel_title){
  ggplot(data = mix.sum,
       mapping = aes(x = p_age,
                     y = prop_degree,
                     fill = contact_age)
       ) +
  geom_bar(stat="identity")+
  theme_classic()+
  labs(x = "", y = "")+ 
  guides(fill=guide_legend(title="Contact age")
  )+ggtitle(panel_title)
}




annotate_figure(
  
ggarrange(

degree.proportion.age(mix.sum = india_mix.sum.no15$india_mix.sum.no15.rural %>% filter(contact_location == "Home"), 
                      panel_title = "Home, Rural")+
  theme(axis.text.x=element_blank()),

degree.proportion.age(mix.sum = india_mix.sum.no15$india_mix.sum.no15.rural %>% filter(contact_location == "Nonhome"), 
                      panel_title = "Nonhome, Rural"),


ncol = 1, nrow = 2,

align = "h",
legend = "right",
common.legend = T
),

left = "Degree Proportion",
bottom = "Participant age"
)



```

### Proportion of the study population in urban areas
```{r, echo=F, warning=F, message=FALSE, error =F, fig.width=7, fig.height=7}

annotate_figure(
  
ggarrange(

degree.proportion.age(mix.sum = india_mix.sum.no15$india_mix.sum.no15.urban %>% filter(contact_location == "Home"), 
                      panel_title = "Home, Urban")+
  theme(axis.text.x=element_blank()),

degree.proportion.age(mix.sum = india_mix.sum.no15$india_mix.sum.no15.urban %>% filter(contact_location == "Nonhome"), 
                      panel_title = "Nonhome, Urban"),


ncol = 1, nrow = 2,

align = "h",
legend = "right",
common.legend = T
),

left = "Degree Proportion",
bottom = "Participant age"
)

```

