---
title: "Descriptive Degree Summary of GlobalMix India Data"
author: "Billy Dehao Chen"
date: "7/31/2023"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

# Background
This is a descriptive summary of contact degree of the India GlobalMix diary data.

# Method
We adapted the code Maria developed for the CorporateMix data to the GlobalMix data to calculate degree information. The degree information was summarized into four separate networks for two different epidemic models (one rural, one urban). We consider the mixing occurs within locations (urban, rural) and across two types of network layers (home/nonhome, indoors/outdoors). We do not model contacts across layers, as we assume they are mutually exclusive across environments.


We excluded contacts lasted ≤ 15 mins in analysis. The degree information was summarized as the average degree of the two-day visits. Given the data were egocentric, we use $M.D.=\frac{edges}{n}$ for the relationship between mean degree ($M.D.$) and the number of edges.


```{r, echo=F, warning=F, message=FALSE, include = FALSE}
# Load libraries and data  ------------------------------------------------
lapply(c("ggpubr", "statnet", "EpiModel", "tidyverse", "socialmixr", "knitr",  "sjlabelled", "kableExtra"), require, character.only = TRUE)


## participant data
india_participant <- 
 # readRDS('./data/participant_contact/india_participant_data_aim1.RDS') #%>% rename(id = rec_id)
readRDS("~/Documents/GitHub/COVID-GlobalMix/data/participant_contact/india_participant_data_aim1.RDS")%>% rename(id = rec_id)


## contact data 
india_contact <- 
 # readRDS("./data/participant_contact/india_contact_data_aim1.RDS") %>% rename(id = rec_id)
 readRDS("~/Documents/GitHub/COVID-GlobalMix/data/participant_contact/india_contact_data_aim1.RDS")%>% rename(id = rec_id)

# Note - validated study_site of participant is exactly the same as those in contact

# Reclassifying participant's and contact's age groups into 0-9 years old, 10-19 years old, while treating other age groups as is.
## participant
india_participant <- 
india_participant %>% 
  mutate(
      participant_age_reclass = case_when(
        participant_age %in% c("<6mo", "6-11mo",   "1-4y",   "5-9y") ~ "0-9y",
        participant_age %in% c("10-14y", "15-19y") ~ "10-19y",
        .default =  participant_age
      )
    )%>% 
  mutate(participant_age_reclass= factor(participant_age_reclass, levels=c("0-9y", "10-19y", "20-29y", "30-39y", "40-59y",   "60+y")
                                         )
         ) 

## contact
india_contact <- 
india_contact %>%     
  mutate(
      contact_age_reclass = case_when(
        contact_age %in% c("<6mo", "6-11mo",   "1-4y",   "5-9y") ~ "0-9y",
        contact_age %in% c("10-14y", "15-19y") ~ "10-19y",
        .default =  contact_age
      )
    )%>% 
    mutate(contact_age_reclass= factor(contact_age_reclass, levels=c("0-9y", "10-19y", "20-29y", "30-39y", "40-59y",   "60+y")
                                         )
         )

# merge participants and contact datasets and process data  ------------------------------------------------
india_mix <- india_participant %>%
  dplyr::select(id,participant_age, participant_age_reclass) %>%
  right_join(india_contact,by = "id") %>% 
  # characterization of home/nonhome status
  mutate(contact_location2 = case_when(location_contact___0 == 1  ~ "Home", # 0 - "My home"
                                       
                                       location_contact___1 == 1 | location_contact___2 == 1 | location_contact___3 == 1 | location_contact___4 == 1 | # "Other home", "School", "Work", "Transport/Hub"
                                       location_contact___5 == 1 | location_contact___6 == 1 | # "Market/Shop", "Street"
                                       location_contact___7 == 1 | location_contact___8 == 1 | # "Playground", "Well"
                                       location_contact___9 == 1 | location_contact___10 == 1 | # "Agricultural Field", "Market/Shop"
                                       location_contact___11 == 1 | location_contact___12 == 1 | # "Restaurant", "Religious centre"
                                       location_contact___13 == 1 | location_contact___14 == 1 | # "Govt offices", "Health center"
                                       location_contact___15 == 1 | location_contact___16 == 1 | # "Bank", "Movie theatre"
                                       location_contact___17 == 1 | location_contact___18 == 1 | location_contact___19 == 1 #"Exhibition", "Social hall", "Other"
                                       ~ "Nonhome") # assign contacts into home or nonhome layer
         ) 


tb_contact_location <-  
  table(india_mix$contact_location2, useNA = c("always")
             ) 
```
## Characterization of home-nonhome status
The home-nonhome status is processed from multiple questions asking contact location; given these questions are not mutually exclusive due to the check-box design in REDCap, a contact is characterized as at home when any contact with a participant reportedly occurred at the participant's home (i.e., "my home") but not at other's home, regardless of the responses for other contact location types. For contacts did not occurred at home, they were characterized as occurring in a nonhome location if any of the nonhome locations were checked, including other's home. Given the sociological contact pattern in a participant's residence and other’s home is likely vary, we consider contacts occurring at home and other's home separately. For a contact checked neither home nor nonhome location, we assigned an NA to this contact. Below is a breakdown of the frequency of contact, in which there was `r paste0(as.numeric(round(tb_contact_location[3]/nrow(india_mix)*100)), "%")` of contact did not check any of the contact locations. We excluded these contacts in analysis.
```{r, echo=F, warning=F, message=FALSE}
kable(tb_contact_location, col.names = c("Contact location", "Freq."))%>% kableExtra::kable_classic(full_width = F, html_font = "Cambria")
```

## Distribution of indoor/outdoor status
The following is a break down of the observed categories of the variable "where_contact" indicating in- and out-door status. Correspondence with Moses is ongoing for the interpretation of the "Both" category.

```{r, echo=F, warning=F, message=FALSE}
kable(table(india_contact$where_contact, useNA = "always"), col.names = c("In-/outdoors", "Freq."))%>%
   kableExtra::kable_classic(full_width = F, html_font = "Cambria")
#chisq.test(table(india_mix$contact_location2, india_mix$study_site))
```

## Repeated contacts
### Distribution of unique/repeated contacts
The following table shows the distribution of repeated/unique contact of the whole India data, regardless of network and layer types.
```{r, echo=F, warning=F, message=FALSE}
kable( table(india_mix$fromdayone, useNA = "always"), col.names = c("Contact day", "Freq."))%>%
   kableExtra::kable_classic(full_width = F, html_font = "Cambria")

```
### Descriptive analysis of repeated/unique contacts in the non-home category
```{r, echo=F, warning=F, message=FALSE}
nonhome_dup_descib <- function(mix, network){
  
  output <- list()
  
#india_mix_nonhome <- # later, we may account for rural/urban status
output$overall_freq <- 
  mix %>% filter(study_site==network & contact_location2 == "Nonhome") %>% group_by(fromdayone) %>% 
  summarize(n=n()
            ) %>% 
  mutate(prop = n/sum(n)) %>% # ~2/3 of the contacts in the nonhome category were duplicated 
  mutate_if(is.numeric, round, 3)


#india_mix_nonhome_bothdays <- # nonhome contacts spanning two days. 
location_labs <- as.character(get_label(mix))
location_labs <-as.character(location_labs)[which(location_labs=="My home"):which(location_labs=="Other")]

location_freq <- 
mix %>% filter(study_site==network & contact_location2 == "Nonhome" & fromdayone == "Both days")%>%
  select(location_contact___0:location_contact___19) %>% `colnames<-`(location_labs)  %>% colSums() %>% sort(., decreasing =T) # most contacts occurred at school, street, and other's home 
 
output$location_freq <- 
location_freq[location_freq>100] 

output

}


nonhome_dup_rural <- 
nonhome_dup_descib(mix = india_mix, network = "Rural")


nonhome_dup_urban <- 
nonhome_dup_descib(mix = india_mix, network = "Urban")
```

The following table summarizes the (relative) frequencies of repeated/unique contact for the non-home category in the rural versus urban settings.
```{r, echo=F, warning=F, message=FALSE}


kable(list(nonhome_dup_rural$overall_freq %>% rename(`fromdayone, rural` = fromdayone),
           
           nonhome_dup_urban$overall_freq %>% rename(`fromdayone, urban` = fromdayone)))%>%
   kableExtra::kable_classic(full_width = F, html_font = "Cambria")

```

The following figure shows the frequency of duplicated contacts by contact location of the two-day study period. Contact locations with frequencies > 100 were shown.
```{r, echo=F, warning=F, message=FALSE, fig.width=10}
par(mfrow = c(1, 2)) 
barplot(nonhome_dup_rural$location_freq, main = "Rural",
        las = 2, cex.names = 1)

barplot(nonhome_dup_urban$location_freq, main = "Urban",
        las = 2, cex.names = 1)


```

```{r, echo=F, warning=F, message=FALSE}
# split data into urban and rural nextworks using study site, and get the number of participants with 0 contact in specified age groups
data_split <- function(india_mix., india_participant., india_contact., study_site., age.grp){
 out <-  list()
 out[[1]] <-
 india_mix. %>% filter(!is.na(contact_location2) # complete-case analysis - exclude contacts didn't have a contact location from analysis
                      ) %>% 
  mutate(contact_location2 = factor(contact_location2,
                                    levels = c("Home","Nonhome"),
                                    ordered = TRUE)
         ) %>% 
  mutate(duration_contact = case_when(duration_contact == ">4 hrs" ~ "4+ hrs",
                                      .default = duration_contact),
         duration_contact = factor(duration_contact,
                                    levels = c("<5 mins", "5-15 mins", "16-30 mins",  
                                               "31 mins-1 hr", "1-4 hrs", "4+ hrs", "Unknown"),
                                    ordered = TRUE)
         ) %>% rename(contact_duration = duration_contact) %>% 
  filter(study_site == study_site.) # here we split the dataset into urban or rural samples


out[[2]] <- # participants with 0 contacts by study site in India
  india_participant. %>%
  filter(!(id %in% india_contact.$id)) %>%
  filter(study_site == study_site.) %>% # here we split the dataset into urban or rural samples
  group_by(participant_age) %>%
  tally(name = "n_participants0")

names(out) <-  c(paste0("india_mix.", tolower(study_site.), age.grp), 
                 paste0("india.no.contacts.",  tolower(study_site.), age.grp)
                 )

out
} 

india_mix.rural.10age.grps <- # rural mixing, original age groups
data_split(india_mix. = india_mix %>% select(-participant_age_reclass, -contact_age_reclass), 
           india_participant. = india_participant %>% select(-participant_age_reclass), 
           india_contact. = india_contact %>% select( -contact_age_reclass),
           study_site. ="Rural", age.grp = ".10age.grps") # 

india_mix.urban.10age.grps <- # urban mixing, original age groups
data_split(india_mix. = india_mix %>% select(-participant_age_reclass, -contact_age_reclass), 
           india_participant. = india_participant %>% select(-participant_age_reclass), 
           india_contact. = india_contact %>% select( -contact_age_reclass),
           study_site. ="Urban", age.grp = ".10age.grps") # .10age.grps


india_mix.rural.6age.grps <- # rural mixing, six age groups
data_split(india_mix. = india_mix %>% 
             select(-c(participant_age,contact_age)) %>% 
             rename(participant_age = participant_age_reclass,
                    contact_age = contact_age_reclass
                    ), 
           india_participant. = india_participant %>% 
             select(-participant_age) %>% 
             rename(participant_age = participant_age_reclass), 
           
           india_contact. = india_contact%>% 
             select(-contact_age) %>% 
             rename(contact_age = contact_age_reclass),
           study_site. ="Rural", age.grp = ".6age.grps") # .6age.grps


india_mix.urban.6age.grps <- # urban mixing, six age groups
data_split(india_mix. = india_mix %>% 
             select(-c(participant_age,contact_age)) %>% 
             rename(participant_age = participant_age_reclass,
                    contact_age = contact_age_reclass
                    ), 
           india_participant. = india_participant %>% 
             select(-participant_age) %>% 
             rename(participant_age = participant_age_reclass), 
           
           india_contact. = india_contact%>% 
             select(-contact_age) %>% 
             rename(contact_age = contact_age_reclass),
           study_site. ="Urban", age.grp = ".6age.grps") # .6age.grps



# function to compile data by participant's and contact's age groups and estimate mean degree (duplicated contacts/dyads at home were counted once)------
summariseContacts <- function(df,
                              filter.contact_duration, 
                              no.contacts
                          
) { 
  
 df %>%
  select(id,participant_age, fromdayone,contact_age,predictor_contact, contact_duration) %>% # summarizing degree by contact location
  rename(p_age = participant_age) %>%
  group_by(p_age) %>%
  mutate(n_participants = n_distinct(id)) %>%  # total number of participants by age group
  ungroup() %>%
  filter(!(contact_duration %in% filter.contact_duration)) %>% # filter out contact with duratioin ≤ 15 mins
  group_by(predictor_contact,p_age,contact_age,n_participants, fromdayone, .drop = FALSE) %>%
  summarise(n_contacts = n()) %>%  # total number of contacts reported over the 2 study days, by predictor_contact, participant's age group, contact's age group, total number of participants in each age group
  mutate(n_contacts = case_when(predictor_contact == "Home" & fromdayone == "Both days" ~ n_contacts/2, # for repeated home contacts over two days, we count them once
                                TRUE ~ n_contacts)
         ) %>%
  filter(!is.na(fromdayone)) %>% # complete case analysis for fromdayone
  group_by(predictor_contact,p_age,contact_age,n_participants, .drop = FALSE) %>%
  summarise(n_contacts = sum(n_contacts)) %>% # summ all the contacts in all categories of "fromdayone" together
  ungroup() %>%
  complete(predictor_contact,p_age,contact_age) %>% # complete-case analysis
  group_by(predictor_contact,p_age) %>%
  fill(n_participants,.direction = "downup") %>% # filling n_participants in groups with 0 contact
  mutate(degree = (n_contacts/n_participants)/2) %>%   # average mean degree for 1 day, the 2 here is to average 2-day degree
  mutate(total_degree = sum(degree)) %>%  # total degree by predictor_contact and participant age group
  mutate(prop_degree = degree/total_degree)  %>% # age distribution of contacts by predictor_contact and participant age
  ungroup() %>%  
  ## add participants with 0 contacts to update n_participants and degree-----------------------------
left_join(no.contacts %>% rename("p_age" = "participant_age"),by = c("p_age")
) %>%
  mutate(n_participants = rowSums(.[c("n_participants", "n_participants0")], na.rm = TRUE)) %>%  # update n_participants; replacing script mutate(n_participants_test = n_participants + n_participants0) from CorporateMix, given NA in n_participants0 caused by fewer categories w/ zero contact
  select(-n_participants0) %>% 
  group_by(predictor_contact,p_age)  %>%
  mutate(degree = (n_contacts/n_participants)/2) %>%   # average mean degree for 1 day
  mutate(total_degree = sum(degree)) %>%  # total degree by predictor_contact and participant age
  mutate(prop_degree = degree/total_degree) %>%   # age distribution of contacts by predictor_contact and participant age
  ungroup()

  
}

india_mix.sum.no15 <- list() # degree for each study site is outputted separately

india_mix.sum.no15[[1]] <- 
  summariseContacts(df = india_mix.rural.10age.grps$india_mix.rural.10age.grps %>% rename(predictor_contact = contact_location2), 
                    filter.contact_duration = c("<5 mins", "5-15 mins"),
                    no.contacts = india_mix.rural.10age.grps$india.no.contacts.rural.10age.grps
                    ) %>% rename( contact_location=predictor_contact )

india_mix.sum.no15[[2]] <- 
  summariseContacts(df = india_mix.urban.10age.grps$india_mix.urban.10age.grps %>% rename(predictor_contact = contact_location2), 
                    filter.contact_duration = c("<5 mins", "5-15 mins"),
                    no.contacts = india_mix.urban.10age.grps$india.no.contacts.urban.10age.grps
                    ) %>% rename( contact_location=predictor_contact )

india_mix.sum.no15[[3]] <- 
  summariseContacts(df = india_mix.rural.6age.grps$india_mix.rural.6age.grps %>% rename(predictor_contact = contact_location2), 
                    filter.contact_duration = c("<5 mins", "5-15 mins"),
                    no.contacts = india_mix.rural.6age.grps$india.no.contacts.rural.6age.grps
                    ) %>% rename( contact_location=predictor_contact )

india_mix.sum.no15[[4]] <- 
  summariseContacts(df = india_mix.urban.6age.grps$india_mix.urban.6age.grps %>% rename(predictor_contact = contact_location2), 
                    filter.contact_duration = c("<5 mins", "5-15 mins"),
                    no.contacts = india_mix.urban.6age.grps$india.no.contacts.urban.6age.grps
                    ) %>% rename( contact_location=predictor_contact )



names(india_mix.sum.no15) <- c("india_mix.sum.no15.rural.10age.grps", "india_mix.sum.no15.urban.10age.grps",
                               "india_mix.sum.no15.rural.6age.grps", "india_mix.sum.no15.urban.6age.grps"
                               )


#saveRDS(india_mix.sum.no15, file = "./data/network_params/india_mix.sum.no15.RData")


# create symmetrical social mixing matrix by average degree and its proportion ----
avg.matrices.india <- list() # single-day symmetric matrices separately for urban and rural populations
avg.matrix <- 
  function(mix.sum, age_grp_count){
    
    if (age_grp_count == 10){
    avg.mix <- mix.sum %>%   # average mean degree for 1 day
      select(-c("total_degree", "prop_degree")) %>% 
      mutate(mix = case_when(p_age == "<6mo" & contact_age == "<6mo" ~ "0s-0s",
                             (p_age == "<6mo" & contact_age == "6-11mo") |
                               (p_age == "6-11mo" & contact_age == "<6mo") ~ "0s-0.49s",
                             (p_age == "<6mo" & contact_age == "1-4y") |
                               (p_age == "1-4y" & contact_age == "<6mo") ~ "0s-1s",
                             (p_age == "<6mo" & contact_age == "5-9y") |
                               (p_age == "5-9y" & contact_age == "<6mo") ~ "0s-5s",
                             (p_age == "<6mo" & contact_age == "10-14y") |
                               (p_age == "10-14y" & contact_age == "<6mo") ~ "0s-10s",
                             (p_age == "<6mo" & contact_age == "15-19y") |
                               (p_age == "15-19y" & contact_age == "<6mo") ~ "0s-14.9s",
                             (p_age == "<6mo" & contact_age == "20-29y") |
                               (p_age == "20-29y" & contact_age == "<6mo") ~ "0s-20s",
                             (p_age == "<6mo" & contact_age == "30-39y") |
                               (p_age == "30-39y" & contact_age == "<6mo") ~ "0s-30s",
                             (p_age == "<6mo" & contact_age == "40-59y") |
                               (p_age == "40-59y" & contact_age == "<6mo") ~ "0s-40s",
                             (p_age == "<6mo" & contact_age == "60+y") |
                               (p_age == "60+y" & contact_age == "<6mo") ~ "0s-60s",
                             
                             p_age == "6-11mo" & contact_age == "6-11mo" ~ "0.49s-0.49s",
                             (p_age == "6-11mo" & contact_age == "1-4y") |
                               (p_age == "1-4y" & contact_age == "6-11mo") ~ "0.49s-1s",
                             (p_age == "6-11mo" & contact_age == "5-9y") |
                               (p_age == "5-9y" & contact_age == "6-11mo") ~ "0.49s-5s",
                             (p_age == "6-11mo" & contact_age == "10-14y") |
                               (p_age == "10-14y" & contact_age == "6-11mo") ~ "0.49s-10s",
                             (p_age == "6-11mo" & contact_age == "15-19y") |
                               (p_age == "15-19y" & contact_age == "6-11mo") ~ "0.49s-14.9s",
                             (p_age == "6-11mo" & contact_age == "20-29y") |
                               (p_age == "20-29y" & contact_age == "6-11mo") ~ "0.49s-20s",
                             (p_age == "6-11mo" & contact_age == "30-39y") |
                               (p_age == "30-39y" & contact_age == "6-11mo") ~ "0.49s-30s",
                             (p_age == "6-11mo" & contact_age == "40-59y") |
                               (p_age == "40-59y" & contact_age == "6-11mo") ~ "0.49s-40s",
                             (p_age == "6-11mo" & contact_age == "60+y") |
                               (p_age == "60+y" & contact_age == "6-11mo") ~ "0.49s-60s",
                             
                             p_age == "1-4y" & contact_age == "1-4y" ~ "1s-1s",
                             (p_age == "1-4y" & contact_age == "5-9y") |
                               (p_age == "5-9y" & contact_age == "1-4y") ~ "1s-5s",
                             (p_age == "1-4y" & contact_age == "10-14y") |
                               (p_age == "10-14y" & contact_age == "1-4y") ~ "1s-10s",
                             (p_age == "1-4y" & contact_age == "15-19y") |
                               (p_age == "15-19y" & contact_age == "1-4y") ~ "1s-14.9s",
                             (p_age == "1-4y" & contact_age == "20-29y") |
                               (p_age == "20-29y" & contact_age == "1-4y") ~ "1s-20s",
                             (p_age == "1-4y" & contact_age == "30-39y") |
                               (p_age == "30-39y" & contact_age == "1-4y") ~ "1s-30s",
                             (p_age == "1-4y" & contact_age == "40-59y") |
                               (p_age == "40-59y" & contact_age == "1-4y") ~ "1s-40s",
                             (p_age == "1-4y" & contact_age == "60+y") |
                               (p_age == "60+y" & contact_age == "1-4y") ~ "1s-60s",
                             
                             p_age == "5-9y" & contact_age == "5-9y" ~ "5s-5s",
                             (p_age == "5-9y" & contact_age == "10-14y") |
                               (p_age == "10-14y" & contact_age == "5-9y") ~ "5s-10s",
                             (p_age == "5-9y" & contact_age == "15-19y") |
                               (p_age == "15-19y" & contact_age == "5-9y") ~ "5s-14.9s",
                             (p_age == "5-9y" & contact_age == "20-29y") |
                               (p_age == "20-29y" & contact_age == "5-9y") ~ "5s-20s",
                             (p_age == "5-9y" & contact_age == "30-39y") |
                               (p_age == "30-39y" & contact_age == "5-9y") ~ "5s-30s",
                             (p_age == "5-9y" & contact_age == "40-59y") |
                               (p_age == "40-59y" & contact_age == "5-9y") ~ "5s-40s",
                             (p_age == "5-9y" & contact_age == "60+y") |
                               (p_age == "60+y" & contact_age == "5-9y") ~ "5s-60s",
                             
                             p_age == "10-14y" & contact_age == "10-14y" ~ "10s-10s",
                             (p_age == "10-14y" & contact_age == "15-19y") |
                               (p_age == "15-19y" & contact_age == "10-14y") ~ "10s-14.9s",
                             (p_age == "10-14y" & contact_age == "20-29y") |
                               (p_age == "20-29y" & contact_age == "10-14y") ~ "10s-20s",
                             (p_age == "10-14y" & contact_age == "30-39y") |
                               (p_age == "30-39y" & contact_age == "10-14y") ~ "10s-30s",
                             (p_age == "10-14y" & contact_age == "40-59y") |
                               (p_age == "40-59y" & contact_age == "10-14y") ~ "10s-40s",
                             (p_age == "10-14y" & contact_age == "60+y") |
                               (p_age == "60+y" & contact_age == "10-14y") ~ "10s-60s",                         
                             
                             p_age == "15-19y" & contact_age == "15-19y" ~ "14.9s-14.9s",
                             (p_age == "15-19y" & contact_age == "20-29y") |
                               (p_age == "20-29y" & contact_age == "15-19y") ~ "14.9s-20s",
                             (p_age == "15-19y" & contact_age == "30-39y") |
                               (p_age == "30-39y" & contact_age == "15-19y") ~ "14.9s-30s",
                             (p_age == "15-19y" & contact_age == "40-59y") |
                               (p_age == "40-59y" & contact_age == "15-19y") ~ "14.9s-40s",
                             (p_age == "15-19y" & contact_age == "60+y") |
                               (p_age == "60+y" & contact_age == "15-19y") ~ "14.9s-60s", 
                             
                             p_age == "20-29y" & contact_age == "20-29y" ~ "20s-20s",
                             (p_age == "20-29y" & contact_age == "30-39y") |
                               (p_age == "30-39y" & contact_age == "20-29y") ~ "20s-30s",
                             (p_age == "20-29y" & contact_age == "40-59y") |
                               (p_age == "40-59y" & contact_age == "20-29y") ~ "20s-40s",
                             (p_age == "20-29y" & contact_age == "60+y") |
                               (p_age == "60+y" & contact_age == "20-29y") ~ "20s-60s",   
                             
                             p_age == "30-39y" & contact_age == "30-39y" ~ "30s-30s",
                             (p_age == "30-39y" & contact_age == "40-59y") |
                               (p_age == "40-59y" & contact_age == "30-39y") ~ "30s-40s",
                             (p_age == "30-39y" & contact_age == "60+y") |
                               (p_age == "60+y" & contact_age == "30-39y") ~ "30s-60s", 
                             
                             p_age == "40-59y" & contact_age == "40-59y" ~ "40s-40s",
                             (p_age == "40-59y" & contact_age == "60+y") |
                               (p_age == "60+y" & contact_age == "40-59y") ~ "40s-60s", 
                             
                             p_age == "60+y" & contact_age == "60+y" ~ "60s-60s",
                             
                             
      )
      ) %>%
      ungroup() %>%
      group_by(predictor_contact,mix) %>%
      summarise(degree = mean(degree))
    
    avg.matrix <- avg.mix %>%
      separate(mix,c("age1","age2"), sep = "-") %>% # age 1 is for participant, age 2 is for contact
      mutate(age1 = factor(age1, levels = c("0s",  "0.49s",  "1s",  "5s", "10s", "14.9s", "20s", "30s", "40s", "60s" )
      ),
      age2 = factor(age2, levels = c("0s",  "0.49s",  "1s",  "5s", "10s", "14.9s", "20s", "30s", "40s", "60s" )
      )
      ) %>% 
      arrange(age1, age2) %>% 
      pivot_wider(names_from = "age1",values_from = "degree") # the matrix pivoted by "age2" is the same but the degrees are in the other side of the diagnoal
    
     #total degree of mixing by age group; On 20230731, we validated the below code with the total degree calculation based on mix.sum using the following script and confirm that the total_degree in avg.total is correct
      #mix.sum %>% filter(predictor_contact =="Nonhome" & ((contact_age == "1-4y"|p_age == "1-4y") & !(contact_age == "1-4y"& p_age == "1-4y"))) %>% select(degree)  %>% summarize(sum(degree)/2)+mix.sum %>% filter(predictor_contact =="Nonhome" & ( (contact_age == "1-4y"& p_age == "1-4y"))) %>% select(degree) %>% as.numeric()
    avg.total <- avg.mix %>%
      ungroup() %>%
      mutate(
        age0s = ifelse((
          (grepl("0s-",mix)|grepl("-0s",mix)) & 
            !(grepl("10s-",mix)| grepl("20s-",mix)|grepl("30s-",mix)| # these age groups are considered as 0s by grepl so we excluded them 
                grepl("40s-",mix)|grepl("60s-",mix)) # these age groups are considered as 0s by grepl so we excluded them 
        ),
        degree,NA
        ),
        age0.49s = ifelse(grepl("0.49s",mix),degree,NA),
        age1s = ifelse(grepl("1s",mix),degree,NA),
        age5s = ifelse(grepl("5s",mix),degree,NA),
        age10s = ifelse(grepl("10s",mix),degree,NA),
        age14.9s = ifelse(grepl("14.9s",mix),degree,NA),
        age20s = ifelse(grepl("20s",mix),degree,NA),
        age30s = ifelse(grepl("30s",mix),degree,NA),
        age40s = ifelse(grepl("40s",mix),degree,NA),
        age60s = ifelse(grepl("60s",mix),degree,NA)
      ) %>%
      select(-mix,-degree) %>%
      group_by(predictor_contact) %>%
      summarise(age0s = sum(age0s, na.rm = T),
                age0.49s = sum(age0.49s, na.rm = T),
                age1s = sum(age1s, na.rm = T),
                age5s = sum(age5s, na.rm = T),
                age10s = sum(age10s, na.rm = T),
                age14.9s = sum(age14.9s, na.rm = T),
                age20s = sum(age20s, na.rm = T),
                age30s = sum(age30s, na.rm = T),
                age40s = sum(age40s, na.rm = T),
                age60s = sum(age60s, na.rm = T)
      ) %>%
      pivot_longer(cols = -predictor_contact,names_to = "age2", values_to = "total_degree") %>% # same result if pivoted by age1
      mutate(age2 = substr(age2,4,8)
      ) %>% 
      mutate(
        age2 = factor(age2, levels = c("0s",  "0.49s",  "1s",  "5s", "10s", "14.9s", "20s", "30s", "40s", "60s" )
        )
      )
    
    
    avg.matrix <- avg.matrix %>%
      left_join(avg.total, by = c("predictor_contact","age2")) %>%
      rename(age = age2) %>%
      mutate(prop_match = case_when(age == "0s" ~ `0s`/total_degree,
                                    age == "0.49s" ~ `0.49s`/total_degree,
                                    age == "1s" ~ `1s`/total_degree,
                                    age == "5s" ~ `5s`/total_degree,
                                    age == "10s" ~ `10s`/total_degree,
                                    age == "14.9s" ~ `14.9s`/total_degree,
                                    age == "20s" ~ `20s`/total_degree,
                                    age == "30s" ~ `30s`/total_degree,
                                    age == "40s" ~ `40s`/total_degree,
                                    age == "60s" ~ `60s`/total_degree
                                    
                                    
      )
      ) %>% 
      mutate(age = as.character(age)) %>% 
      mutate(age = recode(age, 
                          "0s"="<6mo", "0.49s"="6-11mo", "1s"= "1-4y", "5s"="5-9y",
                          "10s"="10-14y", "14.9s"="15-19y", "20s"= "20-29y", "30s"="30-39y",
                          "40s"="40-59y", "60s"="60+y"
      )
      ) %>% 
      mutate(age = factor(age, levels = c("<6mo","6-11mo","1-4y","5-9y", "10-14y","15-19y","20-29y", "30-39y", "40-59y", "60+y")
      )
      ) %>% 
      rename(`<6mo`=`0s`, `6-11mo`=`0.49s`, `1-4y`=`1s`, `5-9y`=`5s`,
             `10-14y`=`10s`, `15-19y`=`14.9s`,  `20-29y` = `20s`, `30-39y`=`30s`,
             `40-59y`=`40s`, `60+y`=`60s`
      )#matrix with mean degree in each cell
    
    # matrix with proportion
    avg.matrix.prop <- avg.matrix %>% mutate( 
      `<6mo` = `<6mo`/total_degree,
      `6-11mo` = `6-11mo`/total_degree,
      `1-4y` = `1-4y`/total_degree,
      `5-9y` = `5-9y`/total_degree,
      `10-14y` = `10-14y`/total_degree,
      `15-19y` = `15-19y`/total_degree,
      `20-29y` = `20-29y`/total_degree,
      `30-39y` = `30-39y`/total_degree,
      `40-59y` = `40-59y`/total_degree,
      `60+y` = `60+y`/total_degree)
    
    } 
    else if (age_grp_count == 6){
      
      avg.mix <- mix.sum %>%   # average mean degree for 1 day
        select(-c("total_degree", "prop_degree")) %>% 
        mutate(mix = case_when(
          
                               p_age == "0-9y" & contact_age == "0-9y" ~ "0s-0s",
                               (p_age == "0-9y" & contact_age == "10-19y") |
                                 (p_age == "10-19y" & contact_age == "0-9y") ~ "0s-10s",
                               (p_age == "0-9y" & contact_age == "20-29y") |
                                 (p_age == "20-29y" & contact_age == "0-9y") ~ "0s-20s",
                               (p_age == "0-9y" & contact_age == "30-39y") |
                                 (p_age == "30-39y" & contact_age == "0-9y") ~ "0s-30s",
                               (p_age == "0-9y" & contact_age == "40-59y") |
                                 (p_age == "40-59y" & contact_age == "0-9y") ~ "0s-40s",
                               (p_age == "0-9y" & contact_age == "60+y") |
                                 (p_age == "60+y" & contact_age == "0-9y") ~ "0s-60s",
                               
                               p_age == "10-19y" & contact_age == "10-19y" ~ "10s-10s",
                               (p_age == "10-19y" & contact_age == "20-29y") |
                                 (p_age == "20-29y" & contact_age == "10-19y") ~ "10s-20s",
                               (p_age == "10-19y" & contact_age == "30-39y") |
                                 (p_age == "30-39y" & contact_age == "10-19y") ~ "10s-30s",
                               (p_age == "10-19y" & contact_age == "40-59y") |
                                 (p_age == "40-59y" & contact_age == "10-19y") ~ "10s-40s",
                               (p_age == "10-19y" & contact_age == "60+y") |
                                 (p_age == "60+y" & contact_age == "10-19y") ~ "10s-60s",
                               
                               
                               p_age == "20-29y" & contact_age == "20-29y" ~ "20s-20s",
                               (p_age == "20-29y" & contact_age == "30-39y") |
                                 (p_age == "30-39y" & contact_age == "20-29y") ~ "20s-30s",
                               (p_age == "20-29y" & contact_age == "40-59y") |
                                 (p_age == "40-59y" & contact_age == "20-29y") ~ "20s-40s",
                               (p_age == "20-29y" & contact_age == "60+y") |
                                 (p_age == "60+y" & contact_age == "20-29y") ~ "20s-60s",                         
                               
                               p_age == "30-39y" & contact_age == "30-39y" ~ "30s-30s",
                               (p_age == "30-39y" & contact_age == "40-59y") |
                                 (p_age == "40-59y" & contact_age == "30-39y") ~ "30s-40s",
                               (p_age == "30-39y" & contact_age == "60+y") |
                                 (p_age == "60+y" & contact_age == "30-39y") ~ "30s-60s",     
                               
                               p_age == "40-59y" & contact_age == "40-59y" ~ "40s-40s",
                               (p_age == "40-59y" & contact_age == "60+y") |
                                 (p_age == "60+y" & contact_age == "40-59y") ~ "40s-60s",     
                               
                               p_age == "60+y" & contact_age == "60+y" ~ "60s-60s",
                               
            
                               
        )
        ) %>%
        ungroup() %>%
        group_by(predictor_contact,mix) %>%
        summarise(degree = mean(degree))
      
      avg.matrix <- avg.mix %>%
        separate(mix,c("age1","age2"), sep = "-") %>% # age 1 is for participant, age 2 is for contact
        mutate(age1 = factor(age1, levels = c("0s", "10s",  "20s", "30s", "40s", "60s" )
        ),
        age2 = factor(age2, levels = c("0s", "10s",  "20s", "30s", "40s", "60s" )
        )
        ) %>% 
        arrange(age1, age2) %>% 
        pivot_wider(names_from = "age1",values_from = "degree") # the matrix pivoted by "age2" is the same but the degrees are in the other side of the diagnoal
      
      
      avg.total <- avg.mix %>% #total degree of mixing by age group
        ungroup() %>%
        mutate(
          age0s = ifelse((
            (grepl("0s-",mix)|grepl("-0s",mix)) & 
              !(grepl("10s-",mix)| grepl("20s-",mix)|grepl("30s-",mix)| # these age groups are considered as 0s by grepl so we excluded them 
                  grepl("40s-",mix)|grepl("60s-",mix)) # these age groups are considered as 0s by grepl so we excluded them 
          ),
          degree,NA
          ),
          age10s = ifelse(grepl("10s",mix),degree,NA),
          age20s = ifelse(grepl("20s",mix),degree,NA),
          age30s = ifelse(grepl("30s",mix),degree,NA),
          age40s = ifelse(grepl("40s",mix),degree,NA),
          age60s = ifelse(grepl("60s",mix),degree,NA)
        ) %>%
        select(-mix,-degree) %>%
        group_by(predictor_contact) %>%
        summarise(age0s = sum(age0s, na.rm = T),
                  age10s = sum(age10s, na.rm = T),
                  age20s = sum(age20s, na.rm = T),
                  age30s = sum(age30s, na.rm = T),
                  age40s = sum(age40s, na.rm = T),
                  age60s = sum(age60s, na.rm = T)
        ) %>%
        pivot_longer(cols = -predictor_contact,names_to = "age2", values_to = "total_degree") %>% # same result if pivoted by age1
        mutate(age2 = substr(age2,4,8)
        ) %>% 
        mutate(
          age2 = factor(age2, levels = c("0s", "10s",  "20s", "30s", "40s", "60s")
          )
        )
      
      
      avg.matrix <- avg.matrix %>%
        left_join(avg.total, by = c("predictor_contact","age2")) %>%
        rename(age = age2) %>%
        mutate(prop_match = case_when(age == "0s" ~ `0s`/total_degree,
                                      age == "10s" ~ `10s`/total_degree,
                                      age == "20s" ~ `20s`/total_degree,
                                      age == "30s" ~ `30s`/total_degree,
                                      age == "40s" ~ `40s`/total_degree,
                                      age == "60s" ~ `60s`/total_degree
                                      
                                      
        )
        ) %>% 
        mutate(age = as.character(age)) %>% 
        mutate(age = recode(age, 
                            "0s"="0-9y", 
                            "10s"="10-19y", "20s"= "20-29y", "30s"="30-39y",
                            "40s"="40-59y", "60s"="60+y"
        )
        ) %>% 
        mutate(age = factor(age, levels = c("0-9y", "10-19y","20-29y", "30-39y", "40-59y", "60+y")
        )
        ) %>% 
        rename(`0-9y`=`0s`, `10-19y`=`10s`, `20-29y` = `20s`, `30-39y`=`30s`,
               `40-59y`=`40s`, `60+y`=`60s`
        )#matrix with mean degree in each cell
      
      # matrix with proportion
      avg.matrix.prop <- avg.matrix %>% mutate( 
        
        `0-9y` = `0-9y`/total_degree,
        `10-19y` = `10-19y`/total_degree,
        `20-29y` = `20-29y`/total_degree,
        `30-39y` = `30-39y`/total_degree,
        `40-59y` = `40-59y`/total_degree,
        `60+y` = `60+y`/total_degree)
    
        
    }
    
    avg.matrix.list <- list()
    avg.matrix.list[[1]] <- avg.matrix %>% ungroup()
    avg.matrix.list[[2]] <- avg.matrix.prop %>% ungroup()
    names(avg.matrix.list) <- c("avg.matrix", "avg.matrix.prop")
    
    avg.matrix.list
  }

# Rural symmetric mixing matrices, 10 age groups
avg.matrices.india$avg.matrix.india.rural.10age.grps <- 
avg.matrix(mix.sum = india_mix.sum.no15$india_mix.sum.no15.rural.10age.grps  %>% rename(predictor_contact = contact_location),
           age_grp_count =10
           )

# Urban symmetric mixing matrices, 10 age groups
avg.matrices.india$avg.matrix.india.urban.10age.grps <- 
avg.matrix(mix.sum = india_mix.sum.no15$india_mix.sum.no15.urban.10age.grps  %>% rename(predictor_contact = contact_location),
           age_grp_count = 10
           )


# Rural symmetric mixing matrices, 6 age groups
avg.matrices.india$avg.matrix.india.rural.6age.grps <- 
avg.matrix(mix.sum = india_mix.sum.no15$india_mix.sum.no15.rural.6age.grps  %>% rename(predictor_contact = contact_location),
           age_grp_count = 6
           )

# Urban symmetric mixing matrices, 6 age groups
avg.matrices.india$avg.matrix.india.urban.6age.grps <- 
avg.matrix(mix.sum = india_mix.sum.no15$india_mix.sum.no15.urban.6age.grps  %>% rename(predictor_contact = contact_location),
           age_grp_count = 6
           )


#saveRDS(avg.matrices.india, file = "./data/network_params/avg.matrices.india.RData")



```

## Total degree by age group
Previously, the raw total degree (by participants' age group) was plotted. Since the total degree for each age group will be instead used for analysis, we plot the latter moving forward.
The below figure shows the total degree of contact in each age group by network (urban/rural) and layer (home/non-home). Panels A and C show the total degree by the original ten age groups, and panels B and D show the total degree by the six age groups combining the categories within each of the first two decades of life into a single group.


```{r pressure, echo=F, fig.width=10, fig.height=8}
# add back to text after revision - The total degree peaked in the age group of 10-14 years old and gradually became lower in the adjacent age groups. For participants < 1 year old in the rural population, the total degree of 6-11 months old #was lower than those < 6 months old.
#The participant's total degree tended to be higher at home than non-home locations among those that were not teenagers (10-19y). 


max_total_deg <- ceiling(max( avg.matrices.india$avg.matrix.india.rural.10age.grps$avg.matrix$total_degree, avg.matrices.india$avg.matrix.india.urban.10age.grps$avg.matrix$total_degree))
  
total_degree <- avg.matrices.india$avg.matrix.india.rural.10age.grps$avg.matrix %>% rename(contact_location = predictor_contact)

total_degree_plot <- # this replaced the function plotting the raw total degree
function(total_degree, network_name, max_total_degree){
  total_degree %>% 
  #select(contact_location,p_age,total_degree) %>%
  #distinct() %>% 
  ggplot( mapping = aes(x = age,y = total_degree)
        )+ 
  geom_col(aes(fill = contact_location) , position = position_dodge()
           )+
  theme_classic()+
  geom_text(aes(label = round(total_degree,1), group = contact_location), 
            colour = "black" ,  vjust = -0.2, size = 3,position = position_dodge(0.8)
            )+
  labs(x = "", y = "", color = "contact_location")+theme(legend.position = "top")+
  guides(fill=guide_legend(title=""))+
  ggtitle(network_name) +
  theme(plot.title = element_text(hjust = 0.5))+ scale_y_continuous(limits = c(0, max_total_degree))
  
}


annotate_figure(
  
ggarrange(
# Total degree by participant age group and network layer
total_degree_plot(total_degree = avg.matrices.india$avg.matrix.india.rural.10age.grps$avg.matrix %>% rename(contact_location = predictor_contact), 
                  network_name = "Rural", max_total_degree=max_total_deg)+
  theme(axis.text.x=element_blank()),
total_degree_plot(total_degree = avg.matrices.india$avg.matrix.india.rural.6age.grps$avg.matrix %>% rename(contact_location = predictor_contact), 
                  network_name = "Rural", max_total_degree=max_total_deg)+
  theme(axis.text.x=element_blank()),
total_degree_plot(total_degree = avg.matrices.india$avg.matrix.india.urban.10age.grps$avg.matrix %>% rename(contact_location = predictor_contact), 
                  network_name = "Urban", max_total_degree=max_total_deg),
total_degree_plot(total_degree = avg.matrices.india$avg.matrix.india.urban.6age.grps$avg.matrix %>% rename(contact_location = predictor_contact), 
                  network_name = "Urban", max_total_degree=max_total_deg),
ncol = 2, nrow = 2,
labels = c("A", "B", "C", "D"),
align = "h",
legend = "top",
common.legend = T
),

left = "Total degree",
bottom = "Age group"
)

```

## Symmetrical mixing matrices, by degree
In the following figures, panels A and C present the information by the ten original age groups. Panel B and D present the information by six age groups.

### Home/nonhome mixing in the rural population
```{r, echo=F, warning=F, message=FALSE, error =F, fig.width=10, fig.height=6}
# To be add back - In the rural setting, the mixings at home were generally more heterogeneous than nonhome settings. In nonhome settings, the degrees of mixing for those < one year old were generally lower than home settings #and close to zero.  The higest degrees were observed in the mixing within the same age groups of 5-9 years old and 10-14 years old in the nonhome settings.  


# symmetric home matrix in long format, rural, 10 age groups
avg.matrix.india.rural.home.10age.grps <- 
avg.matrices.india$avg.matrix.india.rural.10age.grps$avg.matrix  %>% ungroup() %>% filter(predictor_contact == "Home") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `<6mo`:`60+y`, names_to = "vertical_age_grp", values_to = "degree") %>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_contact$contact_age)
                                                                                                                                                                                                                                                                       )
                                                                                                                                                                                                                                             )

# symmetric non-home matrix in long format, rural, 10 age groups
avg.matrix.india.rural.nonhome.10age.grps <- 
avg.matrices.india$avg.matrix.india.rural.10age.grps$avg.matrix  %>% ungroup() %>% filter(predictor_contact == "Nonhome") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `<6mo`:`60+y`, names_to = "vertical_age_grp", values_to = "degree")%>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_contact$contact_age)
                                                                                                                                                                                                                                                                       )
         )

# symmetric home matrix in long format, rural, 6 age groups
avg.matrix.india.rural.home.6age.grps <- 
avg.matrices.india$avg.matrix.india.rural.6age.grps$avg.matrix  %>% ungroup() %>% filter(predictor_contact == "Home") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `0-9y`:`60+y`, names_to = "vertical_age_grp", values_to = "degree") %>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_mix$contact_age_reclass)
                                                                                                                                                                                                                                                                       )
                                                                                                                                                                                                                                             )

# symmetric non-home matrix in long format, rural, 6 age groups
avg.matrix.india.rural.nonhome.6age.grps <- 
avg.matrices.india$avg.matrix.india.rural.6age.grps$avg.matrix  %>% ungroup() %>% filter(predictor_contact == "Nonhome") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `0-9y`:`60+y`, names_to = "vertical_age_grp", values_to = "degree")%>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_mix$contact_age_reclass)
                                                                                                                                                                                                                                                                       )
         )

 


max.degree. <- # max degree across all setting to define the upper bound of color legend
ceiling(
  max(
max(avg.matrices.india$avg.matrix.india.rural.10age.grps$avg.matrix  %>% select(`<6mo`:`60+y`), na.rm = T),
max(avg.matrices.india$avg.matrix.india.urban.10age.grps$avg.matrix %>% select(`<6mo`:`60+y`), na.rm = T)
))


# function to visualize symmetric mixing matrix
symmetric_contactmatrix_viz <- function(matrix_long, max.degree, panel_title, metric){
  ggplot(data = matrix_long, aes(x=vertical_age_grp, y=age, fill=degree)) +  
    geom_raster(hjust = 0.5, vjust = 0.5, show.legend=T) +
     scale_colour_discrete(na.translate = F) + 
     geom_text(aes(label = round(degree, 1)
                   ), size= 3
               )+
    
    # for degree
    {if (metric == "degree") {
      scale_fill_gradient2(low="#0571b0", mid="#92c5de", high="#ca0020" , limit = c(0, max.degree), 
                         breaks = 0 :max.degree.
                         #breaks = c(0,0.5, 1:max.degree.)
                         )
      } else {
    # for proportion
      scale_fill_gradient2(low="#0571b0", mid="#92c5de", high="#ca0020" , limit = c(0, 1), 
                         breaks = c(0,0.2,0.4,0.6,0.8,1)
                         #breaks = c(0,0.5, 1:max.degree.)
                         )
      }
      }+
    
    theme_classic() +
    theme(legend.title = element_text(size = 10),
          legend.text = element_text(size = 7),
          legend.justification = "right",
          legend.position = "right") +
    theme(plot.title = element_text(size = 10), 
          axis.title.x = element_text(size=10, face="bold", angle=0),
          axis.title.y = element_text(size=10, face="bold"),
          axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size= 10))+
    xlab("")+ylab("")+
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+ 
    labs(fill="Degree")+ggtitle(panel_title)
}


 
annotate_figure(
  
ggarrange(
symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.rural.home.10age.grps, max.degree = max.degree., 
                            panel_title = "Home, Rural", metric = "degree")+
  theme(axis.text.x=element_blank()),

symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.rural.home.6age.grps, max.degree = max.degree., 
                            panel_title = "Home, Rural", metric = "degree")+
  theme(axis.text.x=element_blank()),
      

symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.rural.nonhome.10age.grps, max.degree = max.degree., 
                            panel_title = "Nonhome, Rural", metric = "degree"),

symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.rural.nonhome.6age.grps, max.degree = max.degree., 
                            panel_title = "Nonhome, Rural", metric = "degree"),


ncol = 2, nrow = 2,
labels = c("A", "B", "C", "D"),
align = "h",
legend = "top",
common.legend = T
),

left = "Age",
bottom = "Age"
)


```

### Home/nonhome mixing in the urban population

```{r, echo=F, warning=F, message=FALSE, error =F, fig.width=10, fig.height=6}
# Add back to text after revision - The mixing matrices in the home and nonhome settings in the urban population are generally similar to those in the rural population.

# symmetric home matrix in long format, urban, 10 age groups
avg.matrix.india.urban.home.10age.grps <- 
avg.matrices.india$avg.matrix.india.urban.10age.grps$avg.matrix  %>% ungroup() %>% filter(predictor_contact == "Home") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `<6mo`:`60+y`, names_to = "vertical_age_grp", values_to = "degree") %>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_contact$contact_age)
                                                                                                                                                                                                                                                                       )
                                                                                                                                                                                                                                             )

# symmetric non-home matrix in long format, urban, 10 age groups
avg.matrix.india.urban.nonhome.10age.grps <- 
avg.matrices.india$avg.matrix.india.urban.10age.grps$avg.matrix  %>% ungroup() %>% filter(predictor_contact == "Nonhome") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `<6mo`:`60+y`, names_to = "vertical_age_grp", values_to = "degree")%>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_contact$contact_age)
                                                                                                                                                                                                                                                                       )
         )

# symmetric home matrix in long format, urban, 6 age groups
avg.matrix.india.urban.home.6age.grps <- 
avg.matrices.india$avg.matrix.india.urban.6age.grps$avg.matrix  %>% ungroup() %>% filter(predictor_contact == "Home") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `0-9y`:`60+y`, names_to = "vertical_age_grp", values_to = "degree") %>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_mix$contact_age_reclass)
                                                                                                                                                                                                                                                                       )
                                                                                                                                                                                                                                             )

# symmetric non-home matrix in long format, urban, 6 age groups
avg.matrix.india.urban.nonhome.6age.grps <- 
avg.matrices.india$avg.matrix.india.urban.6age.grps$avg.matrix  %>% ungroup() %>% filter(predictor_contact == "Nonhome") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `0-9y`:`60+y`, names_to = "vertical_age_grp", values_to = "degree")%>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_mix$contact_age_reclass)
                                                                                                                                                                                                                                                                       )
         )

annotate_figure(
ggarrange(
symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.urban.home.10age.grps, max.degree = max.degree., 
                            panel_title = "Home, Urban", metric = "degree")+
  theme(axis.text.x=element_blank()),

symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.urban.home.6age.grps, max.degree = max.degree., 
                            panel_title = "Home, Urban", metric = "degree")+
  theme(axis.text.x=element_blank()),
      

symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.urban.nonhome.10age.grps, max.degree = max.degree., 
                            panel_title = "Nonhome, Urban", metric = "degree"),

symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.urban.nonhome.6age.grps, max.degree = max.degree., 
                            panel_title = "Nonhome, Urban", metric = "degree"),


ncol = 2, nrow = 2,
labels = c("A", "B", "C", "D"),
align = "h",
legend = "top",
common.legend = T
),

left = "Age",
bottom = "Age"
)



```



## Symmetrical mixing matrices, by proportion
Proportions below are calculated by dividing the $M.D.$ in each cell ($i,j$) by the total degree of the age group ($j$) it belonged to.

### Home/nonhome mixing in the rural population

```{r, echo=F, warning=F, message=FALSE, error =F, fig.width=10, fig.height=6}
# symmetric home matrix in long format, rural, 10 age groups
avg.matrix.india.rural.home.10age.grps.prop <- 
avg.matrices.india$avg.matrix.india.rural.10age.grps$avg.matrix.prop  %>% ungroup() %>% filter(predictor_contact == "Home") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `<6mo`:`60+y`, names_to = "vertical_age_grp", values_to = "degree") %>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_contact$contact_age)
                                                                                                                                                                                                                                                                       )
                                                                                                                                                                                                                                             )

# symmetric non-home matrix in long format, rural, 10 age groups
avg.matrix.india.rural.nonhome.10age.grps.prop <- 
avg.matrices.india$avg.matrix.india.rural.10age.grps$avg.matrix.prop  %>% ungroup() %>% filter(predictor_contact == "Nonhome") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `<6mo`:`60+y`, names_to = "vertical_age_grp", values_to = "degree")%>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_contact$contact_age)
                                                                                                                                                                                                                                                                       )
         )

# symmetric home matrix in long format, rural, 6 age groups
avg.matrix.india.rural.home.6age.grps.prop <- 
avg.matrices.india$avg.matrix.india.rural.6age.grps$avg.matrix.prop  %>% ungroup() %>% filter(predictor_contact == "Home") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `0-9y`:`60+y`, names_to = "vertical_age_grp", values_to = "degree") %>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_mix$contact_age_reclass)
                                                                                                                                                                                                                                                                       )
                                                                                                                                                                                                                                             )

# symmetric non-home matrix in long format, rural, 6 age groups
avg.matrix.india.rural.nonhome.6age.grps.prop <- 
avg.matrices.india$avg.matrix.india.rural.6age.grps$avg.matrix.prop  %>% ungroup() %>% filter(predictor_contact == "Nonhome") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `0-9y`:`60+y`, names_to = "vertical_age_grp", values_to = "degree")%>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_mix$contact_age_reclass)
                                                                                                                                                                                                                                                                       )
         )

 

 
annotate_figure(
  
ggarrange(
symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.rural.home.10age.grps.prop, max.degree = 1, 
                            panel_title = "Home, Rural", metric = "prop")+
  theme(axis.text.x=element_blank()),

symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.rural.home.6age.grps.prop, max.degree = 1, 
                            panel_title = "Home, Rural", metric = "prop")+
  theme(axis.text.x=element_blank()),
      

symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.rural.nonhome.10age.grps.prop, max.degree = 1, 
                            panel_title = "Nonhome, Rural", metric = "prop"),

symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.rural.nonhome.6age.grps.prop, max.degree = 1, 
                            panel_title = "Nonhome, Rural", metric = "prop"),


ncol = 2, nrow = 2,
labels = c("A", "B", "C", "D"),
align = "h",
legend = "top",
common.legend = T
),

left = "Age",
bottom = "Age"
)


```

### Home/nonhome mixing in the urban population
The mixing matrices in the home and nonhome settings in the urban population are generally similar to those in the rural population.
```{r, echo=F, warning=F, message=FALSE, error =F, fig.width=10, fig.height=6}
# symmetric home matrix in long format, urban, 10 age groups
avg.matrix.india.urban.home.10age.grps.prop <- 
avg.matrices.india$avg.matrix.india.urban.10age.grps$avg.matrix.prop  %>% ungroup() %>% filter(predictor_contact == "Home") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `<6mo`:`60+y`, names_to = "vertical_age_grp", values_to = "degree") %>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_contact$contact_age)
                                                                                                                                                                                                                                                                       )
                                                                                                                                                                                                                                             )

# symmetric non-home matrix in long format, urban, 10 age groups
avg.matrix.india.urban.nonhome.10age.grps.prop <- 
avg.matrices.india$avg.matrix.india.urban.10age.grps$avg.matrix.prop  %>% ungroup() %>% filter(predictor_contact == "Nonhome") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `<6mo`:`60+y`, names_to = "vertical_age_grp", values_to = "degree")%>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_contact$contact_age)
                                                                                                                                                                                                                                                                       )
         )

# symmetric home matrix in long format, urban, 6 age groups
avg.matrix.india.urban.home.6age.grps.prop <- 
avg.matrices.india$avg.matrix.india.urban.6age.grps$avg.matrix.prop  %>% ungroup() %>% filter(predictor_contact == "Home") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `0-9y`:`60+y`, names_to = "vertical_age_grp", values_to = "degree") %>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_mix$contact_age_reclass)
                                                                                                                                                                                                                                                                       )
                                                                                                                                                                                                                                             )

# symmetric non-home matrix in long format, urban, 6 age groups
avg.matrix.india.urban.nonhome.6age.grps.prop <- 
avg.matrices.india$avg.matrix.india.urban.6age.grps$avg.matrix.prop  %>% ungroup() %>% filter(predictor_contact == "Nonhome") %>% select(`age`:`60+y`)  %>% pivot_longer(cols = `0-9y`:`60+y`, names_to = "vertical_age_grp", values_to = "degree")%>% 
  mutate(vertical_age_grp = factor(vertical_age_grp, levels= levels(india_mix$contact_age_reclass)
                                                                                                                                                                                                                                                                       )
         )

 

 
annotate_figure(
  
ggarrange(
symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.urban.home.10age.grps.prop, max.degree = 1, 
                            panel_title = "Home, Urban", metric = "prop")+
  theme(axis.text.x=element_blank()),

symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.urban.home.6age.grps.prop, max.degree = 1, 
                            panel_title = "Home, Urban", metric = "prop")+
  theme(axis.text.x=element_blank()),
      

symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.urban.nonhome.10age.grps.prop, max.degree = 1, 
                            panel_title = "Nonhome, Urban", metric = "prop"),

symmetric_contactmatrix_viz(matrix_long = avg.matrix.india.urban.nonhome.6age.grps.prop, max.degree = 1, 
                            panel_title = "Nonhome, Urban", metric = "prop"),


ncol = 2, nrow = 2,
labels = c("A", "B", "C", "D"),
align = "h",
legend = "top",
common.legend = T
),

left = "Age",
bottom = "Age"
)



```



## Degree proportion of contact age by participant age
The following plots consider the direction of contact (between participants and contacts) and were presented to validate the symmetry mixing matrices. Overall, the proportion distributions mirror the degree distributions in the symmetric mixing matrices. Notably, for participants < one year old, they had non-home contacts with more age groups in urban than rural setting. The patterns were similar across layers (home/nonhome) and networks (urban/rual) for age groups ≥ one year old.

### Proportion of the study population in rural areas
```{r, echo=F, warning=F, message=FALSE, error =F, fig.width=10, fig.height=8}

# function to visualize degree proportion by participant's age and contact's age
degree.proportion.age <- function(mix.sum, panel_title){
  ggplot(data = mix.sum,
       mapping = aes(x = p_age,
                     y = prop_degree,
                     fill = contact_age)
       ) +
  geom_bar(stat="identity")+
  theme_classic()+
  labs(x = "", y = "")+ 
  guides(fill=guide_legend(title="Contact age")
  )+ggtitle(panel_title)
}


annotate_figure(
  
ggarrange(

degree.proportion.age(mix.sum = india_mix.sum.no15$india_mix.sum.no15.rural.10age.grps %>% filter(contact_location == "Home"), 
                      panel_title = "Home, Rural")+
  theme(axis.text.x=element_blank())+theme(legend.position = "bottom"),

degree.proportion.age(mix.sum = india_mix.sum.no15$india_mix.sum.no15.rural.6age.grps %>% filter(contact_location == "Home"), 
                      panel_title = "Home, Rural")+
  theme(axis.text.x=element_blank())+theme(axis.text.y=element_blank())+theme(legend.position = "bottom"),

degree.proportion.age(mix.sum = india_mix.sum.no15$india_mix.sum.no15.rural.10age.grps %>% filter(contact_location == "Nonhome"), 
                      panel_title = "Nonhome, Rural")+ theme(legend.position = "none"),

degree.proportion.age(mix.sum = india_mix.sum.no15$india_mix.sum.no15.rural.6age.grps %>% filter(contact_location == "Nonhome"), 
                      panel_title = "Nonhome, Rural") + theme(axis.text.y=element_blank())+ theme(legend.position = "none"),


ncol = 2, nrow = 2,

align = "h",
labels = c("A", "B", "C", "D"),
common.legend = F
),

left = "Degree Proportion",
bottom = "Participant age"
)

```

### Proportion of the study population in urban areas
```{r, echo=F, warning=F, message=FALSE, error =F,  fig.width=10, fig.height=8}

annotate_figure(
  
ggarrange(

degree.proportion.age(mix.sum = india_mix.sum.no15$india_mix.sum.no15.urban.10age.grps %>% filter(contact_location == "Home"), 
                      panel_title = "Home, Urban")+
  theme(axis.text.x=element_blank())+theme(legend.position = "bottom"),

degree.proportion.age(mix.sum = india_mix.sum.no15$india_mix.sum.no15.urban.6age.grps %>% filter(contact_location == "Home"), 
                      panel_title = "Home, Urban")+
  theme(axis.text.x=element_blank())+theme(axis.text.y=element_blank())+theme(legend.position = "bottom"),

degree.proportion.age(mix.sum = india_mix.sum.no15$india_mix.sum.no15.urban.10age.grps %>% filter(contact_location == "Nonhome"), 
                      panel_title = "Nonhome, Urban")+ theme(legend.position = "none"),

degree.proportion.age(mix.sum = india_mix.sum.no15$india_mix.sum.no15.urban.6age.grps %>% filter(contact_location == "Nonhome"), 
                      panel_title = "Nonhome, Urban") + theme(axis.text.y=element_blank())+ theme(legend.position = "none"),


ncol = 2, nrow = 2,

align = "h",

common.legend = F
),

left = "Degree Proportion",
bottom = "Participant age"
)

```

