---
title: "Network Modeling for GlobalMix India Data"
author: "Billy Dehao Chen"
date: "9/28/2023"
output: word_document
editor_options: 
  chunk_output_type: console
---

# Background
Calculates the final target statistics for the network models by applying individual-level network statistics against the population size and structure.


```{r, echo=F, warning=F, message=FALSE}
lapply(c("tidyverse", "EpiModel", "ggpubr", "knitr", "svglite", "kableExtra"), require, character.only = TRUE)


# load network parameters----------------------------------------
formation_stats <- readRDS("~/Documents/GitHub/COVID-GlobalMix/data/network_params/formation_stats.RData")

dissolution_stats <- readRDS("~/Documents/GitHub/COVID-GlobalMix/data/network_params/known_dur_school_work.RData")

formation_stats$rural$nf.age.grp %>% View()
formation_stats$rural$nf.age.grp$single_day_nf_md_prop[1:6] %>% sum()
# 'raw'  mixing data by mean degree for one day
#gm.raw <- readRDS("~/Documents/GitHub/COVID-GlobalMix/data/network_params/corp_mix_deg/india_mix.sum.no15.RData")
# daily mixing matrix
#matrices <- readRDS("~/Documents/GitHub/COVID-GlobalMix/data/network_params/corp_mix_deg/avg.matrices.india.RData") 

#  daily mixing matrix by mean degree


# function to calculate degree information for later deriving of target statistics
# md.info <- function(raw_contact,sym.matrix){ # it'd be better to organize things in list for this.
#   
#   output <- list()
#   
#   # mean degree by network layer (contact location)
#   output[[1]] <- raw_contact  %>% group_by(contact_location, participant_age, n_participants) %>% 
#   summarise(n_contacts = sum(n_contacts)) %>%
#   ungroup() %>%
#   group_by(contact_location) %>%
#   summarise(n_contacts = sum(n_contacts),
#             n_participants = sum(n_participants)) %>%
#   mutate(md = (n_contacts/n_participants)/2)
#   
#   # total daily degree of edges per age group for nodefactor()
#   output[[2]] <- 
#   rbind(
#   sym.matrix %>%
#   filter(contact_location == "Home") %>%
#   select(total_degree) %>%
#   as_vector() %>%
#   as.numeric(),
#   
#   sym.matrix %>%
#   filter(contact_location == "Nonhome") %>%
#   select(total_degree) %>%
#   as_vector() %>%
#   as.numeric(),
#   
#   sym.matrix %>%
#   filter(contact_location == "School") %>%
#   select(total_degree) %>%
#   as_vector() %>%
#   as.numeric(),
#   
#   sym.matrix %>%
#   filter(contact_location == "Work") %>%
#   select(total_degree) %>%
#   as_vector() %>%
#   as.numeric()
#   
#   
#   )
#   row.names(output[[2]]) <- c("Home", "Nonhome", "School", "Work"); colnames(output[[2]]) <- levels(sym.matrix$age); 
#   output[[2]] <- as.data.frame(output[[2]])
#   
#   # proportion of daily within-age-group matching by contact_location
#   output[[3]] <- sym.matrix  %>% 
#   mutate(within_age_edges = total_degree*prop_match) %>% # at the daily scale
#   select(contact_location,age,total_degree,within_age_edges) %>%
#   group_by(contact_location) %>%
#   summarise(total_degree = sum(total_degree),
#             within_age_edges = sum(within_age_edges)) %>%
#   mutate(match = within_age_edges/total_degree) %>% as.data.frame() # at the daily scale
#   
#   names(output) <- c("md.layer", # md by contact location
#                      "md.ag", # md by age group
#                      "within.ag.match.prop")
#   
#   output
# }
# 
# md.info.rural <-md.info(raw_contact = gm.raw$india_mix.sum.no15.rural.6age.grps,
#                         sym.matrix = matrices$avg.matrix.india.rural$avg.matrix %>%
#                          ungroup()
#                         ) ## rural
# 
# 
# md.info.urban <- md.info(raw_contact = gm.raw$india_mix.sum.no15.urban.6age.grps,
#                          sym.matrix =  matrices$avg.matrix.india.urban$avg.matrix %>%
#                          ungroup()
#                          ) ## urban



```

## Age distribution of target population
```{r, warning=F, message=FALSE, echo=T, fig.height=7}
# age group of GM

target_age_grp <- formation_stats$rural$nf.age.grp$participant_age %>% unique()%>% factor()
  #matrices$avg.matrix.india.rural.6age.grps$avg.matrix$age %>% levels()
total_pop_rural <- c(199+750+933,1017+958,1196+1195,1309+1272,1215+1088+1067+876,777+626+499+321+437)
total_pop_urban <-c(309+1144+1458,1474+1814,1805+1731,1740+1669,1471+1395+1206+975,891+572+412+236+245)
target_age_dist <- data.frame(target_age_grp=rep(target_age_grp,2),
                              total_pop=c(total_pop_rural, total_pop_urban),
                              network=rep(c("rural", "urban"), each = length(target_age_grp))
                              )

# proportion of target population in each age group by network
target_age_dist <- 
target_age_dist %>% 
  group_by(network) %>%
  mutate(prop=total_pop/sum(total_pop))

ggarrange(
target_age_dist %>% ggplot(aes(x=target_age_grp, y=total_pop))+geom_bar(stat = "identity")+facet_wrap(~network)+
  geom_text(aes(label=total_pop), vjust=-0.3, size=3.5)+
  theme_classic()+ylab("Population")+xlab("Age group"),
target_age_dist %>% ggplot(aes(x=target_age_grp, y=prop))+geom_bar(stat = "identity")+facet_wrap(~network)+
  geom_text(aes(label=round(prop,2)), vjust=-0.3, size=3.5)+
  theme_classic()+ylab("Population proportion")+xlab("Age group"),
nrow = 2
)
```




## Set up model attribute and characterize target statistics
```{r, warning=F, message=FALSE, echo=T}
############## Set up vertex attribute ##############
# Initiate nodes
n <- 10000 #each for the two networks
nw_rural <- nw_urban <- network_initialize(n)

node.age.grp <- 
  function(target_age_dist, site){
## nodes in a single site network
target_age_dist_site<- 
target_age_dist %>% filter(network == site) %>% mutate(n_pop_site.age.grp=round(prop*n)) # number of nodes in each age group

## single nodes indicated by age group; 
age.grp_site <- 
target_age_dist_site %>% rownames_to_column() %>% 
  rename(age.grp.num=rowname) %>% 
  slice(rep(1:n(), times= n_pop_site.age.grp)
                          ) %>% ungroup(network) %>% 
  pull(age.grp.num) 


## Age bounds of each node
min_age <- c(0,10,20,30,40,60); max_age <- c(9,19,29,39,59,100) # age ranges

## Generate age for each node based on age bounds
age_site <- c()
for (i in 1:6) {
  age_site <-
    c(age_site,
  runif(n= target_age_dist_site$n_pop_site.age.grp[i],# the number of node to simulate in each group equals to the number of target target population in each group
      min=min_age[i], max=max_age[i]
      ) # age range in each age group
  )
}

data.frame(age.grp_site, age_site)     
}
 
node.age.grp.rural <- 
 node.age.grp(target_age_dist=target_age_dist, site= "rural") 

# node.age.grp.urban <- 
#  node.age.grp(target_age_dist=target_age_dist, site= "urban") 

# Nodes w/ age groups
### Initialize a rural network, home layer
nw_rural <- set_vertex_attribute(nw_rural, "age",
                                 node.age.grp.rural %>% pull(age_site)
                                 )
nw_rural <- set_vertex_attribute(nw_rural, "age.grp",
                                 node.age.grp.rural %>% pull(age.grp_site)
                                 )

# nw_urban <- set_vertex_attribute(nw_urban, "age",
#                                  node.age.grp.urban %>% pull(age_site)
#                                  )
node.age.grp.rural %>% View()

############## Model target statistics ##############


# Total Edges, edge-level
formation_stats$rural$edge <- 
formation_stats$rural$edge %>% mutate(edges=single_day_md*n/2)# the reason /2 is used here is because this is a edge-level statistic

#formation_stats$rural$nf.age.grp %>% View()

# Number of edges per age group, node-level
formation_stats$rural$nf.age.grp <- 
 formation_stats$rural$nf.age.grp %>% 
  left_join(
target_age_dist %>% filter(network == "rural")%>% mutate(n_pop_site.age.grp=round(prop*n)) %>% # calculate number of nodes in each age group based on age distribution of the target population
  rename(participant_age=target_age_grp) %>% select(participant_age, n_pop_site.age.grp), 
by = "participant_age"
  ) %>% mutate(nf.ag = single_day_nf_md_prop*n_pop_site.age.grp) 

 
 
# md.h.ag_rural <- # mean degree of edge in each age group
#   matrices$avg.matrix.india.rural.6age.grps$avg.matrix %>% filter(contact_location == "Home")%>% 
#   select(total_degree) %>%
#   as_vector() %>%
#   as.numeric()
# nf.h.ag <- md.h.ag_rural * age.grp.num_rural # daily total degree * total number of people in each age group = number of edges per age group

#  Number of matched edges nodematch(diff=T), edge-level
formation_stats$rural$nm.age.grp <- 
formation_stats$rural$nm.age.grp %>% 
  left_join(formation_stats$rural$nf.age.grp %>% select(participant_age, contact_location, nf.ag)
            ) %>% 
  mutate(nm.ag = (nf.ag/2)*single_day_nm_md
           )

```

## Model fitting and simulation
```{r, warning=F, message=FALSE, echo=T}
# Formulation model
formation.edge <- ~edges 
formation.edge.nf <- ~edges + nodefactor("age.grp" , levels = 2:6) 
formation.edge.nf.nm <- ~edges + nodefactor("age.grp" , levels = 2:6) + nodematch("age.grp" , levels = 2:6)

# Dissolution model
diss.h <- dissolution_coefs(dissolution = ~offset(edges), duration = 1e6) # 36500 - total number of day in life, very high duration 
diss.nh <- dissolution_coefs(dissolution = ~offset(edges), duration = 1) # non-persistent (turnover every day)
diss.school.rural <- dissolution_coefs(dissolution = ~offset(edges), 
                                       duration = dissolution_stats %>% filter(study_site=="Rural" & contact_location=="School") %>% pull(know_contact_duration_avg.)
                                       ) 
diss.work.rural <- dissolution_coefs(dissolution = ~offset(edges), 
                                       duration = dissolution_stats %>% filter(study_site=="Rural" & contact_location=="Work") %>% pull(know_contact_duration_avg.)
                                       ) 
diss.school.urban <- dissolution_coefs(dissolution = ~offset(edges), 
                                       duration = dissolution_stats %>% filter(study_site=="Urban" & contact_location=="School") %>% pull(know_contact_duration_avg.)
                                       ) 
diss.work.urban <- dissolution_coefs(dissolution = ~offset(edges), 
                                       duration = dissolution_stats %>% filter(study_site=="Urban" & contact_location=="Work") %>% pull(know_contact_duration_avg.)
                                       ) 



# Target statistics, home, rural
tstats.edge.h.rural <- c(formation_stats$rural$edge[1,4])
tstats.edge.nf.h.rural <- c(tstats.edge.h.rural,
                            (formation_stats$rural$nf.age.grp %>% filter(contact_location == "Home" ) %>% pull(nf.ag))[-1])

tstats.edge.nf.nm.h.rural <- c(tstats.edge.nf.h.rural, 
                               (formation_stats$rural$nm.age.grp %>% filter(contact_location == "Home" ) %>% pull(nm.ag))[-1])





```


```{r, warning=F, message=FALSE, echo=T}
# Edge model
## Fit edge-only model to data
est.h.edges <- netest(nw_rural, 
                      formation = formation.edge, 
                      target.stats = tstats.edge.h.rural, 
                      coef.diss =  diss.h,
                 set.control.ergm = control.ergm(MCMLE.maxit = 100)
                 )

## Simulate based on the edge model for only the edge effect
dx.h.edges_obs<- netdx(est.h.edges, nsims = 20, ncores = 8, 
                   nsteps = 1000, dynamic = T,
               set.control.ergm = control.simulate.formula(MCMC.burnin = 1e5),
               nwstats.formula = formation.edge, 
               keep.tedgelist = TRUE)

par(mfrow=c(1,2)
    )

plot(dx.h.edges_obs)
plot(dx.h.edges_obs, type = "duration"); plot(dx.h.edges_obs, type = "dissolution")



## Simulate based on the edge model adding an extra term
dx.h.edges.nf.sim<- netdx(est.h.edges, nsims = 20, ncores = 8, 
                   nsteps = 1000, dynamic = T,
               set.control.ergm = control.simulate.formula(MCMC.burnin = 1e5),
               nwstats.formula = ~edges  + nodefactor("age.grp"),  #formation.edge.nf , 
               keep.tedgelist = TRUE) 

print(dx.h.edges.nf.sim) # the percentage diff of the edge effect is worsen compare to the edge-only model but is still ~ 5%


# Edge + nodefactor(age.grp) model
## Fit edge-only model to data
est.h.edges.nf <- netest(nw_rural, 
                      formation = formation.edge.nf, 
                      target.stats = tstats.edge.nf.h.rural, 
                      coef.diss =  diss.h,
                 set.control.ergm = control.ergm(MCMLE.maxit = 100)
                 )

## Simulate based on the edge model 
dx.h.edges.nf.obs<- netdx(est.h.edges.nf, nsims = 20, ncores = 8, 
                   nsteps = 1000, dynamic = T,
               set.control.ergm = control.simulate.formula(MCMC.burnin = 1e5),
               nwstats.formula = formation.edge.nf, 
               keep.tedgelist = TRUE
               )

print(dx.h.edges.nf.obs)

plot(dx.h.edges.nf.obs)
plot(dx.h.edges.nf.obs, type = "duration")

par(mfrow=c(1,2)
    )
plot(dx.h.edges.nf.obs, type = "duration"); plot(dx.h.edges.obs, type = "dissolution")

## Dropping age group 5, which have a best fit among all nf coefficients
formation.edge.nf_1 <- ~edges + nodefactor("age.grp" , levels = c(2,3,4,6)
                                           )

## Fit edge-only model to data
est.h.edges.nf_1 <- netest(nw_rural, 
                      formation = formation.edge.nf_1, 
                      target.stats = tstats.edge.nf.h.rural[-5], 
                      coef.diss =  diss.h,
                 set.control.ergm = control.ergm(MCMLE.maxit = 100)
                 )

## Simulate based on the edge model 
dx.h.edges.nf.obs_1<- netdx(est.h.edges.nf_1, nsims = 20, ncores = 8, 
                   nsteps = 1000, dynamic = T,
               set.control.ergm = control.simulate.formula(MCMC.burnin = 1e5),
               nwstats.formula = formation.edge.nf_1, 
               keep.tedgelist = TRUE
               )

print(dx.h.edges.nf.obs_1) # 

plot(dx.h.edges.nf.obs_1)
par(mfrow=c(1,2)
    )
plot(dx.h.edges.nf.obs_1, type = "duration"); plot(dx.h.edges.obs_1, type = "dissolution")



```



The table below suggests the edge statistics is still more biased than the edge-only simulation after included the observed nodefactor data
```{r, warning=F, message=FALSE, echo=T}
# Model with target statistics of edge and node factor
## Fit  model to data
est.h.edges.nf <- netest(nw_rural, formation.edge.nf, target.stats.edges.nf.h, coef.diss.h,
                 set.control.ergm = control.ergm(MCMLE.maxit = 500)
                 )
## Simulate 
dx.h.edges.nf_obs <- netdx(est.h.edges.nf, nsims = 100, ncores = 8, 
                   nsteps = 1000, dynamic = T,
               set.control.ergm = control.simulate.formula(MCMC.burnin = 1e6),
               nwstats.formula = ~edges  + nodefactor("age.grp"), 
               keep.tedgelist = TRUE)

dx.h.edges.nf_obs %>% print()
## Extract summary statistics from simulation
dx.h.edges.nf_obs$stats.table.formation %>% select(2, 4) %>%
 # filter(!row_number() %in% c(1)) %>% 
  mutate(Sim_mean_ci_low = `Sim Mean` -1.96*`Sim SE`,
         Sim_mean_ci_up = `Sim Mean` +1.96*`Sim SE`) %>% 
  rownames_to_column(var= "age.grp") %>% 
  mutate(age.grp=str_replace(age.grp,  "nodefactor.age.grp.", "")
  ) %>% 
 select(-`Sim SE`) %>% cbind(., observed_nf =target.stats.edges.nf.h ) %>% select(1,5,2:4)

```

After adding the nodematch term in the simulation, the bias of the edge effect is lower than the edge-only model. Is this a conincendence?
```{r, warning=F, message=FALSE, echo=T}
## Simulate w/ node match
dx.h.edges.nf.nm_sim <- 
  netdx(est.h.edges.nf, nsims = 100, ncores = 8, 
                   nsteps = 1000, dynamic = T,
               set.control.ergm = control.simulate.formula(MCMC.burnin = 1e6),
               nwstats.formula = ~edges  + nodefactor("age.grp") + nodematch("age.grp"), 
               keep.tedgelist = TRUE)

dx.h.edges.nf.nm_sim$stats.table.formation %>% select(2, 4) %>%
  #filter(!row_number() %in% c(1)) %>% 
  mutate(Sim_mean_ci_low = `Sim Mean` -1.96*`Sim SE`,
         Sim_mean_ci_up = `Sim Mean` +1.96*`Sim SE`) %>% 
  rownames_to_column(var= "age.grp") %>% 
  mutate(age.grp=str_replace(age.grp,  "nodefactor.age.grp.", "")
  ) %>% 
 select(-`Sim SE`) %>% cbind(., observed_nf = target.stats.edges.nf.nm.h
                             ) %>% select(1,5,2:4)


```

Now the bias of the edge effect is bigger again after including the observed nodematch data.
```{r, warning=F, message=FALSE, echo=T}
# Model with target statistics of edge and node factor and node match

## Fit  model to data
est.h.edges.nf.nm <- netest(nw_rural, formation.edge.nf.nm, target.stats.edges.nf.nm.h, coef.diss.h,
                 set.control.ergm = control.ergm(MCMLE.maxit = 500)
                 )
## Simulate 
dx.h.edges.nf.nm_obs<- netdx(est.h.edges.nf.nm, nsims = 100, ncores = 8, 
                   nsteps = 1000, dynamic = T,
               set.control.ergm = control.simulate.formula(MCMC.burnin = 1e6),
               nwstats.formula = ~edges  + nodefactor("age.grp") + nodematch("age.grp"), 
               keep.tedgelist = TRUE
               )

dx.h.edges.nf.nm_obs %>% print()
dx.h.edges.nf.nm_obs$stats.table.formation %>% select(2, 4) %>%
  #filter(!row_number() %in% c(1)) %>% 
  mutate(Sim_mean_ci_low = `Sim Mean` -1.96*`Sim SE`,
         Sim_mean_ci_up = `Sim Mean` +1.96*`Sim SE`) %>% 
  rownames_to_column(var= "age.grp") %>% 
  mutate(age.grp=str_replace(age.grp,  "nodefactor.age.grp.", "")
  ) %>% 
 select(-`Sim SE`) %>% cbind(., observed_nf = target.stats.edges.nf.nm.h
                             )%>% select(1,5,2:4)

```














